### 2016-07-06 draft.tex
Initial file in repository.

\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{slashed}
\usepackage{graphicx}
\usepackage{feynmf}
\graphicspath{ {images/} }
\setlength{\parindent}{10ex}

\begin{document}

	\section{Introduction}
	\section{Math details}
	The process is similar in many ways to restrictions on axion emission from supernova cooling. The procedure therefore roughly follows the analogous calculation for axions, as laid out by Raffelt. 
	\subsection{Bremsstrahlung amplitude calculation}
	 There are two processes to consider: the pp bremsstrahlung $ p+p \rightarrow p+p+A$ and the pn $ p+n \rightarrow p+n+A\ $. For the pp case, there are eight tree-level diagrams, as shown in Fig. ; for the pn, five diagrams, as shown in Fig. . \newline

Considering first the pp diagrams, each of the $p-p-\pi $ vertices contribute a factor of $ i\gamma_5 g_{pp}$ , where $g_{pp}$ is the pseudoscalar pion-nucleon coupling. $f_{pp}$, the pseudovector pion-nucleon coupling, is related by $ g_{pp} = \frac{2M_N}{m_\pi} f_{pp} $. The internal  pion line contributes a factor of $\frac{-i}{\mathcal{L}^2 - m_\pi^2}$, where $ \mathcal{L} $ is the appropriate exchange momentum.  The two outgoing nucleons each contribute a spinor $ \bar{u}(p_i)$, and the two incoming nucleons contribute a spinor $u(p_i)$. The outgoing boson A with momentum $q_a$ contributes a polarization vector $\epsilon^\mu$, and the $ p-p-A $ vertex contributes $e\epsilon \gamma_\mu$. The internal fermion line, between the $p-p-\pi$ vertex and the $p-p-A$ vertex, contributes a factor of \[ -i\frac{\slashed p_5 + M_N}{p_5^2-M^2_N} \] where $p_5$ is the momentum of the internal fermion. Considering diagram 2 as an example, we have $p_5 = q_a + p_3$, and so $p_5^2 = p_5 \cdot p_5 = q_a^2 + p_3^2 + 2 (q_a \cdot p_3)$, and the factor from the fermion line becomes \[ -i\frac{\slashed p_i \pm \slashed q_a + M_N}{m_A^2 \pm 2 q_a \cdot p_i} \] where the index labels which of the nucleons attaches to the A boson, while the plus sign corresponds to diagrams where it attaches right of the pion vertex, and the minus to diagrams where it attaches left of the pion vertex. Labeling them from one to eight, with the exchange diagrams given odd labels and the direct given even labels, the matrix elements are then
		 \[ M_1 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed{\epsilon} u(p_1)\]
%
	 	\[ M_2 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p3) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed \epsilon  u(p_1) \]
	%
	 	\[ M_3 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \epsilon  u(p_2) \]
%
	 	\[ M_4 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \epsilon  u(p_2) \]
%	
		 \[ M_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
			 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \slashed{\epsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2)\]
			 %
		\[ M_6 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
		 		 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \slashed{\epsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2)\]
			 		 %
 		 \[ M_7 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
		 		 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \slashed{\epsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1)\]
			 		 		 %
		\[ M_8 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
		}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1)\]
		%
	where the exchange momenta are defined by $ k = p_2-p_4 $ and $ l = p_2-p_3 $, and $ f_{pp} $ is the pseudovector pion-nucleon coupling.

	The amplitude is then \[  \sum_{spins} \mathcal{M}^2 = \sum_{spins}|M_2+M_4+M_6+M_8-M_1-M_3-M_5-M_7|^2  \]. At this point the calculation diverges from the axionic bremsstrahlung calculation: in the region of the mass of the A boson is not necessarily negligible. The kinematic relations are thus \[ 
	p_1 \cdot p_2 = M_N^2 - \frac{l^2}{2} - \frac{k^2}{2} + p_2 \cdot q_a\]
	 \[p_1 \cdot p_3 = M_N^2 + k \cdot l - \frac{k^2}{2} + p_3 \cdot q_a\]  
	 \[p_1 \cdot p_4 = k \cdot l + M_N^2 - \frac{l^2}{2} + p_4 \cdot q_a \]
	 \[p_2 \cdot p_3 = M_N^2 - \frac{l^2}{2} \]
 	 \[p_2 \cdot p_4 = M_N^2 - \frac{k^2}{2} \]
 	 \[p_3 \cdot p_4 = k \cdot l + M_N^2 - \frac{l^2 + k^2}{2} \]
 	 Unfortunately, with these relations it does not seem to be possible to simplify the amplitude into an analytically usable form without making unjustified approximations, and so the final expression contains some two hundred and fifty terms.

 	 For the pn interaction the calculation proceeds similarly, with the only new matrix element coming from diagram five, bremsstrahlung off the internal pion 
 	 \[ M_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \epsilon}{l^2-m_\pi^2
 	 }  \frac{1}{(l-q_a)^2 - m_\pi^2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) u(p_2) (q_a - 2l)\cdot \epsilon \]
	This amplitude too is unwieldy.

	\subsection{Streaming limit}
	The first and simplest bound that may obtained arises from assuming that all produced particles leave the supernova, carrying their energy with them. The constraint is derived simply by requiring that the energy loss through this cooling channel be roughly less than the cooling from neutrino emission; any greater, and it would have an observable effect on supernova cooling.

	The actual quantity of interest therefore is the rate of energy emission through dark bosons. From the spin-summed amplitudes already found this is obtained by integrating over the phase space, and adding a factor of energy

	\[ Q_i = \int (2\pi)^4 E_A \sum_{spins} \mathcal{M}^2_i f(p_1) f(p_2)\delta(p_1+p_2-p_3-p_4-q_a) dLIPS \]
	Here $ E_A $ is the energy of the emitted boson, and $ f(p) $ are the initial occupation numbers. The nucleons in the core are comfortably non-degenerate and non-relativistic, so  the Pauli blocking factor is omitted and the Maxwell-Boltzmann distribution used  \[ f(p) =  \frac{n_b}{2} (\frac{2 \pi}{M_N T})^{3/2} e^{-\frac{\textbf{p}^2} {2 M_N T}} \]

	This integration is performed numerically to obtain $ Q_i $, which is the rate of energy emission per unit volume associated with either the pn or pp process. To obtain the dark gauge boson luminosity, it is assumed that production takes place in a core volume of radius 1 km, so $ \mathcal{L}_A = V(Q_{pp} + Q_{pn}) $. $ \mathcal{L}_A $ is a complicated function of $ m_A $ and $ T $, but is simply proportional to the square of the parameter $ \epsilon $; pulling that out of the expression gives a constraint \[ \epsilon^2 I_A(m_A, T) \le \mathcal{L}_\nu \] or a bound on the coupling of \[ \epsilon \le \sqrt{\frac{4.1 * 10^{37} MeV^2}{I_A(m_A, T)}} \] and the exclusion region is generated by varying the mass.

	\subsection{Decay limit}
	The constraint from the streaming limit above provides an upper bound on the allowed coupling and lower bound on the excluded coupling by considering purely production. Naively it might be expected that this suffices, that all higher couplings are excluded. However, in order to function as a cooling channel, obviously enough of the produced light gauge bosons must escape the supernova. As the coupling increases, so do processes that prevent this,and so the excluded region has an upper bound, above which the luminosity again drops below the neutrino luminosity. The first such limit may be found by considering decay of the dark bosons into Standard Model particles, and assuming that these SM particles are trapped in the supernova core and contribute nothing to the cooling. The dark boson has a typical lifetime of 
	\[ l = \frac{3 E_{A}}{N_{eff} m_A^2 \epsilon^2}  \]
	and so the fraction escaping the supernova is given by 
	\[ e^{\frac{r_{decay}}{l}} = e^{\frac{r_{decay} N_{eff} m_A^2 \epsilon^2}{3 E_A}} \] To take this into account, the above exponential factor is simply appended to the phase space integrand, and the calculation then proceeds as before. The limit is derived from the same equation, with the only complication being the fact that $ I_A $ is now a function of $ \epsilon $, in addition to $ m_A, T $. This makes the numerical calculation slightly more complicated, but otherwise changes nothing of importance. 
	 \[ \epsilon \le \sqrt{\frac{4.1 * 10^{37} MeV^2}{I_A(m_A, T, \epsilon)}} \]

	\subsection{Trapping limit}
	The second constraint that produces an upper bound on the excluded region comes from considering trapping of dark bosons within the supernova. With a large enough coupling, the new particles will thermalize and then be emitted from a spherical shell. In this case the luminosity is given simply by the Steffan-Boltzmann law
	\[ \mathcal{L}_t  = 4\pi r^2 T_A^4 \sigma\]
	where $ r $ is now the radius of the emitting shell and $ T_A $ its temperature. These must typically be calculated, but for $ r $ it is safe to assume a value of 10 km, since the density of the supernova drops drastically around that point. After taking that value for r, the bound on the luminosity translates into a bound on $ T_A $ \[ T_A \le 9.586 MeV \] That bound can then be translated into the desired bound on the coupling as a function of mass by assuming that the particles are emitted from an optical depth $ \tau = \frac{2}{3} $, and finding the temperature that corresponds to that optical depth. This is a somewhat involved calculation.
	First, one needs a model for the density and temperature in the supernova. Following \cite{dent}, we assume \[ \rho = \rho_p (\frac{R}{r})^2 \] \[ T = T_R (\frac{R}{r})^{n/3} \]
	with $  \rho_p  = 3*10^{14} g/cm^3, T_R = 30$ MeV, and taking $ n = 5 $. The optical depth is given by \[ \tau = \int_{r_x}^{\infty} \kappa \rho dr \]where $ \kappa is the opacity $. 
	To find the opacity, we start from the reduced mean Rosseland opacity \[ \frac{1}{\kappa \rho} = \int_{m_x}^{\infty} \frac{15}{4 \pi^4 T^5} \frac{E_A^2 e^{E_A/T} \sqrt{E_A^2 - m_A^2}}{(e^{E_A/T}-1)^2} l_A dE_A \]where $ l_A $ is the mean free path.

	The inverse mean free path can readily be obtained by modifying $ Q_i $, the expression for the energy loss rate, as follows: removing the factor of $ E_A $ and the phase space integral over $ q_A $, and adding a factor of $ e^{E_A/T} $ for detailed balance. This gives the inverse mean free path as a function of mass and coupling. Again the required integration is performed numerically. This then allows the calculation of $ \kappa_x $. The inverse opacities for the pn and pp processes add, giving the total opacity $ \kappa^{-1} = \kappa_{pp}^{-1} + \kappa_{pn}^{-1} $

	Having obtained an expression for $ \kappa $, we can now find the optical depth
	[note to self: rework the steps here; too confusing]
	and the bound on the coupling is finally found by requiring  $ \tau_R(\epsilon,m_A) \le 2/3 $

	\section{Computational details}
	In every case calculating the bound requires integrating an expression involving the long and complicated Bremsstrahlung amplitude, which unfortunately could not be done analytically without making unjustified approximations. The integration was consequently performed numerically using the Monte Carlo routines provided by the Cuba library. The complexity of the integration was such that errors remained relatively large even with highest practicable number of samples. 
	\section{Results}
	\section{Discussion/Conclusion}

%	\begin{thebibliography}{9}
%		
%		G. Raffelt,
%		\emph{Stars as laboratories for fundamental physics: The astrophysics of neutrinos, axions, and other weakly interacting
%			particles},
%		(University of Chicago Press
%		1996)
%		\bibitem{dent}
%		J.B. Dent, F. Ferrer, L. M. Krauss, 2012, arXiv:1201.2683

%	\end{thebibliography}
\end{document}

### 2016-07-07 EFTpart.tex
Add files via upload

\documentclass[]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\begin{document}

\section{EFT Discussion}

	The previous work modelled the nucleon-neucleon interactions involved using the one pion exchange potential (OPE). However, for low energy NN scattering, the OPE approximation proves inconsistent with the nuclear forces involved, and does not represent the fine tuning of the problem. In this case it becomes appropriate to search for an effective field theory (EFT) of the nuclear interaction instead. To this end there has been considerable work done on chiral perturbation theory, producing a number of EFTs representing the low energy interactions. For our purposes we employed perhaps the simplest such scheme, the so-called pionless EFT, in which even the pionic degree of freedom is integrated out, and we are left with a simple contact interaction. The breakdown scale for this theory is set by the pion mass, $ m_\pi = 139 MeV $, and for momenta above this scale in general the pions should be included explicitly in the theory. In our case though, the relevant scales - the supernova temperature and the light dark boson mass - are in general much lower than $ m_\pi $, so we can safely ignore them. There was a slight concern that at the higher end of the mass region we consider, the pionless EFT should no longer apply, but experimentally the EFT we use remains fairly good up to a couple of multiples of $ m_\pi $, by which point Boltzmann suppression factor is so large that EFT deviations become largely insignificant.

	To lowest order, the pionless EFT effective interaction Lagrangian is \[ {\cal L} =
	C_{0}^{\left( ^{3}S_{1}\right) }(N^{T}P_{i}N)^{\dagger }(N^{T}P_{i}N) + C_{0}^{\left( ^{1}S_{0}\right) } (N^{T}\overline{P}_{i}N)^{\dagger }((N^{T}\overline{P}_{i}N) \] where $ C_{0}^{\left( ^{3}S_{1}\right) }, C_{0}^{\left( ^{1}S_{0}\right) } $ are the effective couplings for the $ \left ^{3}S_{1}\right $ and $ {\left ^{1}S_{0}\right $ channels respectively. $ P_i, \overline{P}_i $ are the projection operators onto each channel, explicitly \[ P_{i}= \frac{1}{\sqrt{8}} \sigma_2 \tau_2 \tau_i, \overline{P}_i = \frac{1}{\sqrt{8}} \sigma_2 \sigma_i \tau_2 \], where $ \sigma $ ($ \tau $) acts on spin (isospin) space. The effective couplings are determined by matching to the effective range expansion, and are renormalization-dependent.
		% Can go into much more detail about power counting and matching conditions, but didn't think it was appropriate
	The diagrams to consider therefore has only external fermion lines, with the gaugue boson coming off one of them. This is considerably simpler than the full OPE calculation.

\end{document}

### 2016-07-08 draft.tex
Trivial edit.
Added computational stuff

@@
 The integration was consequently performed numerically using the Monte Carlo routines provided by the Cuba library.
+Employing kinematic relations did not seem to reduce the complexity of the problem, so in the interests of reducing the number of possible mistakes the kinematics were done by brute force.
+We integrated over the entire phase space explicitly in terms of the eleven variables of $ \vec{p_1}, \vec{p_2}, \vec{p_3}, \hat{q_a} $, then fixed $ p_4 $ using the 3-momentum part of the delta-function and used an unpleasantly complicated equation obtained from the energy delta-function to fix the remaining one free momentum amplitude - in our case we chose this to be $ q_a $, the momentum of the emitted boson.
+At each step points resulting in unphysical configurations were discarded, and the remaining points were then plugged in to the appropriate amplitude, and then that result used as the integrand.
+The numerical integration routine used was the \textit{Suave} method provided by CUBA, which combines importance sampling and adaptive subdivision; this method seemed to provide the best compromise between computation time and error.
+
+	Once the integration is complete the calculation of the trapping and streaming limits is a straightforward application of the equations previously derived, and proceeded as outlined above.
+The decay limit is somewhat harder, since $ \epsilon $ appears on both sides of the equation.
+Again we employed an unsubtle approach to solving the problem: $ \epsilon $ was set to an arbitrary value where the constraint was satisfied, and then iteratively reduced until the constraint was no longer satisfied.
+This obviously introduces another source of error, but with a sufficiently small interval in $ \epsilon $ this is negligible.
+The one further slight complication is that at after a certain value of $ M_A $ the decay limit rapidly goes to zero, at which point the procedure was terminated.
+
+	We then scanned over the desired range of values for $ M_A $ and output the three limits - trapping, decay, and streaming - at each point.
 The complexity of the integration was such that errors remained relatively large even with highest practicable number of samples.
+
 	\section{Results}

### 2016-07-25 draft.tex
modifying section 2.

@@
 	\section{Introduction}
-	\section{Math details}
-	The process is similar in many ways to restrictions on axion emission from supernova cooling. The procedure therefore roughly follows the analogous calculation for axions, as laid out by Raffelt. 
+	\section{Computational details}
+	The process we are considering, the bremsstrahlung of a dark photon from nucleon-nucleon scattering, is similar in many ways to the classic calculation of axion emission from supernova cooling.
+The differences arise due to the mass of the dark photon, which can be on the order of the temperature of the supernova.
+This leads to different kinematics compared to the axion case.
+However, the calculation roughly follows the analogous calculation for axions, as laid out by Raffelt, which we briefly review below.
 	\subsection{Bremsstrahlung amplitude calculation}

### 2016-07-25 draft.tex
Modified tex file to be phys rev style.

@@
-\documentclass[10pt,a4paper]{article}
-\usepackage[latin1]{inputenc}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
+\documentclass[nofootinbib,aps,prd,preprint,superscriptaddress]{revtex4}
+\usepackage{amsmath,graphicx,hyperref}
 \usepackage{slashed}
-\usepackage{graphicx}
-\usepackage{feynmf}
-\graphicspath{ {images/} }
-\setlength{\parindent}{10ex}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Command %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newcommand{\fms}[1]{{#1}\!\!\!/}
+\newcommand{\fmsl}[1]{{#1}\!\!\!\!/}
+
+\newcommand{\mc}{\mathcal}
+\newcommand{\mr}{\mathrm}
+\newcommand{\mP}{\mathcal{P}}
+\newcommand{\mO}{\mathcal{O}}
+
+\newcommand{\be}{\begin{equation}} 
+\newcommand{\ee}{\end{equation}} 
+\newcommand{\beq}{\begin{equation}} 
+\newcommand{\eeq}{\end{equation}} 
+\newcommand{\bea}{\begin{eqnarray}} 
+\newcommand{\eea}{\end{eqnarray}}
+
+\newcommand{\ov}{\overline}
+\newcommand{\pp}{\perp}
+\newcommand{\dg}{\dagger}
+\newcommand{\n}{\overline{n}}
+\newcommand{\nn}{\frac{\fms{\overline{n}}}{2}} 
+\newcommand{\nnn}{\frac{\fms{n}}{2}}
+
+\newcommand{\bl}[1]{{\bf{#1}}}
+\newcommand{\bla}[1]{|{\bf{#1}}|}
+\newcommand{\blp}[1]{{\bf{#1}}_{\perp}}
+\newcommand{\blpu}[1]{{\bf{#1}}^{\perp}}
+\newcommand{\blpa}[1]{|{\bf{#1}}_{\perp}|}
+\newcommand{\bs}[1]{\boldsymbol{#1}}
+\newcommand{\bsp}[1]{{\boldsymbol{#1}}_{\perp}}
+
+\newcommand{\ds}{\displaystyle} 
+\newcommand{\nnb}{\nonumber}
+
+\newcommand{\as}{\alpha_s}
+
+\newcommand{\eps}{\epsilon} 
+\newcommand{\veps}{\varepsilon}
+
+\newcommand{\UV}{\veps_{\mr{UV}}}
+\newcommand{\IR}{\veps_{\mr{IR}}}
+
+\newcommand{\La}{\Lambda^2_{\rm{alg}}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\topmargin 0.0 in
 
 \begin{document}
+
+\baselineskip 3.0ex
+
+\vspace*{18pt}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title{Title?}
+
+\def\Pitt{Pittsburgh Particle Physics Astrophysics and Cosmology Center (PITT PACC) \\ Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, Pennsylvania 15260, USA}
+
+\author{Cameron Mahoney}
+\email[E-mail:]{cbm34@pitt.edu}
+\affiliation{\Pitt}
+\author{Adam K. Leibovich}
+\email[E-mail:]{akl2@pitt.edu}
+\affiliation{\Pitt}
+\author{Andrew R. Zentner}
+\email[E-mail:]{zentner@pitt.edu}
+\affiliation{\Pitt}
+
+\begin{abstract} 
+\baselineskip 3.0ex   
+Abstract?
+\end{abstract}
+
+\maketitle
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 The outgoing boson A with momentum $q_a$ contributes a polarization vector $\epsilon^\mu$, and the $ p-p-A $ vertex contributes $e\epsilon \gamma_\mu$.
-The internal fermion line, between the $p-p-\pi$ vertex and the $p-p-A$ vertex, contributes a factor of \[ -i\frac{\slashed p_5 + M_N}{p_5^2-M^2_N} \] where $p_5$ is the momentum of the internal fermion.
-Considering diagram 2 as an example, we have $p_5 = q_a + p_3$, and so $p_5^2 = p_5 \cdot p_5 = q_a^2 + p_3^2 + 2 (q_a \cdot p_3)$, and the factor from the fermion line becomes \[ -i\frac{\slashed p_i \pm \slashed q_a + M_N}{m_A^2 \pm 2 q_a \cdot p_i} \] where the index labels which of the nucleons attaches to the A boson, while the plus sign corresponds to diagrams where it attaches right of the pion vertex, and the minus to diagrams where it attaches left of the pion vertex.
+The internal fermion line, between the $p-p-\pi$ vertex and the $p-p-A$ vertex, contributes a factor of
+\begin{equation} 
+-i\frac{\slashed p_5 + M_N}{p_5^2-M^2_N},
+\end{equation}
+where $p_5$ is the momentum of the internal fermion.
+Considering diagram 2 as an example, we have $p_5 = q_a + p_3$, and so $p_5^2 = p_5 \cdot p_5 = q_a^2 + p_3^2 + 2 (q_a \cdot p_3)$, and the factor from the fermion line becomes
+\begin{equation}
+-i\frac{\slashed p_i \pm \slashed q_a + M_N}{m_A^2 \pm 2 q_a \cdot p_i},
+\end{equation}
+where the index labels which of the nucleons attaches to the A boson, while the plus sign corresponds to diagrams where it attaches right of the pion vertex, and the minus to diagrams where it attaches left of the pion vertex.
 Labeling them from one to eight, with the exchange diagrams given odd labels and the direct given even labels, the matrix elements are then
-		 \[ M_1 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
-	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed{\epsilon} u(p_1)\]
-%
-	 	\[ M_2 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
-	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p3) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed \epsilon  u(p_1) \]
-	%
-	 	\[ M_3 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
-	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \epsilon  u(p_2) \]
-%
-	 	\[ M_4 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
-	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \epsilon  u(p_2) \]
-%	
-		 \[ M_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
-			 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \slashed{\epsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2)\]
-			 %
-		\[ M_6 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
-		 		 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \slashed{\epsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2)\]
-			 		 %
- 		 \[ M_7 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
-		 		 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \slashed{\epsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1)\]
-			 		 		 %
-		\[ M_8 = \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
-		}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1)\]
-		%
+\bea
+M_1 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
+	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed{\epsilon} u(p_1),\\
+M_2 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
+	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p3) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed \epsilon  u(p_1), \\
+M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
+	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \epsilon  u(p_2), \\
+M_4 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
+	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \epsilon  u(p_2), \\
+M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
+			 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \slashed{\epsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
+M_6 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
+		 		 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \slashed{\epsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
+M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
+		 		 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \slashed{\epsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),\\
+M_8 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
+		}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),
+\eea
 where the exchange momenta are defined by $ k = p_2-p_4 $ and $ l = p_2-p_3 $, and $ f_{pp} $ is the pseudovector pion-nucleon coupling.
 
-	The amplitude is then \[  \sum_{spins} \mathcal{M}^2 = \sum_{spins}|M_2+M_4+M_6+M_8-M_1-M_3-M_5-M_7|^2  \].
-At this point the calculation diverges from the axionic bremsstrahlung calculation: in the region of the mass of the A boson is not necessarily negligible.
-The kinematic relations are thus \[
-	p_1 \cdot p_2 = M_N^2 - \frac{l^2}{2} - \frac{k^2}{2} + p_2 \cdot q_a\]
-	 \[p_1 \cdot p_3 = M_N^2 + k \cdot l - \frac{k^2}{2} + p_3 \cdot q_a\]  
-	 \[p_1 \cdot p_4 = k \cdot l + M_N^2 - \frac{l^2}{2} + p_4 \cdot q_a \]
-	 \[p_2 \cdot p_3 = M_N^2 - \frac{l^2}{2} \]
- 	 \[p_2 \cdot p_4 = M_N^2 - \frac{k^2}{2} \]
- 	 \[p_3 \cdot p_4 = k \cdot l + M_N^2 - \frac{l^2 + k^2}{2} \]
+The amplitude is then 
+\beq
+\sum_{spins} \mathcal{M}^2 = \sum_{spins}|M_2+M_4+M_6+M_8-M_1-M_3-M_5-M_7|^2.
+\eeq
+At this point the calculation diverges from the axionic bremsstrahlung calculation: in the region of the mass of the A boson is not necessarily negligible. The kinematic relations are thus \bea 
+p_1 \cdot p_2 &=& M_N^2 - \frac{l^2}{2} - \frac{k^2}{2} + p_2 \cdot q_a,\\
+p_1 \cdot p_3 &=& M_N^2 + k \cdot l - \frac{k^2}{2} + p_3 \cdot q_a,\\  
+p_1 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2}{2} + p_4 \cdot q_a, \\
+p_2 \cdot p_3 &=& M_N^2 - \frac{l^2}{2}, \\
+p_2 \cdot p_4 &=& M_N^2 - \frac{k^2}{2},\\
+p_3 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2 + k^2}{2}
+\eea
  Unfortunately, with these relations it does not seem to be possible to simplify the amplitude into an analytically usable form without making unjustified approximations, and so the final expression contains some two hundred and fifty terms.
@@
  For the pn interaction the calculation proceeds similarly, with the only new matrix element coming from diagram five, bremsstrahlung off the internal pion 
- 	 \[ M_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \epsilon}{l^2-m_\pi^2
- 	 }  \frac{1}{(l-q_a)^2 - m_\pi^2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) u(p_2) (q_a - 2l)\cdot \epsilon \]
+ \beq
+ M_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \epsilon}{l^2-m_\pi^2
+ 	 }  \frac{1}{(l-q_a)^2 - m_\pi^2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) u(p_2) (q_a - 2l)\cdot \epsilon
+\eeq
 This amplitude too is unwieldy.
@@
 
-	\[ Q_i = \int (2\pi)^4 E_A \sum_{spins} \mathcal{M}^2_i f(p_1) f(p_2)\delta(p_1+p_2-p_3-p_4-q_a) dLIPS \]
+\beq
+Q_i = \int (2\pi)^4 E_A \sum_{spins} \mathcal{M}^2_i f(p_1) f(p_2)\delta(p_1+p_2-p_3-p_4-q_a) dLIPS.
+\eeq
 Here $ E_A $ is the energy of the emitted boson, and $ f(p) $ are the initial occupation numbers.
-The nucleons in the core are comfortably non-degenerate and non-relativistic, so  the Pauli blocking factor is omitted and the Maxwell-Boltzmann distribution used  \[ f(p) =  \frac{n_b}{2} (\frac{2 \pi}{M_N T})^{3/2} e^{-\frac{\textbf{p}^2} {2 M_N T}} \]
+The nucleons in the core are comfortably non-degenerate and non-relativistic, so  the Pauli blocking factor is omitted and the Maxwell-Boltzmann distribution used
+\beq
+	f(p) =  \frac{n_b}{2} (\frac{2 \pi}{M_N T})^{3/2} e^{-\frac{\textbf{p}^2} {2 M_N T}}.
+\eeq
 
@@
 To obtain the dark gauge boson luminosity, it is assumed that production takes place in a core volume of radius 1 km, so $ \mathcal{L}_A = V(Q_{pp} + Q_{pn}) $.
-$ \mathcal{L}_A $ is a complicated function of $ m_A $ and $ T $, but is simply proportional to the square of the parameter $ \epsilon $; pulling that out of the expression gives a constraint \[ \epsilon^2 I_A(m_A, T) \le \mathcal{L}_\nu \] or a bound on the coupling of \[ \epsilon \le \sqrt{\frac{4.1 * 10^{37} MeV^2}{I_A(m_A, T)}} \] and the exclusion region is generated by varying the mass.
+$ \mathcal{L}_A $ is a complicated function of $ m_A $ and $ T $, but is simply proportional to the square of the parameter $ \epsilon $; pulling that out of the expression gives a constraint
+\beq
+\epsilon^2 I_A(m_A, T) \le \mathcal{L}_\nu
+\eeq
+or a bound on the coupling of 
+\beq 
+\epsilon \le \sqrt{\frac{4.1 * 10^{37} MeV^2}{I_A(m_A, T)}} 
+\eeq 
+and the exclusion region is generated by varying the mass.
 
@@
 The dark boson has a typical lifetime of
-	\[ l = \frac{3 E_{A}}{N_{eff} m_A^2 \epsilon^2}  \]
+\beq
+l = \frac{3 E_{A}}{N_{eff} m_A^2 \epsilon^2},
+\eeq
 and so the fraction escaping the supernova is given by 
-	\[ e^{\frac{r_{decay}}{l}} = e^{\frac{r_{decay} N_{eff} m_A^2 \epsilon^2}{3 E_A}} \] To take this into account, the above exponential factor is simply appended to the phase space integrand, and the calculation then proceeds as before.
+\beq
+e^{\frac{r_{decay}}{l}} = e^{\frac{r_{decay} N_{eff} m_A^2 \epsilon^2}{3 E_A}}.
+\eeq
+To take this into account, the above exponential factor is simply appended to the phase space integrand, and the calculation then proceeds as before.
 The limit is derived from the same equation, with the only complication being the fact that $ I_A $ is now a function of $ \epsilon $, in addition to $ m_A, T $.
 This makes the numerical calculation slightly more complicated, but otherwise changes nothing of importance.
-	 \[ \epsilon \le \sqrt{\frac{4.1 * 10^{37} MeV^2}{I_A(m_A, T, \epsilon)}} \]
+\beq
+\epsilon \le \sqrt{\frac{4.1 * 10^{37} MeV^2}{I_A(m_A, T, \epsilon)}}.
+\eeq
 
@@
 In this case the luminosity is given simply by the Steffan-Boltzmann law
-	\[ \mathcal{L}_t  = 4\pi r^2 T_A^4 \sigma\]
+\beq
+\mathcal{L}_t  = 4\pi r^2 T_A^4 \sigma,
+\eeq
 where $ r $ is now the radius of the emitting shell and $ T_A $ its temperature.
 These must typically be calculated, but for $ r $ it is safe to assume a value of 10 km, since the density of the supernova drops drastically around that point.
-After taking that value for r, the bound on the luminosity translates into a bound on $ T_A $ \[ T_A \le 9.586 MeV \] That bound can then be translated into the desired bound on the coupling as a function of mass by assuming that the particles are emitted from an optical depth $ \tau = \frac{2}{3} $, and finding the temperature that corresponds to that optical depth.
+After taking that value for r, the bound on the luminosity translates into a bound on $ T_A $
+\beq
+T_A \le 9.586 MeV.
+\eeq
+That bound can then be translated into the desired bound on the coupling as a function of mass by assuming that the particles are emitted from an optical depth $ \tau = \frac{2}{3} $, and finding the temperature that corresponds to that optical depth.
 This is a somewhat involved calculation.
-	First, one needs a model for the density and temperature in the supernova. Following \cite{dent}, we assume \[ \rho = \rho_p (\frac{R}{r})^2 \] \[ T = T_R (\frac{R}{r})^{n/3} \]
-	with $  \rho_p  = 3*10^{14} g/cm^3, T_R = 30$ MeV, and taking $ n = 5 $. The optical depth is given by \[ \tau = \int_{r_x}^{\infty} \kappa \rho dr \]where $ \kappa is the opacity $. 
-	To find the opacity, we start from the reduced mean Rosseland opacity \[ \frac{1}{\kappa \rho} = \int_{m_x}^{\infty} \frac{15}{4 \pi^4 T^5} \frac{E_A^2 e^{E_A/T} \sqrt{E_A^2 - m_A^2}}{(e^{E_A/T}-1)^2} l_A dE_A \]where $ l_A $ is the mean free path.
+First, one needs a model for the density and temperature in the supernova. Following \cite{dent}, we assume 
+\bea
+\rho &=& \rho_p (\frac{R}{r})^2,\\
+T &=& T_R (\frac{R}{r})^{n/3},
+\eea
+with $  \rho_p  = 3*10^{14} g/cm^3, T_R = 30$ MeV, and taking $ n = 5 $. The optical depth is given by 
+\beq
+\tau = \int_{r_x}^{\infty} \kappa \rho dr,
+\eeq
+where $ \kappa$ is the opacity.  To find the opacity, we start from the reduced mean Rosseland opacity 
+\beq
+\frac{1}{\kappa \rho} = \int_{m_x}^{\infty} \frac{15}{4 \pi^4 T^5} \frac{E_A^2 e^{E_A/T} \sqrt{E_A^2 - m_A^2}}{(e^{E_A/T}-1)^2} l_A dE_A,
+\eeq
+where $ l_A $ is the mean free path.
 
@@
 %	\end{thebibliography}
+\end{document}\acknowledgments
+
+AKL was supported in part by NSF grant PHY-1519175.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{thebibliography}{99}
+%\normalsize
+
+\end{thebibliography}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2016-07-29 draft.tex
Worked on II.A.

@@
 \section{Introduction}
+
 \section{Computational details}
@@
 However, the calculation roughly follows the analogous calculation for axions, as laid out by Raffelt, which we briefly review below.
+As in the classical axion calculation, we will use the one-pion exchange (OPE) approximation.
+
 \subsection{Bremsstrahlung amplitude calculation}
-	 There are two processes to consider: the pp bremsstrahlung $ p+p \rightarrow p+p+A$ and the pn $ p+n \rightarrow p+n+A\ $.
-For the pp case, there are eight tree-level diagrams, as shown in Fig.
-; for the pn, five diagrams, as shown in Fig.
+	 There are two processes to consider: the $pp$ scattering with the bremsstrahlung of the dark photon, $ p+p \rightarrow p+p+A$, and the $pn$ scattering with bremsstrahlung, $ p+n \rightarrow p+n+A\ $.
+For the $pp$ case there are eight tree-level diagrams, with the emission of the $A'$ from each of the external legs, as shown in Fig.
+, while for the $pn$ case there are five diagrams, including when the $A'$ is emitted from the exchanged charged pion, as shown in Fig.
 .
-\newline
 
-Considering first the pp diagrams, each of the $p-p-\pi $ vertices contribute a factor of $ i\gamma_5 g_{pp}$ , where $g_{pp}$ is the pseudoscalar pion-nucleon coupling.
-$f_{pp}$, the pseudovector pion-nucleon coupling, is related by $ g_{pp} = \frac{2M_N}{m_\pi} f_{pp} $.
-The internal  pion line contributes a factor of $\frac{-i}{\mathcal{L}^2 - m_\pi^2}$, where $ \mathcal{L} $ is the appropriate exchange momentum.
-The two outgoing nucleons each contribute a spinor $ \bar{u}(p_i)$, and the two incoming nucleons contribute a spinor $u(p_i)$.
-The outgoing boson A with momentum $q_a$ contributes a polarization vector $\epsilon^\mu$, and the $ p-p-A $ vertex contributes $e\epsilon \gamma_\mu$.
-The internal fermion line, between the $p-p-\pi$ vertex and the $p-p-A$ vertex, contributes a factor of
-\begin{equation} 
--i\frac{\slashed p_5 + M_N}{p_5^2-M^2_N},
-\end{equation}
-where $p_5$ is the momentum of the internal fermion.
-Considering diagram 2 as an example, we have $p_5 = q_a + p_3$, and so $p_5^2 = p_5 \cdot p_5 = q_a^2 + p_3^2 + 2 (q_a \cdot p_3)$, and the factor from the fermion line becomes
-\begin{equation}
--i\frac{\slashed p_i \pm \slashed q_a + M_N}{m_A^2 \pm 2 q_a \cdot p_i},
-\end{equation}
-where the index labels which of the nucleons attaches to the A boson, while the plus sign corresponds to diagrams where it attaches right of the pion vertex, and the minus to diagrams where it attaches left of the pion vertex.
-Labeling them from one to eight, with the exchange diagrams given odd labels and the direct given even labels, the matrix elements are then
+The calculation of these diagrams are straightforward, using standard Feynman rules.
+Each of the $p-p-\pi $ vertices contribute a factor of $g_{pp}$,  the pseudoscalar pion-nucleon coupling.
+$f_{pp}$, the pseudovector pion-nucleon coupling, is related by $g_{pp} = \frac{2M_N}{m_\pi} f_{pp} $.
+The $ p-p-A' $ vertex contributes $e\epsilon \gamma_\mu$, where $\epsilon$ is the mixing strength between the photon and dark photon.
+Labeling the contributions according to the Feynman diagrams in Fig.
+, the matrix elements are
 \bea
 M_1 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
-	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed{\epsilon} u(p_1),\\
+	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed{\varepsilon} u(p_1),\\
 M_2 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
-	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p3) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed \epsilon  u(p_1), \\
+	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p3) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed \varepsilon  u(p_1), \\
 M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
-	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \epsilon  u(p_2), \\
+	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \varepsilon  u(p_2), \\
 M_4 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
-	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \epsilon  u(p_2), \\
+	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \varepsilon  u(p_2), \\
 M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
-			 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \slashed{\epsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
+			 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \slashed{\varepsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
 M_6 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
-		 		 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \slashed{\epsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
+		 		 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \slashed{\varepsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
 M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
-		 		 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \slashed{\epsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),\\
+		 		 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \slashed{\varepsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),\\
 M_8 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
-		}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),
+		}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \slashed{\varepsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),
 \eea
-where the exchange momenta are defined by $ k = p_2-p_4 $ and $ l = p_2-p_3 $, and $ f_{pp} $ is the pseudovector pion-nucleon coupling.
+where the exchange momenta are defined by $ k = p_2-p_4 $ and $ l = p_2-p_3 $, and the dark photon's polarization is given by $\varepsilon$.
+Note that these matrix elements agree with Ref.~\cite{Dent:2012mx}.
 
-The amplitude is then 
-\beq
-\sum_{spins} \mathcal{M}^2 = \sum_{spins}|M_2+M_4+M_6+M_8-M_1-M_3-M_5-M_7|^2.
-\eeq
-At this point the calculation diverges from the axionic bremsstrahlung calculation: in the region of the mass of the A boson is not necessarily negligible. The kinematic relations are thus \bea 
+At this point the calculation diverges from the axion bremsstrahlung calculation, since in the kinematic region of interest for supernova explosions, the mass of the $A'$ boson is not necessarily negligible.
+The kinematic relations are thus \bea
 p_1 \cdot p_2 &=& M_N^2 - \frac{l^2}{2} - \frac{k^2}{2} + p_2 \cdot q_a,\\
@@
 p_2 \cdot p_4 &=& M_N^2 - \frac{k^2}{2},\\
-p_3 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2 + k^2}{2}
+p_3 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2 + k^2}{2}.
 \eea
- Unfortunately, with these relations it does not seem to be possible to simplify the amplitude into an analytically usable form without making unjustified approximations, and so the final expression contains some two hundred and fifty terms.
+Unfortunately, with these relations it does not seem to be possible to simplify the amplitude into an analytically usable form without making unjustified approximations, and so the final expression for the spin-averaged squared matrix element, $ \mathcal{M}^2_{pp}$, contains some two hundred and fifty terms, and thus we do not reproduce that result here.\footnote{At this point we diverge from Ref.~\cite{Dent:2012mx} for two reasons.
+One, they use the kinematics as if the $A'$ were massless, as in the axion calculation, and independent of that choice, their squared matrix element does not respect the correct exchange symmetry, as can be seen by inspection of their Eq.
+(A.3), with the claim that only $C_k$ appearing in that equation is nonzero.}
 
- For the pn interaction the calculation proceeds similarly, with the only new matrix element coming from diagram five, bremsstrahlung off the internal pion 
+ For the $pn$ scattering, the calculation proceeds similarly, with the only new Feynman diagram coming from bremsstrahlung off the internal pi, resulting in  
  \beq
- M_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \epsilon}{l^2-m_\pi^2
- 	 }  \frac{1}{(l-q_a)^2 - m_\pi^2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) u(p_2) (q_a - 2l)\cdot \epsilon
+ M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \epsilon}{l^2-m_\pi^2
+ 	 }  \frac{1}{(l-q_a)^2 - m_\pi^2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) u(p_2) (q_a - 2l)\cdot \varepsilon
 \eeq
-This amplitude too is unwieldy.
+Again, due to the more complicated kinematics due to the non-negligible mass of the $A'$, the resulting squared amplitude, $ \mathcal{M}^2_{pn}$, is too unwieldy to reproduce here.
 
@@
 \section{Results}
+
 \section{Discussion/Conclusion}
 
-%	\begin{thebibliography}{9}
-%		
-%		G. Raffelt,
-%		\emph{Stars as laboratories for fundamental physics: The astrophysics of neutrinos, axions, and other weakly interacting
-%			particles},
-%		(University of Chicago Press
-%		1996)
-%		\bibitem{dent}
-%		J.B. Dent, F. Ferrer, L. M. Krauss, 2012, arXiv:1201.2683
-
-%	\end{thebibliography}
-\end{document}\acknowledgments
+\acknowledgments
 
 AKL was supported in part by NSF grant PHY-1519175.
+
+\begin{thebibliography}{99}
+%\normalsize
+
+%\cite{Dent:2012mx}
+\bibitem{Dent:2012mx} 
+  J.~B.~Dent, F.~Ferrer and L.~M.~Krauss,
+  %``Constraints on Light Hidden Sector Gauge Bosons from Supernova Cooling,''
+  arXiv:1201.2683 [astro-ph.CO].
+  %%CITATION = ARXIV:1201.2683;%%
+  %56 citations counted in INSPIRE as of 29 Jul 2016
+
+\end{thebibliography}
+
+\end{document}
 
@@
 
-\begin{thebibliography}{99}
-%\normalsize
-
-\end{thebibliography}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-07-29 draft.tex
tiny change to footnote
Went through II.B - II.D.

@@
 One, they use the kinematics as if the $A'$ were massless, as in the axion calculation, and independent of that choice, their squared matrix element does not respect the correct exchange symmetry, as can be seen by inspection of their Eq.
-(A.3), with the claim that only $C_k$ appearing in that equation is nonzero.}
+(A.3), with their claim that only the coefficient $C_k$ appearing in that equation is nonzero.}
 
@@
 \subsection{Streaming limit}
-The first and simplest bound that may obtained arises from assuming that all produced particles leave the supernova, carrying their energy with them.
+The first and simplest bound that may be obtained arises from assuming that all produced particles leave the supernova, carrying their energy with them.
 The constraint is derived simply by requiring that the energy loss through this cooling channel be roughly less than the cooling from neutrino emission; any greater, and it would have an observable effect on supernova cooling.
@@
 The actual quantity of interest therefore is the rate of energy emission through dark bosons.
-From the spin-summed amplitudes already found this is obtained by integrating over the phase space, and adding a factor of energy
-
+From the spin-summed squared amplitudes already given, this is obtained by integrating over the phase space, and adding a factor of energy
 \beq
-Q_i = \int (2\pi)^4 E_A \sum_{spins} \mathcal{M}^2_i f(p_1) f(p_2)\delta(p_1+p_2-p_3-p_4-q_a) dLIPS.
+Q_i = \int (2\pi)^4 E_A \sum_{spins} \mathcal{M}^2_i f(p_1) f(p_2)\delta(p_1+p_2-p_3-p_4-q_a) d\Pi,
 \eeq
-Here $ E_A $ is the energy of the emitted boson, and $ f(p) $ are the initial occupation numbers.
-The nucleons in the core are comfortably non-degenerate and non-relativistic, so  the Pauli blocking factor is omitted and the Maxwell-Boltzmann distribution used
+where $d\Pi$ is the Lorentz-invariant phase space, $ E_A $ is the energy of the emitted boson, and $ f(p) $ are the initial occupation numbers.
+The nucleons in the core are comfortably non-degenerate and non-relativistic, so  the Pauli blocking factor is omitted and the Maxwell-Boltzmann distribution is used
 \beq
@@
 
-This integration is performed numerically to obtain $ Q_i $, which is the rate of energy emission per unit volume associated with either the pn or pp process.
-To obtain the dark gauge boson luminosity, it is assumed that production takes place in a core volume of radius 1 km, so $ \mathcal{L}_A = V(Q_{pp} + Q_{pn}) $.
-$ \mathcal{L}_A $ is a complicated function of $ m_A $ and $ T $, but is simply proportional to the square of the parameter $ \epsilon $; pulling that out of the expression gives a constraint
+The integration is performed numerically to obtain $ Q_i$, which is the rate of energy emission per unit volume associated with either the $pn$ or $pp$ process.
+To obtain the dark gauge boson luminosity, it is assumed that production takes place in a core volume $V$ of radius 1 km, giving $ \mathcal{L}_A = V(Q_{pp} + Q_{pn}) $.
+The luminosity $\mathcal{L}_A $ is a complicated function of $ m_A $ and $ T $, but is simply proportional to the square of the parameter $ \epsilon $.
+Pulling that out of the expression gives a constraint
 \beq
@@
 \beq 
-\epsilon \le \sqrt{\frac{4.1 * 10^{37} MeV^2}{I_A(m_A, T)}} 
+\epsilon \le \sqrt{\frac{4.1 \times 10^{37} MeV^2}{I_A(m_A, T)}} 
 \eeq 
@@
 \subsection{Decay limit}
-The constraint from the streaming limit above provides an upper bound on the allowed coupling and lower bound on the excluded coupling by considering purely production.
-Naively it might be expected that this suffices, that all higher couplings are excluded.
-However, in order to function as a cooling channel, obviously enough of the produced light gauge bosons must escape the supernova.
-As the coupling increases, so do processes that prevent this,and so the excluded region has an upper bound, above which the luminosity again drops below the neutrino luminosity.
+The constraint from the streaming limit above provides an upper bound on the allowed coupling (or lower bound on the excluded coupling) by considering the production on the $A'$.
+Naively it might be expected that this suffices, in that all higher couplings are excluded.
+However, in order to function as a cooling channel, enough of the produced dark gauge bosons must escape the supernova.
+As the coupling increases, so do processes that prevent the escape, and so the excluded region has an upper bound, above which the luminosity again drops below the neutrino luminosity.
 The first such limit may be found by considering decay of the dark bosons into Standard Model particles, and assuming that these SM particles are trapped in the supernova core and contribute nothing to the cooling.
@@
 \eeq
-and so the fraction escaping the supernova is given by 
+and so the fraction escaping the supernova before decaying is given by 
 \beq
@@
 The limit is derived from the same equation, with the only complication being the fact that $ I_A $ is now a function of $ \epsilon $, in addition to $ m_A, T $.
-This makes the numerical calculation slightly more complicated, but otherwise changes nothing of importance.
+This makes the numerical calculation slightly more complicated, but otherwise changes nothing of importance, with now the constraint a transcendental equation,
 \beq
@@
 The second constraint that produces an upper bound on the excluded region comes from considering trapping of dark bosons within the supernova.
-With a large enough coupling, the new particles will thermalize and then be emitted from a spherical shell.
+With a large enough coupling, the new particles will thermalize and then they will be emitted from a spherical shell.
 In this case the luminosity is given simply by the Steffan-Boltzmann law
@@
 where $ r $ is now the radius of the emitting shell and $ T_A $ its temperature.
-These must typically be calculated, but for $ r $ it is safe to assume a value of 10 km, since the density of the supernova drops drastically around that point.
+We can estimate $ r = 10$ km, since the density of the supernova drops drastically around that point.
 After taking that value for r, the bound on the luminosity translates into a bound on $ T_A $
 \beq
-T_A \le 9.586 MeV.
+T_A \le 9.586\rm\ MeV.
 \eeq
-That bound can then be translated into the desired bound on the coupling as a function of mass by assuming that the particles are emitted from an optical depth $ \tau = \frac{2}{3} $, and finding the temperature that corresponds to that optical depth.
+That bound can then be translated into the desired bound on the coupling as a function of mass by assuming that the particles are emitted from an optical depth $ \tau = 2/3 $, and finding the temperature that corresponds to that optical depth.
 This is a somewhat involved calculation.
-First, one needs a model for the density and temperature in the supernova. Following \cite{dent}, we assume 
+First, one needs a model for the density and temperature in the supernova. Following \cite{Dent:2012mx}, we assume 
 \bea
-\rho &=& \rho_p (\frac{R}{r})^2,\\
-T &=& T_R (\frac{R}{r})^{n/3},
+\rho &=& \rho_p \left(\frac{R}{r}\right)^2,\\
+T &=& T_R \left(\frac{R}{r}\right)^{n/3},
 \eea
-with $  \rho_p  = 3*10^{14} g/cm^3, T_R = 30$ MeV, and taking $ n = 5 $. The optical depth is given by 
+with $  \rho_p  = 3\times10^{14}\ {\rm g/cm}^3, T_R = 30$ MeV, and taking $ n = 5 $. The optical depth is given by 
 \beq
@@
 This then allows the calculation of $ \kappa_x $.
-The inverse opacities for the pn and pp processes add, giving the total opacity $ \kappa^{-1} = \kappa_{pp}^{-1} + \kappa_{pn}^{-1} $
+The inverse opacities for the $pn$ and $pp$ processes add, giving the total opacity $ \kappa^{-1} = \kappa_{pp}^{-1} + \kappa_{pn}^{-1} $
 

### 2016-08-01 draft.tex
modified equations to make easier to read
did some on results

@@
 \beq
-e^{\frac{r_{decay}}{l}} = e^{\frac{r_{decay} N_{eff} m_A^2 \epsilon^2}{3 E_A}}.
+e^{r_{decay}/l} = e^{r_{decay} N_{eff} m_A^2 \epsilon^2/(3 E_A)}.
 \eeq
@@
 \beq
-\epsilon \le \sqrt{\frac{4.1 * 10^{37} MeV^2}{I_A(m_A, T, \epsilon)}}.
+\epsilon \le \sqrt{\frac{4.1 \times 10^{37} MeV^2}{I_A(m_A, T, \epsilon)}}.
 \eeq
@@
 
+Both approaches produce constraints that are significantly weaker than the previous work, and that largely reproduce constraints already obtained from beam dump experiments.
+The squared matrix element obtained from the full one-pion-exchange in the end agrees quite well with that obtained using the approximations appropriate for axionic calculations; the reduction in the bremsstrahlung rate apparently results from significant changes to the phase space when the exact kinematics are used.
+The effective field theory calculation weakens the constraint by a further order of magnitude, and this difference between the EFT and OPE constraints results only from a difference in the matrix element calculated from each.
+It's well-known that the OPE model ignores effects related to chiral symmetry, and these evidently serve to reduce the bremsstrahlung rate considerably.
+Although there is some question as to the applicability of the simple pionless EFT at the highest masses considered, but at that point even significant deviation would not change the overall conclusion.
+
 \section{Discussion/Conclusion}

### 2016-08-30 draft.tex
Add files via upload

@@
 \usepackage{slashed}
+\usepackage{epstopdf}
 
@@
 \bea
-\rho &=& \rho_p \left(\frac{R}{r}\right)^2,\\
-T &=& T_R \left(\frac{R}{r}\right)^{n/3},
+\rho &=& \rho_p \left(\frac{R}{r}\right)^n,\\
+T &=& T_R \left(\frac{\rho(r)}{\rho_R}\right)^{1/3},
 \eea
@@
 
-Having obtained an expression for $ \kappa $, we can now find the optical depth
-	[note to self: rework the steps here; too confusing]
-and the bound on the coupling is finally found by requiring  $ \tau_R(\epsilon,m_A) \le 2/3 $
+Having obtained an expression for $ \kappa $, we can now find the optical depth as follows: define a new quantity $ \tau_R = \kappa_R \rho_R R $. We then have 
+\beq \kappa \rho R = \tau_R (\frac{\rho}{\rho_R})^2 (\frac{T_R}{T})^{3/2}  \eeq
+This is combined with the expressions for the density and temperature as a function of r and plugged in to the integral expression for the optical depth to obtain 
+\bea \tau_x &=& \int_{r_x}^{\infty} \tau_R (\frac{R}{r})^{3n/2} \\
+ &=& \frac{\tau_r}{\frac{3n}{2}-1} (\frac{T_A}{T_R})^{(9/2-3/n)} \eea
+and the bound on the coupling is finally found by requiring  $ \tau_x(\epsilon,m_A) \le 2/3 $
 
@@
 
+The calculation is dependent on a number of constants.
+We chose the following values as roughly typical of supernovae: T, the temperature of the supernova core, was set to 30 MeV; r, the radius of the supernova core, to 1 km; $ R $, the distance at which decay products are trapped, to 10 km; $ \mathcal{L} $, the luminosity bound, to $ 10^{53} erg/s $; and $ \n_b $, the baryon number density in the supernova interior, to $ 1.79*10^{38} cm^{-3} $.
+
 \section{Results}
+
+\begin{figure}[h!]
+\includegraphics[height=9cm]{ope_bound.eps}
+\caption{CAPTION}
+\end{figure}
 

### 2016-09-30 draft.tex
Added figures at last

@@
 \section{Computational details}
+	simple energy loss calculation
+
 	The process we are considering, the bremsstrahlung of a dark photon from nucleon-nucleon scattering, is similar in many ways to the classic calculation of axion emission from supernova cooling.
@@
 \subsection{Bremsstrahlung amplitude calculation}
-	 There are two processes to consider: the $pp$ scattering with the bremsstrahlung of the dark photon, $ p+p \rightarrow p+p+A$, and the $pn$ scattering with bremsstrahlung, $ p+n \rightarrow p+n+A\ $.
+	 There are two processes to consider: the $pp$ scattering with the bremsstrahlung of the dark photon off the proton, $ p+p \rightarrow p+p+A$, and the $pn$ scattering with bremsstrahlung off the proton or the charged pion, $ p+n \rightarrow p+n+A\ $.
 For the $pp$ case there are eight tree-level diagrams, with the emission of the $A'$ from each of the external legs, as shown in Fig.
-, while for the $pn$ case there are five diagrams, including when the $A'$ is emitted from the exchanged charged pion, as shown in Fig.
+, while for the $pn$ case there are five diagrams, including when the $A'$ is emitted from the exchanged pion, as shown in Fig.
 .
 
-The calculation of these diagrams are straightforward, using standard Feynman rules.
-Each of the $p-p-\pi $ vertices contribute a factor of $g_{pp}$,  the pseudoscalar pion-nucleon coupling.
-$f_{pp}$, the pseudovector pion-nucleon coupling, is related by $g_{pp} = \frac{2M_N}{m_\pi} f_{pp} $.
-The $ p-p-A' $ vertex contributes $e\epsilon \gamma_\mu$, where $\epsilon$ is the mixing strength between the photon and dark photon.
-Labeling the contributions according to the Feynman diagrams in Fig.
-, the matrix elements are
-\bea
-M_1 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
-	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed{\varepsilon} u(p_1),\\
-M_2 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
-	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p3) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed \varepsilon  u(p_1), \\
-M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
-	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \varepsilon  u(p_2), \\
-M_4 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
-	 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \varepsilon  u(p_2), \\
-M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
-			 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \slashed{\varepsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
-M_6 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
-		 		 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \slashed{\varepsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
-M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
-		 		 }  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \slashed{\varepsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),\\
-M_8 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
-		}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \slashed{\varepsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),
-\eea
-where the exchange momenta are defined by $ k = p_2-p_4 $ and $ l = p_2-p_3 $, and the dark photon's polarization is given by $\varepsilon$.
-Note that these matrix elements agree with Ref.~\cite{Dent:2012mx}.
-
-At this point the calculation diverges from the axion bremsstrahlung calculation, since in the kinematic region of interest for supernova explosions, the mass of the $A'$ boson is not necessarily negligible.
+The calculation of these diagrams is straightforward, and is described in the appendix.
+Having obtained the diagrams the calculation diverges from the axion bremsstrahlung calculation, since in the kinematic region of interest for supernova explosions the mass of the $A'$ boson is not necessarily negligible.
 The kinematic relations are thus \bea
@@
 
+\appendix
+\section{Bremsstrahlung diagrams}
+	Each of the $p-p-\pi $ vertices contribute a factor of $g_{pp}$,  the pseudoscalar pion-nucleon coupling.
+$f_{pp}$, the pseudovector pion-nucleon coupling, is related by $g_{pp} = \frac{2M_N}{m_\pi} f_{pp} $.
+The $ p-p-A' $ vertex contributes $e\epsilon \gamma_\mu$, where $\epsilon$ is the mixing strength between the photon and dark photon.
+Labeling the contributions according to the Feynman diagrams in Fig.
+, the matrix elements are
+	\bea
+	M_1 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
+	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed{\varepsilon} u(p_1),\\
+	M_2 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
+	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p3) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed \varepsilon  u(p_1), \\
+	M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
+	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \varepsilon  u(p_2), \\
+	M_4 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
+	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \varepsilon  u(p_2), \\
+	M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
+	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \slashed{\varepsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
+	M_6 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
+	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \slashed{\varepsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
+	M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
+	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \slashed{\varepsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),\\
+	M_8 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
+	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \slashed{\varepsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),
+	\eea
+	where the exchange momenta are defined by $ k = p_2-p_4 $ and $ l = p_2-p_3 $, and the dark photon's polarization is given by $\varepsilon$. 
+	For $pn$ scattering, four of the diagrams are simply the $ M_1, M_2, M_3, M_4 $ given above, with the only new Feynman diagram coming from bremsstrahlung off the internal pi, resulting in  
+	 \beq
+	 M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \epsilon}{l^2-m_\pi^2
+	 }  \frac{1}{(l-q_a)^2 - m_\pi^2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) u(p_2) (q_a - 2l)\cdot \varepsilon
+	 \eeq
+	 Note that these matrix elements agree with Ref.~\cite{Dent:2012mx}.
 \acknowledgments

### 2016-09-30 draft.tex
added results

@@
 \section{Computational details}
-	simple energy loss calculation
 
@@
 \eea
-Unfortunately, with these relations it does not seem to be possible to simplify the amplitude into an analytically usable form without making unjustified approximations, and so the final expression for the spin-averaged squared matrix element, $ \mathcal{M}^2_{pp}$, contains some two hundred and fifty terms, and thus we do not reproduce that result here.\footnote{At this point we diverge from Ref.~\cite{Dent:2012mx} for two reasons.
+Unfortunately, with these relations it does not seem to be possible to simplify the amplitude into an analytically usable form without making unjustified approximations, and so the final expression for the spin-averaged squared matrix element, $ \mathcal{M}^2_{pp}$, contains some two hundred and fifty terms, and thus we do not reproduce that result here.
+The pn calculation likewise results in a very large and unwieldy expression for $ \mathcal{M}^2_{pn}$.
+\footnote{At this point we diverge from Ref.~\cite{Dent:2012mx} for two reasons.
 One, they use the kinematics as if the $A'$ were massless, as in the axion calculation, and independent of that choice, their squared matrix element does not respect the correct exchange symmetry, as can be seen by inspection of their Eq.
 (A.3), with their claim that only the coefficient $C_k$ appearing in that equation is nonzero.}
-
- For the $pn$ scattering, the calculation proceeds similarly, with the only new Feynman diagram coming from bremsstrahlung off the internal pi, resulting in  
- \beq
- M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \epsilon}{l^2-m_\pi^2
- 	 }  \frac{1}{(l-q_a)^2 - m_\pi^2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) u(p_2) (q_a - 2l)\cdot \varepsilon
-\eeq
-Again, due to the more complicated kinematics due to the non-negligible mass of the $A'$, the resulting squared amplitude, $ \mathcal{M}^2_{pn}$, is too unwieldy to reproduce here.
 
@@
 The actual quantity of interest therefore is the rate of energy emission through dark bosons.
-From the spin-summed squared amplitudes already given, this is obtained by integrating over the phase space, and adding a factor of energy
+From the spin-summed squared amplitudes already found, this is obtained by integrating over the phase space, and adding a factor of energy of the emitted particle.
 \beq
@@
 The second constraint that produces an upper bound on the excluded region comes from considering trapping of dark bosons within the supernova.
-With a large enough coupling, the new particles will thermalize and then they will be emitted from a spherical shell.
+With a large enough coupling, the new particles will thermalize and then will be emitted from a spherical shell.
 In this case the luminosity is given simply by the Steffan-Boltzmann law
@@
 \begin{figure}[h!]
-\includegraphics[height=9cm]{ope_bound.eps}
-\caption{CAPTION}
+\includegraphics[height=9cm]{stages.eps}
+\caption{The changes in the bounds generated as each stage of the calculation departs from Ref.~\cite{Dent:2012mx}. Interestingly the kinematics have apparently relatively little effect.}
 \end{figure}
 
-Both approaches produce constraints that are significantly weaker than the previous work, and that largely reproduce constraints already obtained from beam dump experiments.
-The squared matrix element obtained from the full one-pion-exchange in the end agrees quite well with that obtained using the approximations appropriate for axionic calculations; the reduction in the bremsstrahlung rate apparently results from significant changes to the phase space when the exact kinematics are used.
-The effective field theory calculation weakens the constraint by a further order of magnitude, and this difference between the EFT and OPE constraints results only from a difference in the matrix element calculated from each.
-It's well-known that the OPE model ignores effects related to chiral symmetry, and these evidently serve to reduce the bremsstrahlung rate considerably.
-Although there is some question as to the applicability of the simple pionless EFT at the highest masses considered, but at that point even significant deviation would not change the overall conclusion.
+\begin{figure}[h!]
+	\includegraphics[height=9cm]{endtoend.png}
+	\caption{A comparison of the final result for the excluded region with the result from Ref.~\cite{Dent:2012mx}.
+The excluded region is clearly significantly less restrictive, and opens up the region of parameter space for $\epsilon \approx  1e-8-9 $.}
+\end{figure}
 
 \section{Discussion/Conclusion}	
+	The revised approach produce constraints that are significantly weaker than the previous work, and that largely reproduce constraints already obtained from beam dump experiments.
 
@@
 	where the exchange momenta are defined by $ k = p_2-p_4 $ and $ l = p_2-p_3 $, and the dark photon's polarization is given by $\varepsilon$. 
-	For $pn$ scattering, four of the diagrams are simply the $ M_1, M_2, M_3, M_4 $ given above, with the only new Feynman diagram coming from bremsstrahlung off the internal pi, resulting in  
+	For $pn$ scattering, four of the diagrams are simply the same as those given above. The only new Feynman diagram comes from bremsstrahlung off the internal pion, and results in  
 	 \beq

### 2016-11-08 draft.tex
Trivial change to title.
I'm an idiot

@@
 \section{Introduction}
+
+This calculation was done in Ref.~\cite{Dent:2012mx} Using the one-pion exchange model of nucleon-nucleon interactions\footnote{There is also some question as to the applicability of this approach in this regime.
+Pionless effective field theory techniques developed for low-energy nucleons might provide a more accurate answer; this may be considered in a later paper} they largely followed the form of the calculation of the axionic bremsstrahlung rate [brinkmann/turner/iwamoto], in which the axion is taken to be massless.
+Considering the energy scales in the problem, this is clearly a reasonable approximation when dealing with axion masses on the order of $ 10^-3 $ eV; it is less clear that it is still appropriate when dealing with dark photon masses on the order of 10-100 MeV.
+We therefore reproduce the calculation without making that simplifying assumption, and see if it has an effect on the result.
+We find that it does indeed quite dramatically change the excluded region in $ \eps-m_A $ space, increasing the lower bound by some two orders of magnitude and opening up a considerable portion of the parameter space.
 

### 2016-12-07 draft.tex
Resolved conflict, added title.
Very minor additions to intro, but I am working on it.

@@
-\documentclass[nofootinbib,aps,prd,preprint,superscriptaddress]{revtex4}
+\documentclass[nofootinbib,prd,superscriptaddress,twocolumn]{revtex4}
 \usepackage{amsmath,graphicx,hyperref}
@@
 
-\title{Title?}
+\title{Updated Constraints on Self-Interacting Dark Matter from Supernova 1987A}
 
@@
 \section{Introduction}
+
+Dark matter that interacts with itself through a large elastic scattering cross section 
+(on the order of $\sigma \sim 10^{-24}\, \mathrm{cm}^2$) 
+has been considered for numerous reasons over the past several decades.
 

### 2017-01-05 draft.tex
Added two paragraphs to the introduction.

@@
 \usepackage{epstopdf}
+\usepackage{color}
+\usepackage[dvipsnames]{xcolor}
 
@@
 
+%--- journals
+\newcommand{\physrep}{Phys. Reports}
+\newcommand{\mnras}{Mon. Not. R. Astron. Soc.}
+\newcommand{\apjl}{Astrophys. J. Lett.}
+\newcommand{\jcap}{J. Cosmol. Astropart. Phys.}
+
+%--- for comments
+\newcommand{\arz}[1]{{{\bf{\color{BrickRed}[ARZ: #1]}}}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibliographystyle{apsrev}
 
@@
 
-Dark matter that interacts with itself through a large elastic scattering cross section 
-(on the order of $\sigma \sim 10^{-24}\, \mathrm{cm}^2$) 
-has been considered for numerous reasons over the past several decades.
+A nearly overwhelming preponderance of observational evidence indicates that a form of nonrelativistic, nonbaryonic, 
+dark matter constitutes the vast majority of mass in the Universe and drives the formation of cosmic structure. 
+The pace of the quest to identify the dark matter is accelerating on many fronts. Weakly-interacting massive 
+particles (WIMPs) have received the most attention as dark matter candidates (see Ref.~\cite{jungman_etal96} for a review). 
+Dark matter particles that interact with standard model particles only weakly, while interacting among themselves 
+much more strongly have been studied as an alternative to WIMP scenarios in many contexts 
+\cite{carlson_etal92,deLaix_etal95,atrio-barandela_davidson97,spergel_steinhardt00,hogan_dalcanton00,mohapatra_teplitz00,
+dave_etal01,hisano_etal04,hisano_etal05,pospelov_etal08,arkani-hamed_etal08a,lattanzi_silk08,ackerman_etal09,feng_etal09,
+kong_etal15} \arz{Need to add some more recent references here.} 
+and constraints on self-interacting dark matter (SIDM) models have been explored by many authors \cite{yoshida_etal00,gnedin_ostriker01,miralda-escude02,randall_etal08,kamionkowski_profumo08,zentner09,robertson_zentner09,pieri_etal09,spolyar_etal09,finkbeiner_etal09,
+slatyer_etal09,bramante_etal14,albuquerque_etal14,kaplinghat_etal14,chen_etal14,feng_etal16,catena_widmark16}.
+In this paper, we revisit and update astrophysical constraints on SIDM models from 
+supernova cooling, finding constraints that are considerably less restrictive than in 
+previous work. 
+\arz{Might want to add a comment about SIDM affecting small-scale structure in CDM, the satellites problems and core/cusp problems.}
 
-This calculation was done in Ref.~\cite{Dent:2012mx} Using the one-pion exchange model of nucleon-nucleon interactions\footnote{There is also some question as to the applicability of this approach in this regime.
+SIDM models in which large self-interaction cross sections are mediated by sufficiently light 
+bosons ($M \lesssim 100$~GeV) can be constrained astrophysically using supernovae, particularly 
+SN1987A. Light gauge bosons will be produced within the hot supernovae core and 
+radiated from the supernova. This non-standard energy loss mechanism can result in an energy loss rate 
+from the supernova core that is inconsistent with observations of SN1987A, analogous to the 
+classic constraint on axions \cite{raffelt96_book}. Constraints on SIDM from this mechanism 
+were already considered by \cite{dent_etal12} and \cite{rrapaj_reddy16}.
+
+This calculation was done in Ref.~\cite{dent_etal12} Using the one-pion exchange model of nucleon-nucleon interactions\footnote{There is also some question as to the applicability of this approach in this regime.
 Pionless effective field theory techniques developed for low-energy nucleons might provide a more accurate answer; this may be considered in a later paper} they largely followed the form of the calculation of the axionic bremsstrahlung rate [brinkmann/turner/iwamoto], in which the axion is taken to be massless.
@@
 The pn calculation likewise results in a very large and unwieldy expression for $ \mathcal{M}^2_{pn}$.
-\footnote{At this point we diverge from Ref.~\cite{Dent:2012mx} for two reasons.
+\footnote{At this point we diverge from Ref.~\cite{dent_etal12} for two reasons.
 One, they use the kinematics as if the $A'$ were massless, as in the axion calculation, and independent of that choice, their squared matrix element does not respect the correct exchange symmetry, as can be seen by inspection of their Eq.
@@
 This is a somewhat involved calculation.
-First, one needs a model for the density and temperature in the supernova. Following \cite{Dent:2012mx}, we assume 
+First, one needs a model for the density and temperature in the supernova. Following \cite{dent_etal12}, we assume 
 \bea
@@
 
-\begin{figure}[h!]
-\includegraphics[height=9cm]{stages.eps}
-\caption{The changes in the bounds generated as each stage of the calculation departs from Ref.~\cite{Dent:2012mx}. Interestingly the kinematics have apparently relatively little effect.}
+\begin{figure}[th]
+\includegraphics[width=9cm]{stages.eps}
+\caption{The changes in the bounds generated as each stage of the calculation departs from Ref.~\cite{dent_etal12}. Interestingly the kinematics have apparently relatively little effect.}
 \end{figure}
 
-\begin{figure}[h!]
-	\includegraphics[height=9cm]{endtoend.png}
-	\caption{A comparison of the final result for the excluded region with the result from Ref.~\cite{Dent:2012mx}.
+Let's put some text here.
+
+\begin{figure}[th]
+	\includegraphics[width=9cm]{endtoend.png}
+	\caption{A comparison of the final result for the excluded region with the result from Ref.~\cite{dent_etal12}.
 The excluded region is clearly significantly less restrictive, and opens up the region of parameter space for $\epsilon \approx  1e-8-9 $.}
@@
 	 \eeq
-	 Note that these matrix elements agree with Ref.~\cite{Dent:2012mx}.
+	 Note that these matrix elements agree with Ref.~\cite{dent_etal12}.
 \acknowledgments
@@
 
-\begin{thebibliography}{99}
-%\normalsize
-
-%\cite{Dent:2012mx}
-\bibitem{Dent:2012mx} 
-  J.~B.~Dent, F.~Ferrer and L.~M.~Krauss,
-  %``Constraints on Light Hidden Sector Gauge Bosons from Supernova Cooling,''
-  arXiv:1201.2683 [astro-ph.CO].
-  %%CITATION = ARXIV:1201.2683;%%
-  %56 citations counted in INSPIRE as of 29 Jul 2016
-
-\end{thebibliography}
+\bibliography{draft}
 

### 2017-01-05 draft.tex
Finished first draft of introduction section.

@@
 
+%------------------------- Introduction ---
 \section{Introduction}
@@
 from the supernova core that is inconsistent with observations of SN1987A, analogous to the 
-classic constraint on axions \cite{raffelt96_book}. Constraints on SIDM from this mechanism 
-were already considered by \cite{dent_etal12} and \cite{rrapaj_reddy16}.
+classic constraint on axions \cite{raffelt96_book}. This mechanism was already exploited by 
+\cite{dent_etal12} (and \cite{rrapaj_reddy16}, with a slight modification) (\arz{Cameron, add others of which you may be aware.}) 
+to constraint dark photon models of SIDM in which the self-interaction arises from a Yukawa potential and the 
+vector boson is kinetically mixed with the standard model photon.
 
-This calculation was done in Ref.~\cite{dent_etal12} Using the one-pion exchange model of nucleon-nucleon interactions\footnote{There is also some question as to the applicability of this approach in this regime.
-Pionless effective field theory techniques developed for low-energy nucleons might provide a more accurate answer; this may be considered in a later paper} they largely followed the form of the calculation of the axionic bremsstrahlung rate [brinkmann/turner/iwamoto], in which the axion is taken to be massless.
-Considering the energy scales in the problem, this is clearly a reasonable approximation when dealing with axion masses on the order of $ 10^-3 $ eV; it is less clear that it is still appropriate when dealing with dark photon masses on the order of 10-100 MeV.
-We therefore reproduce the calculation without making that simplifying assumption, and see if it has an effect on the result.
-We find that it does indeed quite dramatically change the excluded region in $ \eps-m_A $ space, increasing the lower bound by some two orders of magnitude and opening up a considerable portion of the parameter space.
+As we mentioned above, we find SN1987A constraints on dark photon SIDM models that are considerably different 
+from those of \cite{dent_etal12}. If correct, this has important consequences. The Snowmass white paper by Kaplinghat, 
+Tulin, and Yu \cite{kaplinghat_etal13_whitepaper} nicely summarizes a variety of constraints on dark photon models of 
+SIDM. One point that is clear from Ref.~\cite{kaplinghat_etal13_whitepaper} is that there is only a narrow range of 
+viable photon mixing parameters that can lead to production of SIDM in the early universe, while evading all constraints, 
+including the constraint of \cite{dent_etal12}. Our results suggest that the SN1987A constraints from Ref.~\cite{dent_etal12} 
+are too restrictive. The less restrictive constraints that we quote open up a space of unrestricted mixing parameters that 
+ranges over two orders of magnitude. Interestingly, the parameter space opened by our updated constraints corresponds to a 
+space that may a significant impact on cosmological structure formation, particularly the structures of dark matter halos and galaxies.
 
+The discrepancy between our result and that of Ref.~\cite{dent_etal12} is due to several factors. First, it is straightforward to 
+demonstrate that the kinematical relationships in given in Appendix A of Ref.~\cite{dent_etal12} are incorrect. Second, the 
+squared matrix elements given in Eq.~(A3) and Eq.~(C18) of Ref.~\cite{dent_etal12} are incorrect. Our squared matrix elements 
+are considerably more complicated. There appear to be a number of errors that led to the incorrect squared matrix elements in 
+Ref.~\cite{dent_etal12}. At the very least, these errors include simplification using the incorrect kinematics and neglect of the 
+mass of the gauge boson (which, while legitimate for the $\sim$meV-mass axion, is not justified in this context). Additional 
+discrepancies must be present, the causes of which are not apparent from the exposition, 
+because the squared matrix elements in Eq.~(A3) and Eq.~(C18) of Ref.~\cite{dent_etal12} 
+do not obey the correct symmetries under interchange of the incoming or outgoing baryon momenta. 
+Given these errors, we suggest that our results should supercede these previously-published constraints.
+
+The remainder of this paper is organized as follows. In Section~\ref{section:model}, we discuss 
+dark photon models. We describe our calculation of SN1987A constraints on SIDM in 
+Section~\ref{section:computational} and present our primary results in Section~\ref{section:results}. 
+We summarize our work and draw conclusions in Section~\ref{section:conclusions}.
+
+%---- Model Details
+\section{Dark Photon Model of SIDM}
+\label{section:model}
+
+%----- Computational Details
 \section{Computational details}
+\label{section:computational}
 
@@
 
-\section{Computational details}
+\subsection{Phase Space Integration}
 In every case calculating the bound requires integrating an expression involving the long and complicated Bremsstrahlung amplitude, which unfortunately could not be done analytically without making unjustified approximations.
@@
 
+%-------------------- RESULTS
 \section{Results}
+\label{section:results}
 
@@
 
-\section{Discussion/Conclusion}	
+%--------------------------- CONCLUSIONS
+\section{Discussion and Conclusions}
+\label{section:conclusions}
+
 	The revised approach produce constraints that are significantly weaker than the previous work, and that largely reproduce constraints already obtained from beam dump experiments.
 
+%------------ APPENDIX
 \appendix

### 2017-01-05 draft.tex
Wrote a brief, new section 2 that serves to introduce our notation.

@@
 \cite{dent_etal12} (and \cite{rrapaj_reddy16}, with a slight modification) (\arz{Cameron, add others of which you may be aware.}) 
-to constraint dark photon models of SIDM in which the self-interaction arises from a Yukawa potential and the 
+to constraint dark electromagnetism models of SIDM in which the self-interaction arises from a Yukawa potential and the 
 vector boson is kinetically mixed with the standard model photon.
@@
 from those of \cite{dent_etal12}. If correct, this has important consequences. The Snowmass white paper by Kaplinghat, 
-Tulin, and Yu \cite{kaplinghat_etal13_whitepaper} nicely summarizes a variety of constraints on dark photon models of 
+Tulin, and Yu \cite{kaplinghat_etal13_whitepaper} nicely summarizes a variety of constraints on dark electromagnetism models of 
 SIDM. One point that is clear from Ref.~\cite{kaplinghat_etal13_whitepaper} is that there is only a narrow range of 
@@
 \label{section:model}
+
+We consider constraints on SIDM specifically within the context of dark electromagnetism models. 
+Dark electromagnetism models are models in which a hidden, dark, sector contains a broken U(1)$'$ 
+symmetry and the U(1)$'$ gauge boson is kinetically mixed with the standard model photon. For the 
+purposes of this study, this is important because it demands that the Lagrangian contains terms such as 
+%
+\begin{equation}
+\mathcal{L}_{\mathrm{int}} = g_{\chi} \bar{\chi} \, \tilde{\slashed{A'} } \chi + q \bar{f}\, \tilde{\slashed{A} } f, 
+\end{equation}
+%
+where $\chi$ is the dark matter, $g_{\chi}$ is the dark coupling, $\tilde{A}'$ is the dark gauge boson, 
+$f$ is a standard model fermion of charge $q$, and $\tilde{A}$ is the standard model gauge boson. 
+The kinetic mixing causes the $\tilde{A}$ to be an admixture of the massless photon, $A$, and 
+the dark photon, $A'$ of mass $m_{\mathrm{A'}}$, so that the dark matter particles are coupled to the standard model 
+fermions with a coupling constant $\epsilon q$, where $\epsilon$ is the kinetic mixing parameter. 
+The first term in this interaction gives rise to the dark matter self-interactions.
+
+Dark gauge bosons are produced in astrophysical environments such as supernova 
+cores via brehmsstrahlung off of standard model particles. This brehmsstrahlung 
+occurs through the $\epsilon q$ coupling. The rate of brehmsstrahlung 
+also depends upon the mass of the $A'$. Consequently, 
+supernova cooling can constrain the mixing $\epsilon$ as a function of 
+$m_{A'}$ for such models and producing such a constraint is the 
+primary aim of this paper.
 
@@
 \includegraphics[width=9cm]{stages.eps}
-\caption{The changes in the bounds generated as each stage of the calculation departs from Ref.~\cite{dent_etal12}. Interestingly the kinematics have apparently relatively little effect.}
+\caption{The changes in the bounds generated as each stage of the calculation departs from Ref.~\cite{dent_etal12}. Interestingly the kinematics have apparently relatively little effect.
+\arz{Cameron, several to-do items for this figure. On the y-axis, the symbol should be "$\epsilon$" rather than 
+"e". Can we write numbers as "$10^{-9}$" rather than "1e-09" and so on? Can we make the axis labels and 
+tick mark labels larger? Can you make all of the lines thicker? Can you make each of the four lines a distinct color?}
+}
 \end{figure}
@@
 	\caption{A comparison of the final result for the excluded region with the result from Ref.~\cite{dent_etal12}.
-The excluded region is clearly significantly less restrictive, and opens up the region of parameter space for $\epsilon \approx  1e-8-9 $.}
+The excluded region is clearly significantly less restrictive, and opens up the region of parameter space for $\epsilon \approx  1e-8-9 $.
+\arz{Cameron, some similar comments as for Figure 1. Can we write numbers as "$10^{-9}$" rather 
+than "1e-09" and so on? Can we make the axis labels and tick mark labels larger?}	
+	}
 \end{figure}

### 2017-01-06 draft.tex
Some minor corrections. Added comments about needed citations.
Some minor edits for completeness.

@@
 
-\newcommand{\eps}{\epsilon} 
+\newcommand{\eps}{\varepsilon} 
 \newcommand{\veps}{\varepsilon}
@@
 
+\arz{Need to add citations to many of the Feng et al. papers here.}
 We consider constraints on SIDM specifically within the context of dark electromagnetism models. 
@@
 \begin{equation}
-\mathcal{L}_{\mathrm{int}} = g_{\chi} \bar{\chi} \, \tilde{\slashed{A'} } \chi + q \bar{f}\, \tilde{\slashed{A} } f, 
+\mathcal{L}_{\mathrm{int}} = g_{\chi} \bar{\chi} \, \widetilde{\slashed{A'}} \chi + q \bar{f}\, \widetilde{\slashed{A}} f, 
 \end{equation}
 %
-where $\chi$ is the dark matter, $g_{\chi}$ is the dark coupling, $\tilde{A}'$ is the dark gauge boson, 
-$f$ is a standard model fermion of charge $q$, and $\tilde{A}$ is the standard model gauge boson. 
-The kinetic mixing causes the $\tilde{A}$ to be an admixture of the massless photon, $A$, and 
-the dark photon, $A'$ of mass $m_{\mathrm{A'}}$, so that the dark matter particles are coupled to the standard model 
-fermions with a coupling constant $\epsilon q$, where $\epsilon$ is the kinetic mixing parameter. 
-The first term in this interaction gives rise to the dark matter self-interactions.
+where $\chi$ is the dark matter, $g_{\chi}$ is the dark coupling, $\widetilde{A'}$ is the dark gauge boson, 
+$f$ is a standard model fermion of charge $q$, and $\widetilde{A}$ is the standard model gauge boson. 
+The kinetic mixing, through a term 
+$\frac{1}{2}\frac{\varepsilon}{\sqrt{1+\varepsilon^2}}\, \widetilde{F}_{\mu \nu}\widetilde{F}'^{\mu \nu}$ 
+in the Lagrangian causes the $\widetilde{A}$ to be an admixture of the massless photon $A$, 
+and the dark photon $A'$, 
+of mass $m_{\mathrm{A'}} = m_{\mathrm{\widetilde{A}'}} \sqrt{1 + \varepsilon^2} \simeq m_{\widetilde{A}'}$ because 
+the viable parameter range has $\varepsilon \ll 1$. The dark matter particles are thereby coupled 
+to the standard model fermions with a coupling constant $\varepsilon q$, 
+where $\varepsilon$ is the kinetic mixing parameter. The first term in this 
+interaction Lagrangian gives rise to the dark matter self-interactions.
 
 Dark gauge bosons are produced in astrophysical environments such as supernova 
-cores via brehmsstrahlung off of standard model particles. This brehmsstrahlung 
-occurs through the $\epsilon q$ coupling. The rate of brehmsstrahlung 
-also depends upon the mass of the $A'$. Consequently, 
-supernova cooling can constrain the mixing $\epsilon$ as a function of 
-$m_{A'}$ for such models and producing such a constraint is the 
+cores primarily via brehmsstrahlung off of standard model particles. This brehmsstrahlung 
+occurs through the $\varepsilon q$ coupling to charged standard model particles, 
+in this  particular case the proton and pion. The rate of brehmsstrahlung 
+depends upon both $\varepsilon$ and the mass of the $A'$. Consequently, 
+supernova cooling can constrain the mixing $\varepsilon$ as a function of 
+$m_{A'}$ for such models. Delineating such a constraint is the 
 primary aim of this paper.
@@
 To obtain the dark gauge boson luminosity, it is assumed that production takes place in a core volume $V$ of radius 1 km, giving $ \mathcal{L}_A = V(Q_{pp} + Q_{pn}) $.
-The luminosity $\mathcal{L}_A $ is a complicated function of $ m_A $ and $ T $, but is simply proportional to the square of the parameter $ \epsilon $.
+The luminosity $\mathcal{L}_A $ is a complicated function of $ m_A $ and $ T $, but is simply proportional to the square of the parameter $ \varepsilon $.
 Pulling that out of the expression gives a constraint
 \beq
-\epsilon^2 I_A(m_A, T) \le \mathcal{L}_\nu
+\varepsilon^2 I_A(m_A, T) \le \mathcal{L}_\nu
 \eeq
@@
 \beq 
-\epsilon \le \sqrt{\frac{4.1 \times 10^{37} MeV^2}{I_A(m_A, T)}} 
+\varepsilon \le \sqrt{\frac{4.1 \times 10^{37} MeV^2}{I_A(m_A, T)}} 
 \eeq 
@@
 \beq
-l = \frac{3 E_{A}}{N_{eff} m_A^2 \epsilon^2},
+l = \frac{3 E_{A}}{N_{eff} m_A^2 \varepsilon^2},
 \eeq
@@
 \beq
-e^{r_{decay}/l} = e^{r_{decay} N_{eff} m_A^2 \epsilon^2/(3 E_A)}.
+e^{r_{decay}/l} = e^{r_{decay} N_{eff} m_A^2 \varepsilon^2/(3 E_A)}.
 \eeq
 To take this into account, the above exponential factor is simply appended to the phase space integrand, and the calculation then proceeds as before.
-The limit is derived from the same equation, with the only complication being the fact that $ I_A $ is now a function of $ \epsilon $, in addition to $ m_A, T $.
+The limit is derived from the same equation, with the only complication being the fact that $ I_A $ is now a function of $ \varepsilon $, in addition to $ m_A, T $.
 This makes the numerical calculation slightly more complicated, but otherwise changes nothing of importance, with now the constraint a transcendental equation,
 \beq
-\epsilon \le \sqrt{\frac{4.1 \times 10^{37} MeV^2}{I_A(m_A, T, \epsilon)}}.
+\varepsilon \le \sqrt{\frac{4.1 \times 10^{37} MeV^2}{I_A(m_A, T, \varepsilon)}}.
 \eeq
@@
  &=& \frac{\tau_r}{\frac{3n}{2}-1} (\frac{T_A}{T_R})^{(9/2-3/n)} \eea
-and the bound on the coupling is finally found by requiring  $ \tau_x(\epsilon,m_A) \le 2/3 $
+and the bound on the coupling is finally found by requiring  $ \tau_x(\varepsilon,m_A) \le 2/3 $
 
@@
 Once the integration is complete the calculation of the trapping and streaming limits is a straightforward application of the equations previously derived, and proceeded as outlined above.
-The decay limit is somewhat harder, since $ \epsilon $ appears on both sides of the equation.
-Again we employed an unsubtle approach to solving the problem: $ \epsilon $ was set to an arbitrary value where the constraint was satisfied, and then iteratively reduced until the constraint was no longer satisfied.
-This obviously introduces another source of error, but with a sufficiently small interval in $ \epsilon $ this is negligible.
+The decay limit is somewhat harder, since $ \varepsilon $ appears on both sides of the equation.
+Again we employed an unsubtle approach to solving the problem: $ \varepsilon $ was set to an arbitrary value where the constraint was satisfied, and then iteratively reduced until the constraint was no longer satisfied.
+This obviously introduces another source of error, but with a sufficiently small interval in $ \varepsilon $ this is negligible.
 The one further slight complication is that at after a certain value of $ M_A $ the decay limit rapidly goes to zero, at which point the procedure was terminated.
@@
 \caption{The changes in the bounds generated as each stage of the calculation departs from Ref.~\cite{dent_etal12}. Interestingly the kinematics have apparently relatively little effect.
-\arz{Cameron, several to-do items for this figure. On the y-axis, the symbol should be "$\epsilon$" rather than 
+\arz{Cameron, several to-do items for this figure. On the y-axis, the symbol should be "$\varepsilon$" rather than 
 "e". Can we write numbers as "$10^{-9}$" rather than "1e-09" and so on? Can we make the axis labels and 
@@
 	\caption{A comparison of the final result for the excluded region with the result from Ref.~\cite{dent_etal12}.
-The excluded region is clearly significantly less restrictive, and opens up the region of parameter space for $\epsilon \approx  1e-8-9 $.
+The excluded region is clearly significantly less restrictive, and opens up the region of parameter space for $\varepsilon \approx  1e-8-9 $.
 \arz{Cameron, some similar comments as for Figure 1. Can we write numbers as "$10^{-9}$" rather 
@@
 $f_{pp}$, the pseudovector pion-nucleon coupling, is related by $g_{pp} = \frac{2M_N}{m_\pi} f_{pp} $.
-The $ p-p-A' $ vertex contributes $e\epsilon \gamma_\mu$, where $\epsilon$ is the mixing strength between the photon and dark photon.
+The $ p-p-A' $ vertex contributes $e\varepsilon \gamma_\mu$, where $\varepsilon$ is the mixing strength between the photon and dark photon.
 Labeling the contributions according to the Feynman diagrams in Fig.
@@
 	\bea
-	M_1 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
+	M_1 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2
 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed{\varepsilon} u(p_1),\\
-	M_2 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
+	M_2 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2
 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p3) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed \varepsilon  u(p_1), \\
-	M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
+	M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2
 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \varepsilon  u(p_2), \\
-	M_4 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
+	M_4 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2
 	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \varepsilon  u(p_2), \\
-	M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
+	M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2
 	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \slashed{\varepsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
-	M_6 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
+	M_6 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2
 	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \slashed{\varepsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
-	M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
+	M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2
 	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \slashed{\varepsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),\\
-	M_8 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
+	M_8 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2
 	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \slashed{\varepsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),
@@
 	 \beq
-	 M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \epsilon}{l^2-m_\pi^2
+	 M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \varepsilon}{l^2-m_\pi^2
 	 }  \frac{1}{(l-q_a)^2 - m_\pi^2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) u(p_2) (q_a - 2l)\cdot \varepsilon

### 2017-01-06 draft.tex
Some additions to the Methods section.

@@
 \newcommand{\as}{\alpha_s}
+\newcommand{\qa}{q_{A'}}
 
@@
 %----- Computational Details
-\section{Computational details}
+\section{Methods}
 \label{section:computational}
 
-	The process we are considering, the bremsstrahlung of a dark photon from nucleon-nucleon scattering, is similar in many ways to the classic calculation of axion emission from supernova cooling.
-The differences arise due to the mass of the dark photon, which can be on the order of the temperature of the supernova.
-This leads to different kinematics compared to the axion case.
-However, the calculation roughly follows the analogous calculation for axions, as laid out by Raffelt, which we briefly review below.
-As in the classical axion calculation, we will use the one-pion exchange (OPE) approximation.
+We aim to estimate the rate of energy loss from the core of a supernova from $A'$ brehmsstrahlung 
+during nucleon-nucleon interactions. The calculation is analogous to the well-known estimate of axion 
+emission from supernova cores described in Ref.~\cite{raffelt96_book} and references therein, but is 
+more complicated because the mass of the $A'$, unlike the mass of the axion, is not necessarily 
+negligible. This section describes the calculation of the rate of energy loss from a supernova core 
+from $A'$ brehmsstrahlung.
+
+The brehmsstrahlung process is not the only process with which we must be concerned. Clearly, the rate of 
+brehmsstrahlung will increase with $\varepsilon$; however, $\varepsilon$ can become sufficiently large 
+that the radiated gauge bosons do not escape the supernova. This happens if the $A'$ either decay to 
+standard model particles or interact with standard model particles prior to exiting the supernova core. 
+In either case, the energy is not lost and the $A'$ does not provide a cooling channel for the supernova. 
+Consequently, for a given $m_{A'}$, there is a maximum $\varepsilon$ that can be constrained in this 
+manner. We estimate $A'$ decay and scattering probabilities, and the upper limits on the $\varepsilon$ 
+constraints in this section as well.
 
 \subsection{Bremsstrahlung amplitude calculation}
-	 There are two processes to consider: the $pp$ scattering with the bremsstrahlung of the dark photon off the proton, $ p+p \rightarrow p+p+A$, and the $pn$ scattering with bremsstrahlung off the proton or the charged pion, $ p+n \rightarrow p+n+A\ $.
-For the $pp$ case there are eight tree-level diagrams, with the emission of the $A'$ from each of the external legs, as shown in Fig.
-, while for the $pn$ case there are five diagrams, including when the $A'$ is emitted from the exchanged pion, as shown in Fig.
-.
 
-The calculation of these diagrams is straightforward, and is described in the appendix.
-Having obtained the diagrams the calculation diverges from the axion bremsstrahlung calculation, since in the kinematic region of interest for supernova explosions the mass of the $A'$ boson is not necessarily negligible.
-The kinematic relations are thus \bea
+There are two processes to consider in order to estimate the rate of energy loss via $A'$ brehmsstrahlung. The first is  
+proton-proton (pp) scattering with the bremsstrahlung of the dark photon off the proton; $p+p \rightarrow p+p+A$. The 
+second is proton-neutron (pn) scattering with bremsstrahlung off of either the proton or the charged pion; 
+$p+n \rightarrow p+n+A$. We estimate the rates for these processes using the one-pion exchange (OPE) 
+approximation for nucleon interactions. In the pp case, there are eight tree-level diagrams, 
+with the emission of the $A'$ from each of the external legs, while for the pn case, there are five diagrams, 
+including a diagram in which the $A'$ is emitted from the exchanged pion. These diagrams are shown 
+correctly in Fig. 3 and Fig. 4 of Ref.~\cite{dent_etal12}.
+
+Evaluating these diagrams is tedious, but very straightforward. We give further details in Appendix~\ref{appendix:details}. 
+The calculation differs from the well-known axion bremsstrahlung calculation, because the mass of the $A'$ boson is not 
+necessarily negligible in the kinematic region of interest for supernova explosions.
+The correct kinematical relations are 
+%
+\bea 
 p_1 \cdot p_2 &=& M_N^2 - \frac{l^2}{2} - \frac{k^2}{2} + p_2 \cdot q_a,\\
@@
 p_2 \cdot p_4 &=& M_N^2 - \frac{k^2}{2},\\
-p_3 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2 + k^2}{2}.
+p_3 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2 + k^2}{2},
 \eea
+%
+where $p_1$ and $p_2$ are the four-momenta of the incoming nucleons, $p_3$ and $p_4$ are the momenta 
+of the outgoing nucleons, $\qa$ is the $A'$ momentum, $k=p_2 - p_3$, $l=p_2 - p_4$, and $M_{\mathrm{N}}$ 
+is the nucleon mass. These kinematical relations correct the relations in Ref.~\cite{dent_etal12}.
+
 Unfortunately, with these relations it does not seem to be possible to simplify the amplitude into an analytically usable form without making unjustified approximations, and so the final expression for the spin-averaged squared matrix element, $ \mathcal{M}^2_{pp}$, contains some two hundred and fifty terms, and thus we do not reproduce that result here.
@@
 \appendix
+\label{appendix:details}
+
 \section{Bremsstrahlung diagrams}

### 2017-01-06 draft.tex
Added more details on the calculation. Moved contents of appendix to main text.

@@
 \usepackage{slashed}
+\usepackage{feynmp}
 \usepackage{epstopdf}
@@
 and the dark photon $A'$, 
-of mass $m_{\mathrm{A'}} = m_{\mathrm{\widetilde{A}'}} \sqrt{1 + \varepsilon^2} \simeq m_{\widetilde{A}'}$ because 
+of mass $m_{\mathrm{A'}} = m_{\mathrm{\widetilde{A}'}} \sqrt{1 + \varepsilon^2} \simeq m_\mathrm{{\widetilde{A}'}}$ because 
 the viable parameter range has $\varepsilon \ll 1$. The dark matter particles are thereby coupled 
@@
 approximation for nucleon interactions. In the pp case, there are eight tree-level diagrams, 
-with the emission of the $A'$ from each of the external legs, while for the pn case, there are five diagrams, 
-including a diagram in which the $A'$ is emitted from the exchanged pion. These diagrams are shown 
-correctly in Fig. 3 and Fig. 4 of Ref.~\cite{dent_etal12}.
+with the emission of the $A'$ from each of the external legs. One of these diagrams is shown 
+in Fig.~\ref{fig:ppdiagram}; the remaining seven diagrams come from placing the radiated $A'$ 
+on each of the other three protons and then, for each of these, interchanging the outgoing momenta. 
+For the pn case, there are five diagrams, four of which are analogous to the pp diagram shown in 
+Fig.~\ref{fig:ppdiagram}. The fifth diagram, shown in Fig.~\ref{fig:npdiagram}, corresponds to 
+emission of the $A'$ from the exchanged, charged pion.
 
-Evaluating these diagrams is tedious, but very straightforward. We give further details in Appendix~\ref{appendix:details}. 
-The calculation differs from the well-known axion bremsstrahlung calculation, because the mass of the $A'$ boson is not 
+%-------------- PP Feynman Diagram
+\begin{figure}
+\includegraphics[width=8cm]{ppdiagram.pdf}
+\caption{One of the eight Feynman diagrams for the pp process. Three of the other diagrams are obtained by 
+placing the $A'$ on each of the protons in turn. The remaining four diagrams come from swapping the outgoing 
+momenta.}
+\label{fig:ppdiagram}
+\end{figure}
+
+Evaluating these diagrams is tedious, but very straightforward. The calculation differs 
+from the well-known axion bremsstrahlung calculation, because the mass of the $A'$ boson is not 
 necessarily negligible in the kinematic region of interest for supernova explosions.
@@
 \bea 
-p_1 \cdot p_2 &=& M_N^2 - \frac{l^2}{2} - \frac{k^2}{2} + p_2 \cdot q_a,\\
-p_1 \cdot p_3 &=& M_N^2 + k \cdot l - \frac{k^2}{2} + p_3 \cdot q_a,\\  
-p_1 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2}{2} + p_4 \cdot q_a, \\
+p_1 \cdot p_2 &=& M_N^2 - \frac{l^2}{2} - \frac{k^2}{2} + p_2 \cdot \qa,\\
+p_1 \cdot p_3 &=& M_N^2 + k \cdot l - \frac{k^2}{2} + p_3 \cdot \qa,\\  
+p_1 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2}{2} + p_4 \cdot \qa, \\
 p_2 \cdot p_3 &=& M_N^2 - \frac{l^2}{2}, \\ 
-p_2 \cdot p_4 &=& M_N^2 - \frac{k^2}{2},\\
+p_2 \cdot p_4 &=& M_N^2 - \frac{k^2}{2},\quad \mathrm{and}\\
 p_3 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2 + k^2}{2},
@@
 
-Unfortunately, with these relations it does not seem to be possible to simplify the amplitude into an analytically usable form without making unjustified approximations, and so the final expression for the spin-averaged squared matrix element, $ \mathcal{M}^2_{pp}$, contains some two hundred and fifty terms, and thus we do not reproduce that result here.
+\arz{Cameron, can you double check this. I think there were some errors in the momenta and in the relative 
+signs of the diagrams. I tried to fixe them.}
+The eight diagrams contribute the following eight terms to the pp amplitude, 
+%
+\begin{widetext}
+\begin{eqnarray}
+	M_1 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_1} 
+	\bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed \epsilon  u(p_1), \\
+	M_2 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_1} 
+	\bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p_4) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed{\epsilon} u(p_1),\\
+	M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_2} 
+	\bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p_4) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
+	M_4 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_2} 
+	\bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
+	M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_3} 
+	\bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
+	M_6 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_3} 
+	\bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
+	M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_4} 
+	\bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),\\
+	M_8 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_4} 
+	\bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),\\
+\end{eqnarray}
+\end{widetext}
+%
+where the dark photon polarization is given by $\epsilon$. The squared amplitude is given by 
+%
+\begin{equation}
+\vert \mathcal{M}_{\mathrm{pp}} \vert^2 = \sum_{s_1,s_2}\, \left\vert \sum_{i=1}^{8}\, M_i \right\vert^2, 
+\end{equation}
+%
+where the first summation is over the incoming proton polarizations. Unfortunately, with the kinematical relations above, 
+the squared amplitude does not yield a tidy expression for the spin-averaged squared matrix element. Our result 
+contains over 200 terms, so we do not reproduce it here for reasons of convenience. However, we note that 
+our result for $\vert \mathcal{M}_{\mathrm{pp}} \vert^2$ is symmetric under exchange of $k$ and $l$ as required.
+
+ it does not seem to be possible to simplify the amplitude into an analytically usable form without making unjustified approximations, and so the final expression for the spin-averaged squared matrix element, $ \mathcal{M}^2_{pp}$, contains some two hundred and fifty terms, and thus we do not reproduce that result here.
 The pn calculation likewise results in a very large and unwieldy expression for $ \mathcal{M}^2_{pn}$.
@@
 (A.3), with their claim that only the coefficient $C_k$ appearing in that equation is nonzero.}
+
+%-------------- NP Feynman Diagram
+\begin{figure}
+\includegraphics[width=8cm]{npdiagram.pdf}
+\caption{One of the five Feynman diagrams for the np process. This particular diagram shows 
+internal brehmsstrahlung off of the charged pion. The remaining four diagrams are analogous to the 
+pp diagram shown in Fig.~\ref{fig:ppdiagram}.}
+\label{fig:npdiagram}
+\end{figure}
 
@@
 \beq
-Q_i = \int (2\pi)^4 E_A \sum_{spins} \mathcal{M}^2_i f(p_1) f(p_2)\delta(p_1+p_2-p_3-p_4-q_a) d\Pi,
+Q_i = \int (2\pi)^4 E_A \sum_{spins} \mathcal{M}^2_i f(p_1) f(p_2)\delta(p_1+p_2-p_3-p_4-\qa) d\Pi,
 \eeq
@@
 
-The inverse mean free path can readily be obtained by modifying $ Q_i $, the expression for the energy loss rate, as follows: removing the factor of $ E_A $ and the phase space integral over $ q_A $, and adding a factor of $ e^{E_A/T} $ for detailed balance.
+The inverse mean free path can readily be obtained by modifying $ Q_i $, the expression for the energy loss rate, as follows: removing the factor of $ E_A $ and the phase space integral over $ \qa $, and adding a factor of $ e^{E_A/T} $ for detailed balance.
 This gives the inverse mean free path as a function of mass and coupling.
@@
 Employing kinematic relations did not seem to reduce the complexity of the problem, so in the interests of reducing the number of possible mistakes the kinematics were done by brute force.
-We integrated over the entire phase space explicitly in terms of the eleven variables of $ \vec{p_1}, \vec{p_2}, \vec{p_3}, \hat{q_a} $, then fixed $ p_4 $ using the 3-momentum part of the delta-function and used an unpleasantly complicated equation obtained from the energy delta-function to fix the remaining one free momentum amplitude - in our case we chose this to be $ q_a $, the momentum of the emitted boson.
+We integrated over the entire phase space explicitly in terms of the eleven variables of $ \vec{p_1}, \vec{p_2}, \vec{p_3}, \hat{\qa} $, then fixed $ p_4 $ using the 3-momentum part of the delta-function and used an unpleasantly complicated equation obtained from the energy delta-function to fix the remaining one free momentum amplitude - in our case we chose this to be $ \qa $, the momentum of the emitted boson.
 At each step points resulting in unphysical configurations were discarded, and the remaining points were then plugged in to the appropriate amplitude, and then that result used as the integrand.
@@
 Labeling the contributions according to the Feynman diagrams in Fig.
-, the matrix elements are
-	\bea
-	M_1 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2
-	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed{\varepsilon} u(p_1),\\
-	M_2 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2
-	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p3) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed \varepsilon  u(p_1), \\
-	M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2
-	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \varepsilon  u(p_2), \\
-	M_4 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2
-	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \varepsilon  u(p_2), \\
-	M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2
-	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \slashed{\varepsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
-	M_6 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2
-	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \slashed{\varepsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
-	M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2
-	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \slashed{\varepsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),\\
-	M_8 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2
-	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \slashed{\varepsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),
-	\eea
-	where the exchange momenta are defined by $ k = p_2-p_4 $ and $ l = p_2-p_3 $, and the dark photon's polarization is given by $\varepsilon$. 
+, the matrix elements are where the exchange momenta are defined by $ k = p_2-p_4 $ and $ l = p_2-p_3 $, and the dark photon's polarization is given by $\epsilon$.
 	For $pn$ scattering, four of the diagrams are simply the same as those given above. The only new Feynman diagram comes from bremsstrahlung off the internal pion, and results in  
@@
 	 M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \varepsilon}{l^2-m_\pi^2
-	 }  \frac{1}{(l-q_a)^2 - m_\pi^2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) u(p_2) (q_a - 2l)\cdot \varepsilon
+	 }  \frac{1}{(l-\qa)^2 - m_\pi^2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) u(p_2) (\qa - 2l)\cdot \varepsilon
 	 \eeq

### 2017-01-07 draft.tex
Significant additions and edits to section 3.

@@
 	M_8 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_4} 
-	\bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),\\
+	\bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),
 \end{eqnarray}
@@
 %
-where the first summation is over the incoming proton polarizations. Unfortunately, with the kinematical relations above, 
-the squared amplitude does not yield a tidy expression for the spin-averaged squared matrix element. Our result 
+where the first summation is over the incoming proton polarizations. These expressions are identical to those 
+given in Ref.~\cite{dent_etal12}; however, they do not simplify significantly if the correct kinematics are used. 
+Unfortunately, with the kinematical relations above, the squared amplitude does not yield a tidy expression 
+for the spin-averaged squared matrix element. Our result 
 contains over 200 terms, so we do not reproduce it here for reasons of convenience. However, we note that 
@@
 
- it does not seem to be possible to simplify the amplitude into an analytically usable form without making unjustified approximations, and so the final expression for the spin-averaged squared matrix element, $ \mathcal{M}^2_{pp}$, contains some two hundred and fifty terms, and thus we do not reproduce that result here.
-The pn calculation likewise results in a very large and unwieldy expression for $ \mathcal{M}^2_{pn}$.
-\footnote{At this point we diverge from Ref.~\cite{dent_etal12} for two reasons.
-One, they use the kinematics as if the $A'$ were massless, as in the axion calculation, and independent of that choice, their squared matrix element does not respect the correct exchange symmetry, as can be seen by inspection of their Eq.
-(A.3), with their claim that only the coefficient $C_k$ appearing in that equation is nonzero.}
+The pn process contain four diagrams analogous to the the diagrams for the pp process (there are only four, of course, 
+because the neutrons cannot radiate the $A'$). The new diagram that is relevant in the pn process is shown in 
+Fig.~\ref{fig:npdiagram} and yields a contribution of 
+%
+\begin{widetext}
+\begin{equation}
+M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \varepsilon}{l^2-m_\pi^2}  \frac{1}{(l-\qa)^2 - m_\pi^2} 
+\bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p_4) \gamma_5 u(p_2) (\qa - 2l)\cdot \varepsilon.
+\end{equation}
+\end{widetext}
+%
+The pn processes likewise yield a squared amplitude, 
+$\vert \mathcal{M}_{\mathrm{pn}} \vert^2$ that is unwieldy, so we do not give the 
+the full expression here.
 
@@
 
-\subsection{Streaming limit}
-The first and simplest bound that may be obtained arises from assuming that all produced particles leave the supernova, carrying their energy with them.
-The constraint is derived simply by requiring that the energy loss through this cooling channel be roughly less than the cooling from neutrino emission; any greater, and it would have an observable effect on supernova cooling.
+%------------------------------------- STREAMING CONSTRAINT
+\subsection{The Streaming Limit of the Energy Loss Rate}
 
-The actual quantity of interest therefore is the rate of energy emission through dark bosons.
-From the spin-summed squared amplitudes already found, this is obtained by integrating over the phase space, and adding a factor of energy of the emitted particle.
+The first and simplest bound that may be obtained arises from assuming that all $A'$ particles produced in the supernova core 
+leave the supernova, carrying their energies with them. The constraint can be derived simply by 
+requiring that the energy loss through this cooling channel be less than the cooling from neutrino emission; 
+any greater, and it would have an observable effect on supernova cooling. This calculation yields values of 
+$\varepsilon$ above which cooling through $A'$ production is too rapid to be consistent with SN1987A. 
+We will consider modifications to this bound from $A'$ trapping and decay in subsequent subsections.
+
+The quantity of interest is the rate of energy emission through dark gauge bosons. 
+From the spin-summed, squared amplitudes described in the previous subsection, 
+the energy emission rate is obtained by integrating over the phase space, 
+and adding a factor of the energy of the emitted particle. To be specific, the 
+energy emission rate per unit volume is 
+%
+\begin{widetext}
 \beq
-Q_i = \int (2\pi)^4 E_A \sum_{spins} \mathcal{M}^2_i f(p_1) f(p_2)\delta(p_1+p_2-p_3-p_4-\qa) d\Pi,
+\label{eq:rate1}
+Q_i = (2\pi)^4 \int\, E_{\mathrm{A}'} \, \sum_{s_1,s_2}\, \vert \mathcal{M}_i \vert^2 f(p_1) f(p_2)\delta^{(4)}(p_1+p_2-p_3-p_4-\qa)\, d\Pi,
 \eeq
-where $d\Pi$ is the Lorentz-invariant phase space, $ E_A $ is the energy of the emitted boson, and $ f(p) $ are the initial occupation numbers.
-The nucleons in the core are comfortably non-degenerate and non-relativistic, so  the Pauli blocking factor is omitted and the Maxwell-Boltzmann distribution is used
+\end{widetext}
+%
+where $d\Pi$ is the Lorentz-invariant phase space, 
+$ E_{\mathrm{A}'}$ is the energy of the emitted $A'$ boson, 
+$f(p)$ are the phase-space densities of the incoming nucleons, and 
+the index $i$ refers to either the pp or pn processes. 
+The nucleons in the core are comfortably non-degenerate and non-relativistic, 
+so the Pauli blocking factor is omitted from Eq.~(\ref{eq:rate1}) and we take 
+all nucleons to have a Maxwell-Boltzmann momentum distribution, so 
 \beq
-f(p) =  \frac{n_b}{2} (\frac{2 \pi}{M_N T})^{3/2} e^{-\frac{\textbf{p}^2} {2 M_N T}}.
+f(p) =  \frac{n_b}{2} \left( \frac{2 \pi}{M_N T} \right)^{3/2} \exp \left(-\frac{p^2}{2 M_N T} \right).
 \eeq
+%
+We chose a baryon number density of $n_{\mathrm{b}} \approx 1.8 \times 10^{38}\, \mathrm{cm}^{-3}$ and a 
+core supernova temperature of $T = 30\, \mathrm{MeV}$, both of which are typical choices and thought to 
+be representative of supernova cores. \arz{Need to put a citation here for the properties of supernova cores. 
+I can probably find something in the literature, but please put something here if you have a citation.}
 
-The integration is performed numerically to obtain $ Q_i$, which is the rate of energy emission per unit volume associated with either the $pn$ or $pp$ process.
-To obtain the dark gauge boson luminosity, it is assumed that production takes place in a core volume $V$ of radius 1 km, giving $ \mathcal{L}_A = V(Q_{pp} + Q_{pn}) $.
-The luminosity $\mathcal{L}_A $ is a complicated function of $ m_A $ and $ T $, but is simply proportional to the square of the parameter $ \varepsilon $.
-Pulling that out of the expression gives a constraint
-\beq
-\varepsilon^2 I_A(m_A, T) \le \mathcal{L}_\nu
-\eeq
-or a bound on the coupling of 
-\beq 
-\varepsilon \le \sqrt{\frac{4.1 \times 10^{37} MeV^2}{I_A(m_A, T)}} 
-\eeq 
-and the exclusion region is generated by varying the mass.
+We performed the phase space integrals using the Monte Carlo routines in the {\tt CUBA} library. 
+\arz{There needs to be some reference, citation, or some other information give about this library here.} 
+We integrated over the momenta $\vec{p}_1$, $\vec{p}_2$, $\vec{p}_3$, and the direction of the 
+three-momentum of the radiated boson $\hat{q}_{\mathrm{A}'}$, after fixing $\vec{p}_4$ 
+and the magnitude of $\vec{q}_{\mathrm{A}'}$ using the delta functions. 
+\arz{Cameron, can you double check this to be sure that it is correct? I rephrased it a bit, 
+but I found the earlier phrasing to be a bit ambiguous and I can't remember which choice 
+you made.} We used the {\tt suave} method provided within {\tt CUBA}, which combines 
+importance sampling and adaptive subdivision, as this method provided the best compromise 
+between accuracy and run-time for this particular application.
 
+To obtain the dark gauge boson luminosity from $Q_{\mathrm{pp}}$ and $Q_{\mathrm{pn}}$, 
+we assumed that $A'$ production takes place in a stellar core of radius $\sim 1$~km, so that 
+the total luminosity of $A'$ is 
+%
+\begin{equation}
+L_{\mathrm{A}'} = V (Q_{\mathrm{pp}} + Q_{\mathrm{pn}})
+\end{equation}
+%
+where $V$ is the volume of the sphere. Clearly, $L_{\mathrm{A}'}$ is proportional to $\varepsilon^2$, 
+so that writing $L_{\mathrm{A}'} = \varepsilon^2 I_{\mathrm{A}'}(m_{\mathrm{A}'},T)$ and 
+$L_{\nu}$ as the neutrino luminosity, we can write the constraint as 
+%
+\begin{equation}
+\varepsilon \lesssim \sqrt{\frac{L_{\nu}}{I_{\mathrm{A}'}(m_{\mathrm{A}'}, T)}}.
+\end{equation}
+%
+Following SOMEBODAY \arz{We need a citation here.}, we show a constraint taking 
+$L_{\nu} \approx 10^{53}\, \mathrm{erg/s} \approx 4 \times 10^{37}\, \mathrm{MeV}^2$.
+
+%---------------------------------- DECAY LIMIT
 \subsection{Decay limit}
@@
 
+%---------------------------------- TRAPPING	
 \subsection{Trapping limit}
@@
 \subsection{Phase Space Integration}
-In every case calculating the bound requires integrating an expression involving the long and complicated Bremsstrahlung amplitude, which unfortunately could not be done analytically without making unjustified approximations.
-The integration was consequently performed numerically using the Monte Carlo routines provided by the Cuba library.
-Employing kinematic relations did not seem to reduce the complexity of the problem, so in the interests of reducing the number of possible mistakes the kinematics were done by brute force.
-We integrated over the entire phase space explicitly in terms of the eleven variables of $ \vec{p_1}, \vec{p_2}, \vec{p_3}, \hat{\qa} $, then fixed $ p_4 $ using the 3-momentum part of the delta-function and used an unpleasantly complicated equation obtained from the energy delta-function to fix the remaining one free momentum amplitude - in our case we chose this to be $ \qa $, the momentum of the emitted boson.
-At each step points resulting in unphysical configurations were discarded, and the remaining points were then plugged in to the appropriate amplitude, and then that result used as the integrand.
-The numerical integration routine used was the \textit{Suave} method provided by CUBA, which combines importance sampling and adaptive subdivision; this method seemed to provide the best compromise between computation time and error.
+
+In every case
 
@@
 The one further slight complication is that at after a certain value of $ M_A $ the decay limit rapidly goes to zero, at which point the procedure was terminated.
-
-We then scanned over the desired range of values for $ M_A $ and output the three limits - trapping, decay, and streaming - at each point.
-The complexity of the integration was such that errors remained relatively large even with highest practicable number of samples.
-
-The calculation is dependent on a number of constants.
-We chose the following values as roughly typical of supernovae: T, the temperature of the supernova core, was set to 30 MeV; r, the radius of the supernova core, to 1 km; $ R $, the distance at which decay products are trapped, to 10 km; $ \mathcal{L} $, the luminosity bound, to $ 10^{53} erg/s $; and $ \n_b $, the baryon number density in the supernova interior, to $ 1.79*10^{38} cm^{-3} $.
 
@@
 
-%------------ APPENDIX
-\appendix
-\label{appendix:details}
-
-\section{Bremsstrahlung diagrams}
-	Each of the $p-p-\pi $ vertices contribute a factor of $g_{pp}$,  the pseudoscalar pion-nucleon coupling.
-$f_{pp}$, the pseudovector pion-nucleon coupling, is related by $g_{pp} = \frac{2M_N}{m_\pi} f_{pp} $.
-The $ p-p-A' $ vertex contributes $e\varepsilon \gamma_\mu$, where $\varepsilon$ is the mixing strength between the photon and dark photon.
-Labeling the contributions according to the Feynman diagrams in Fig.
-, the matrix elements are where the exchange momenta are defined by $ k = p_2-p_4 $ and $ l = p_2-p_3 $, and the dark photon's polarization is given by $\epsilon$.
-	For $pn$ scattering, four of the diagrams are simply the same as those given above. The only new Feynman diagram comes from bremsstrahlung off the internal pion, and results in  
-	 \beq
-	 M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \varepsilon}{l^2-m_\pi^2
-	 }  \frac{1}{(l-\qa)^2 - m_\pi^2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) u(p_2) (\qa - 2l)\cdot \varepsilon
-	 \eeq
-	 Note that these matrix elements agree with Ref.~\cite{dent_etal12}.
 \acknowledgments

### 2017-01-07 draft.tex
Made some further changes through section 3.

@@
 \newcommand{\La}{\Lambda^2_{\rm{alg}}}
+
+\newcommand{\dd}{\mathrm{d}}
 
@@
 \label{eq:rate1}
-Q_i = (2\pi)^4 \int\, E_{\mathrm{A}'} \, \sum_{s_1,s_2}\, \vert \mathcal{M}_i \vert^2 f(p_1) f(p_2)\delta^{(4)}(p_1+p_2-p_3-p_4-\qa)\, d\Pi,
+Q_i = (2\pi)^4 \int\, E_{\mathrm{A}'} \, \sum_{s_1,s_2}\, \vert \mathcal{M}_i \vert^2 f(p_1) f(p_2)\delta^{(4)}(p_1+p_2-p_3-p_4-\qa)\, \dd \Pi,
 \eeq
@@
 %
-where $d\Pi$ is the Lorentz-invariant phase space, 
+where 
+%
+\begin{equation}
+d\Pi = \frac{\dd^3 \vec{q}_{\mathrm{A}'}}{(2\pi)^3 2E_{\mathrm{A}'}}\, \prod_{i=1}^{4}\, \frac{\dd^3 \vec{p}_i}{(2\pi^3) 2E_1}
+\end{equation} 
+is the Lorentz-invariant phase space interval, 
 $ E_{\mathrm{A}'}$ is the energy of the emitted $A'$ boson, 
@@
 \begin{equation}
+\label{eq:bound1}
 \varepsilon \lesssim \sqrt{\frac{L_{\nu}}{I_{\mathrm{A}'}(m_{\mathrm{A}'}, T)}}.
@@
 %
-Following SOMEBODAY \arz{We need a citation here.}, we show a constraint taking 
+Following SOMEBODY \arz{We need a citation here.}, we derive a constraint taking 
 $L_{\nu} \approx 10^{53}\, \mathrm{erg/s} \approx 4 \times 10^{37}\, \mathrm{MeV}^2$.
 
+The constraint derived in this manner from Eq.~(\ref{eq:bound1}) sets the lower limit on the 
+exclusion band shown in Figure~\ref{fig:bound1}, which we will discuss in more detail 
+below. If all of the $A'$ produced in the core left the supernova freely, the bound of values of 
+$\varepsilon$ higher than those given by Eq.~(\ref{eq:bound1}) would be ruled out. However, 
+as we have already mentioned, $\varepsilon$ can become sufficiently large that only a negligible 
+amount of energy actually leaves the supernova core because of either $A'$ decays or scattering. 
+These considerations place an upper limit on the values of $\varepsilon$ for which this constraint 
+applies, and we discuss these effects in the next two subsections.
+
 %---------------------------------- DECAY LIMIT
-\subsection{Decay limit}
-The constraint from the streaming limit above provides an upper bound on the allowed coupling (or lower bound on the excluded coupling) by considering the production on the $A'$.
-Naively it might be expected that this suffices, in that all higher couplings are excluded.
-However, in order to function as a cooling channel, enough of the produced dark gauge bosons must escape the supernova.
-As the coupling increases, so do processes that prevent the escape, and so the excluded region has an upper bound, above which the luminosity again drops below the neutrino luminosity.
-The first such limit may be found by considering decay of the dark bosons into Standard Model particles, and assuming that these SM particles are trapped in the supernova core and contribute nothing to the cooling.
+\subsection{The Decay Limit}
+
+The constraint from the streaming limit above provides an upper bound on the allowed coupling 
+(or lower bound on the excluded coupling) from the production on $A'$ bosons. 
+In order to function as an effective cooling channel, enough of the dark gauge bosons 
+must escape the supernova. As the coupling increases, so do processes that prevent this escape, 
+and so the excluded region has an upper bound, above which the luminosity again drops below the 
+neutrino luminosity. The first such limit may be found by considering decay of the dark bosons 
+into Standard Model particles. Standard model particles will scatter and thermalize 
+on a timescale much shorter than the timescale for the evolution of the core, so decays 
+contribute nothing to the cooling.
+
 The dark boson has a typical lifetime of 
+\arz{Cameron, try to rephrase this. This is not the lifetime, but rather the 
+mean distance to a decay.}
+%
 \beq
@@
 \eeq
-To take this into account, the above exponential factor is simply appended to the phase space integrand, and the calculation then proceeds as before.
-The limit is derived from the same equation, with the only complication being the fact that $ I_A $ is now a function of $ \varepsilon $, in addition to $ m_A, T $.
-This makes the numerical calculation slightly more complicated, but otherwise changes nothing of importance, with now the constraint a transcendental equation,
-\beq
-\varepsilon \le \sqrt{\frac{4.1 \times 10^{37} MeV^2}{I_A(m_A, T, \varepsilon)}}.
-\eeq
+%
+To account for the suppression of gauge boson luminosity due to decays we simply multiply the phase space 
+integrand in Eq.~(\ref{eq:rate1}) by the exponential suppression factor, after which the calculation proceeds 
+as in the previous subsection. The limit is derived in the same way, 
+with the additional complication that $I_{\mathrm{A}'}$ is now a function of $\varepsilon $, in addition to $m_{\mathrm{A}'}$ and $T$. 
+The constraint Eq.~(\ref{eq:bound1}), therefore, becomes a transcendental equation that must be solved numerically.
+
+The luminosity in $A'$ will be an increasing function of $\varepsilon$ until decays suppress the gauge boson luminosity, 
+at which point $L_{\mathrm{A}'}$ becomes a rapidly decreasing function of $\varepsilon$. Therefore, the excluded values of 
+$\varepsilon$ at a given mass will generally have a lower bound set by the calculations of the previous subsection, and an 
+upper bound set by decays.
 
@@
 \subsection{Trapping limit}
-The second constraint that produces an upper bound on the excluded region comes from considering trapping of dark bosons within the supernova.
-With a large enough coupling, the new particles will thermalize and then will be emitted from a spherical shell.
-In this case the luminosity is given simply by the Steffan-Boltzmann law
+
+\arz{This section needs some work as it is a bit hard to follow.}
+The second effect that produces an upper bound on the excluded region 
+comes from considering trapping of dark bosons within the supernova. 
+With a large enough coupling, the dark photons will thermalize and then 
+will be emitted from an approximately spherical ``dark photosphere" at the radial position 
+where the $A'$ mean free path becomes larger than the typical size of the supernova core. 
+In this case the luminosity is given simply by Stefan's law, 
 \beq
@@
 \eeq
-where $ r $ is now the radius of the emitting shell and $ T_A $ its temperature.
-We can estimate $ r = 10$ km, since the density of the supernova drops drastically around that point.
+where $r$ is now the radius of the emitting shell and $T_A$ its temperature. 
+We estimate the radius of this dark photosphere as $r=10$ km, 
+because the density of the supernova drops drastically around that point. 
 After taking that value for r, the bound on the luminosity translates into a bound on $ T_A $ 
@@
 \begin{figure}[th]
+	\includegraphics[width=9cm]{endtoend.png}
+	\caption{A comparison of the final result for the excluded region with the result from Ref.~\cite{dent_etal12}.
+The excluded region is clearly significantly less restrictive, and opens up the region of parameter space for $\varepsilon \approx  1e-8-9 $.
+\arz{Cameron, some similar comments as for Figure 1. Can we write numbers as "$10^{-9}$" rather 
+than "1e-09" and so on? Can we make the axis labels and tick mark labels larger?}}
+\label{fig:constraint}
+\end{figure}
+
+\begin{figure}[th]
 \includegraphics[width=9cm]{stages.eps}
@@
 Let's put some text here.
-
-\begin{figure}[th]
-	\includegraphics[width=9cm]{endtoend.png}
-	\caption{A comparison of the final result for the excluded region with the result from Ref.~\cite{dent_etal12}.
-The excluded region is clearly significantly less restrictive, and opens up the region of parameter space for $\varepsilon \approx  1e-8-9 $.
-\arz{Cameron, some similar comments as for Figure 1. Can we write numbers as "$10^{-9}$" rather 
-than "1e-09" and so on? Can we make the axis labels and tick mark labels larger?}	
-	}
-\end{figure}
 

### 2017-01-10 draft.tex
Minor edits to decay section.

@@
 \cite{dent_etal12} (and \cite{rrapaj_reddy16}, with a slight modification) (\arz{Cameron, add others of which you may be aware.}) 
-to constraint dark electromagnetism models of SIDM in which the self-interaction arises from a Yukawa potential and the 
-vector boson is kinetically mixed with the standard model photon.
+to constraint dark electromagnetism models of SIDM in which the self-interaction arises from a Yukawa potential 
+and the vector boson is kinetically mixed with the standard model photon.
 
 As we mentioned above, we find SN1987A constraints on dark photon SIDM models that are considerably different 
-from those of \cite{dent_etal12}. If correct, this has important consequences. The Snowmass white paper by Kaplinghat, 
-Tulin, and Yu \cite{kaplinghat_etal13_whitepaper} nicely summarizes a variety of constraints on dark electromagnetism models of 
-SIDM. One point that is clear from Ref.~\cite{kaplinghat_etal13_whitepaper} is that there is only a narrow range of 
-viable photon mixing parameters that can lead to production of SIDM in the early universe, while evading all constraints, 
-including the constraint of \cite{dent_etal12}. Our results suggest that the SN1987A constraints from Ref.~\cite{dent_etal12} 
-are too restrictive. The less restrictive constraints that we quote open up a space of unrestricted mixing parameters that 
-ranges over two orders of magnitude. Interestingly, the parameter space opened by our updated constraints corresponds to a 
-space that may a significant impact on cosmological structure formation, particularly the structures of dark matter halos and galaxies.
+from those of \cite{dent_etal12}. If correct, our result has important consequences. 
+The Snowmass white paper by Kaplinghat, Tulin, and Yu \cite{kaplinghat_etal13_whitepaper} nicely 
+summarizes a variety of constraints on dark electromagnetism models of SIDM. 
+One point that is clear from Ref.~\cite{kaplinghat_etal13_whitepaper} is that there exists 
+only a narrow range of viable photon mixing parameters that can lead to production of SIDM in the early universe and 
+interesting effects on cosmological structure formation, while simultaneously evading all constraints, 
+including the constraint of Ref.~\cite{dent_etal12}. Our results suggest that the SN1987A constraints from 
+Ref.~\cite{dent_etal12} are too restrictive. The constraints that we quote reveal a region of unrestricted mixing 
+parameters that ranges over two orders of magnitude. Interestingly, the parameter space opened by our updated 
+constraints corresponds to SIDM models that may have a significant impact on cosmological structure formation, 
+particularly the structures of dark matter halos and galaxies.
 
-The discrepancy between our result and that of Ref.~\cite{dent_etal12} is due to several factors. First, it is straightforward to 
+The discrepancy between our result and that of Ref.~\cite{dent_etal12} arises due to multiple factors. First, it is straightforward to 
 demonstrate that the kinematical relationships in given in Appendix A of Ref.~\cite{dent_etal12} are incorrect. Second, the 
 squared matrix elements given in Eq.~(A3) and Eq.~(C18) of Ref.~\cite{dent_etal12} are incorrect. Our squared matrix elements 
-are considerably more complicated. There appear to be a number of errors that led to the incorrect squared matrix elements in 
+are considerably more complicated. Multiple errors must have led to the incorrect squared matrix elements in 
 Ref.~\cite{dent_etal12}. At the very least, these errors include simplification using the incorrect kinematics and neglect of the 
-mass of the gauge boson (which, while legitimate for the $\sim$meV-mass axion, is not justified in this context). Additional 
-discrepancies must be present, the causes of which are not apparent from the exposition, 
-because the squared matrix elements in Eq.~(A3) and Eq.~(C18) of Ref.~\cite{dent_etal12} 
-do not obey the correct symmetries under interchange of the incoming or outgoing baryon momenta. 
+mass of the gauge boson (which, while legitimate for the $\sim$meV-mass axion, is not justified in this context). 
+Discrepancies in addition to those kinematical issues must also be present, 
+the causes of which are not apparent from the exposition, because the squared matrix 
+elements in Eq.~(A3) and Eq.~(C18) of Ref.~\cite{dent_etal12} do not obey the 
+correct symmetries under interchange of the incoming or outgoing baryon momenta. 
 Given these errors, we suggest that our results should supercede these previously-published constraints.
@@
 
-\subsection{Bremsstrahlung amplitude calculation}
+\subsection{Brehmsstrahlung of $A'$ Bosons}
 
@@
 
-\arz{Cameron, can you double check this. I think there were some errors in the momenta and in the relative 
-signs of the diagrams. I tried to fixe them.}
+\arz{Cameron, can you double check this? I think there were some errors in the momenta and in the relative 
+signs of the diagrams. I tried to fix them. Please go over this carefully.}
 The eight diagrams contribute the following eight terms to the pp amplitude, 
@@
 \begin{eqnarray}
-	M_1 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_1} 
-	\bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed \epsilon  u(p_1), \\
-	M_2 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_1} 
-	\bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p_4) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed{\epsilon} u(p_1),\\
-	M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_2} 
-	\bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p_4) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
-	M_4 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_2} 
-	\bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
-	M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_3} 
-	\bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
-	M_6 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_3} 
-	\bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
-	M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_4} 
-	\bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),\\
-	M_8 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_4} 
-	\bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),
+	M_1 &=& \frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_1}\ 
+	\bar{u}(p_4) \gamma_5 u(p_2)\  \bar{u}(p_3) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed \epsilon  u(p_1), \\
+	M_2 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_1}\  
+	\bar{u}(p_3) \gamma_5 u(p_2)\  \bar{u}(p_4) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed{\epsilon} u(p_1),\\
+	M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_2}\ 
+	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
+	M_4 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_2}\ 
+	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
+	M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_3}\
+	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
+	M_6 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_3}\ 
+	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
+	M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_4}\ 
+	\bar{u}(p_4) \gamma_5 u(p_2)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),\\
+	M_8 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_4}\ 
+	\bar{u}(p_3) \gamma_5 u(p_2)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),
 \end{eqnarray}
@@
 %
-where the dark photon polarization is given by $\epsilon$. The squared amplitude is given by 
+where the dark photon polarization is given by $\epsilon^{\nu}$. The squared amplitude is given by 
 %
@@
 \begin{equation}
-M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \varepsilon}{l^2-m_\pi^2}  \frac{1}{(l-\qa)^2 - m_\pi^2} 
+M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{(l-\qa)^2 - m_\pi^2} 
 \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p_4) \gamma_5 u(p_2) (\qa - 2l)\cdot \varepsilon.
@@
 internal brehmsstrahlung off of the charged pion. The remaining four diagrams are analogous to the 
-pp diagram shown in Fig.~\ref{fig:ppdiagram}.}
+pp diagram shown in Fig.~\ref{fig:ppdiagram}. In the case of the np processes, there are only four 
+diagrams for brehmsstrahlung off of the external legs because two of the legs correspond to the 
+uncharged neutron.}
 \label{fig:npdiagram}
@@
 so the Pauli blocking factor is omitted from Eq.~(\ref{eq:rate1}) and we take 
-all nucleons to have a Maxwell-Boltzmann momentum distribution, so 
+all nucleons to have a Maxwell-Boltzmann phase-space distribution distribution, 
 \beq
@@
 %
-We chose a baryon number density of $n_{\mathrm{b}} \approx 1.8 \times 10^{38}\, \mathrm{cm}^{-3}$ and a 
+We choose a baryon number density of $n_{\mathrm{b}} \approx 1.8 \times 10^{38}\, \mathrm{cm}^{-3}$ and a 
 core supernova temperature of $T = 30\, \mathrm{MeV}$, both of which are typical choices and thought to 
@@
 %
-where $V$ is the volume of the sphere. Clearly, $L_{\mathrm{A}'}$ is proportional to $\varepsilon^2$, 
-so that writing $L_{\mathrm{A}'} = \varepsilon^2 I_{\mathrm{A}'}(m_{\mathrm{A}'},T)$ and 
-$L_{\nu}$ as the neutrino luminosity, we can write the constraint as 
+where $V$ is the volume of the sphere. Clearly, $L_{\mathrm{A}'}$ is proportional to $\varepsilon^2$. 
+Writing $L_{\mathrm{A}'} = \varepsilon^2 I_{\mathrm{A}'}(m_{\mathrm{A}'},T)$, as in Ref.~\cite{dent_etal12}, 
+and $L_{\nu}$ as the neutrino luminosity, we can write the constraint as 
 %
@@
 The constraint derived in this manner from Eq.~(\ref{eq:bound1}) sets the lower limit on the 
-exclusion band shown in Figure~\ref{fig:bound1}, which we will discuss in more detail 
-below. If all of the $A'$ produced in the core left the supernova freely, the bound of values of 
-$\varepsilon$ higher than those given by Eq.~(\ref{eq:bound1}) would be ruled out. However, 
-as we have already mentioned, $\varepsilon$ can become sufficiently large that only a negligible 
-amount of energy actually leaves the supernova core because of either $A'$ decays or scattering. 
-These considerations place an upper limit on the values of $\varepsilon$ for which this constraint 
-applies, and we discuss these effects in the next two subsections.
+exclusion band shown in Figure~\ref{fig:constraint}. We will discuss Fig.~\ref{fig:constraint} 
+in more detail below. If all of the $A'$ produced in the core leave the supernova freely, all 
+values of $\varepsilon$ higher than those given by Eq.~(\ref{eq:bound1}) would be ruled out. 
+However, as we have already mentioned, $\varepsilon$ can become sufficiently large that only a 
+negligible amount of energy actually exits the supernova core. For large values or $\varepsilon$, 
+this can occur because of either $A'$ decays or $A'$ scattering. These additional considerations place 
+an upper limit on the values of $\varepsilon$ for which this constraint applies, 
+and we discuss these effects in the next two subsections.
 
@@
 The constraint from the streaming limit above provides an upper bound on the allowed coupling 
-(or lower bound on the excluded coupling) from the production on $A'$ bosons. 
-In order to function as an effective cooling channel, enough of the dark gauge bosons 
-must escape the supernova. As the coupling increases, so do processes that prevent this escape, 
+from the production on $A'$ bosons. In order to function as an effective cooling channel, the 
+radiated dark gauge bosons must escape the supernova in sufficient numbers. 
+As the coupling increases, so do processes that prevent this escape, 
 and so the excluded region has an upper bound, above which the luminosity again drops below the 
@@
 
+\arz{I removed reference to $N_{\rm eff}$ because for us $N_{\rm eff}=1$ (doesn't it? the 
+only kinematically-allowed decay is to electron-positron pairs, correct?). I also rephrased a 
+little bit. Please review this. 
 The dark boson has a typical lifetime of
-\arz{Cameron, try to rephrase this. This is not the lifetime, but rather the 
-mean distance to a decay.}
+\begin{equation}
+\tau_{\mathrm{A}'} = \frac{3}{\varepsilon^2 \alpha m_{\mathrm{A}'}},
+\end{equation}
+where $\alpha$ is the fine structure constant. Therefore, in the relativistic limit, 
+the typical travel distance to decay is given by 
 %
 \beq
-l = \frac{3 E_{A}}{N_{eff} m_A^2 \varepsilon^2},
+l = \gamma \tau_{\mathrm{A}'} = \frac{3 E_{A}}{N_{eff} m_A^2 \varepsilon^2},
 \eeq
-and so the fraction escaping the supernova before decaying is given by 
+and so the fraction escaping the supernova before decaying may be estimated as (e.g., \Ref.~\cite{bjorken_etal09})
 \beq

### 2017-01-10 draft.tex
Made changes all the way through to the results section.

@@
 \newcommand{\as}{\alpha_s}
-\newcommand{\qa}{q_{A'}}
+\newcommand{\qa}{q_{\mathrm{A}'}}
 
@@
 \newcommand{\La}{\Lambda^2_{\rm{alg}}}
+
+\newcommand{\Aprime}{\mathrm{A}'}
+\newcommand{\rdp}{r_{\mathrm{dp}}}
 
@@
 from the supernova core that is inconsistent with observations of SN1987A, analogous to the 
-classic constraint on axions \cite{raffelt96_book}. This mechanism was already exploited by 
+classic constraint on axions \cite{turner88,raffelt96_book}. This mechanism was already exploited by 
 \cite{dent_etal12} (and \cite{rrapaj_reddy16}, with a slight modification) (\arz{Cameron, add others of which you may be aware.}) 
@@
 The Snowmass white paper by Kaplinghat, Tulin, and Yu \cite{kaplinghat_etal13_whitepaper} nicely 
-summarizes a variety of constraints on dark electromagnetism models of SIDM. 
+summarizes a variety of constraints on dark electromagnetism models of SIDM (many details can be 
+found in the the very informative work of Ref.~\cite{bjorken_etal09}). 
 One point that is clear from Ref.~\cite{kaplinghat_etal13_whitepaper} is that there exists 
@@
 \begin{equation}
-\mathcal{L}_{\mathrm{int}} = g_{\chi} \bar{\chi} \, \widetilde{\slashed{A'}} \chi + q \bar{f}\, \widetilde{\slashed{A}} f, 
+\mathcal{L}_{\mathrm{int}} = g_{\chi} \bar{\chi} \, \widetilde{\slashed{\Aprime}} \chi + q \bar{f}\, \widetilde{\slashed{A}} f, 
 \end{equation}
 %
-where $\chi$ is the dark matter, $g_{\chi}$ is the dark coupling, $\widetilde{A'}$ is the dark gauge boson, 
+where $\chi$ is the dark matter, $g_{\chi}$ is the dark coupling, $\widetilde{\Aprime}$ is the dark gauge boson, 
 $f$ is a standard model fermion of charge $q$, and $\widetilde{A}$ is the standard model gauge boson. 
@@
 in the Lagrangian causes the $\widetilde{A}$ to be an admixture of the massless photon $A$, 
-and the dark photon $A'$, 
-of mass $m_{\mathrm{A'}} = m_{\mathrm{\widetilde{A}'}} \sqrt{1 + \varepsilon^2} \simeq m_\mathrm{{\widetilde{A}'}}$ because 
+and the dark photon $\Aprime$, 
+of mass $m_{\mathrm{\Aprime}} = m_{\mathrm{\widetilde{A}'}} \sqrt{1 + \varepsilon^2} \simeq m_\mathrm{{\widetilde{A}'}}$ because 
 the viable parameter range has $\varepsilon \ll 1$. The dark matter particles are thereby coupled 
@@
 in this  particular case the proton and pion. The rate of brehmsstrahlung 
-depends upon both $\varepsilon$ and the mass of the $A'$. Consequently, 
+depends upon both $\varepsilon$ and the mass of the $\Aprime$. Consequently, 
 supernova cooling can constrain the mixing $\varepsilon$ as a function of 
-$m_{A'}$ for such models. Delineating such a constraint is the 
+$m_{\Aprime}$ for such models. Delineating such a constraint is the 
 primary aim of this paper.
@@
 
-We aim to estimate the rate of energy loss from the core of a supernova from $A'$ brehmsstrahlung 
+We aim to estimate the rate of energy loss from the core of a supernova from $\Aprime$ brehmsstrahlung 
 during nucleon-nucleon interactions. The calculation is analogous to the well-known estimate of axion 
 emission from supernova cores described in Ref.~\cite{raffelt96_book} and references therein, but is 
-more complicated because the mass of the $A'$, unlike the mass of the axion, is not necessarily 
+more complicated because the mass of the $\Aprime$, unlike the mass of the axion, is not necessarily 
 negligible. This section describes the calculation of the rate of energy loss from a supernova core 
-from $A'$ brehmsstrahlung.
+from $\Aprime$ brehmsstrahlung.
 
@@
 brehmsstrahlung will increase with $\varepsilon$; however, $\varepsilon$ can become sufficiently large 
-that the radiated gauge bosons do not escape the supernova. This happens if the $A'$ either decay to 
+that the radiated gauge bosons do not escape the supernova. This happens if the $\Aprime$ either decay to 
 standard model particles or interact with standard model particles prior to exiting the supernova core. 
-In either case, the energy is not lost and the $A'$ does not provide a cooling channel for the supernova. 
-Consequently, for a given $m_{A'}$, there is a maximum $\varepsilon$ that can be constrained in this 
-manner. We estimate $A'$ decay and scattering probabilities, and the upper limits on the $\varepsilon$ 
+In either case, the energy is not lost and the $\Aprime$ does not provide a cooling channel for the supernova. 
+Consequently, for a given $m_{\Aprime}$, there is a maximum $\varepsilon$ that can be constrained in this 
+manner. We estimate $\Aprime$ decay and scattering probabilities, and the upper limits on the $\varepsilon$ 
 constraints in this section as well.
 
-\subsection{Brehmsstrahlung of $A'$ Bosons}
+\subsection{Brehmsstrahlung of $\Aprime$ Bosons}
 
-There are two processes to consider in order to estimate the rate of energy loss via $A'$ brehmsstrahlung. The first is  
+There are two processes to consider in order to estimate the rate of energy loss via $\Aprime$ brehmsstrahlung. The first is  
 proton-proton (pp) scattering with the bremsstrahlung of the dark photon off the proton; $p+p \rightarrow p+p+A$. The 
@@
 approximation for nucleon interactions. In the pp case, there are eight tree-level diagrams, 
-with the emission of the $A'$ from each of the external legs. One of these diagrams is shown 
-in Fig.~\ref{fig:ppdiagram}; the remaining seven diagrams come from placing the radiated $A'$ 
+with the emission of the $\Aprime$ from each of the external legs. One of these diagrams is shown 
+in Fig.~\ref{fig:ppdiagram}; the remaining seven diagrams come from placing the radiated $\Aprime$ 
 on each of the other three protons and then, for each of these, interchanging the outgoing momenta. 
@@
 Fig.~\ref{fig:ppdiagram}. The fifth diagram, shown in Fig.~\ref{fig:npdiagram}, corresponds to 
-emission of the $A'$ from the exchanged, charged pion.
+emission of the $\Aprime$ from the exchanged, charged pion.
 
@@
 \caption{One of the eight Feynman diagrams for the pp process. Three of the other diagrams are obtained by 
-placing the $A'$ on each of the protons in turn. The remaining four diagrams come from swapping the outgoing 
+placing the $\Aprime$ on each of the protons in turn. The remaining four diagrams come from swapping the outgoing 
 momenta.}
@@
 Evaluating these diagrams is tedious, but very straightforward. The calculation differs 
-from the well-known axion bremsstrahlung calculation, because the mass of the $A'$ boson is not 
+from the well-known axion bremsstrahlung calculation, because the mass of the $\Aprime$ boson is not 
 necessarily negligible in the kinematic region of interest for supernova explosions.
@@
 where $p_1$ and $p_2$ are the four-momenta of the incoming nucleons, $p_3$ and $p_4$ are the momenta 
-of the outgoing nucleons, $\qa$ is the $A'$ momentum, $k=p_2 - p_3$, $l=p_2 - p_4$, and $M_{\mathrm{N}}$ 
+of the outgoing nucleons, $\qa$ is the $\Aprime$ momentum, $k=p_2 - p_3$, $l=p_2 - p_4$, and $M_{\mathrm{N}}$ 
 is the nucleon mass. These kinematical relations correct the relations in Ref.~\cite{dent_etal12}.
@@
 The pn process contain four diagrams analogous to the the diagrams for the pp process (there are only four, of course, 
-because the neutrons cannot radiate the $A'$). The new diagram that is relevant in the pn process is shown in 
+because the neutrons cannot radiate the $\Aprime$). The new diagram that is relevant in the pn process is shown in 
 Fig.~\ref{fig:npdiagram} and yields a contribution of 
@@
 
-The first and simplest bound that may be obtained arises from assuming that all $A'$ particles produced in the supernova core 
+The first and simplest bound that may be obtained arises from assuming that all $\Aprime$ particles produced in the supernova core 
 leave the supernova, carrying their energies with them. The constraint can be derived simply by 
@@
 any greater, and it would have an observable effect on supernova cooling. This calculation yields values of 
-$\varepsilon$ above which cooling through $A'$ production is too rapid to be consistent with SN1987A. 
-We will consider modifications to this bound from $A'$ trapping and decay in subsequent subsections.
+$\varepsilon$ above which cooling through $\Aprime$ production is too rapid to be consistent with SN1987A. 
+We will consider modifications to this bound from $\Aprime$ trapping and decay in subsequent subsections.
 
@@
 is the Lorentz-invariant phase space interval, 
-$ E_{\mathrm{A}'}$ is the energy of the emitted $A'$ boson, 
+$ E_{\mathrm{A}'}$ is the energy of the emitted $\Aprime$ boson, 
 $f(p)$ are the phase-space densities of the incoming nucleons, and 
@@
 To obtain the dark gauge boson luminosity from $Q_{\mathrm{pp}}$ and $Q_{\mathrm{pn}}$, 
-we assumed that $A'$ production takes place in a stellar core of radius $\sim 1$~km, so that 
-the total luminosity of $A'$ is 
+we assumed that $\Aprime$ production takes place in a stellar core of radius $\sim 1$~km, so that 
+the total luminosity of $\Aprime$ is 
 %
@@
 exclusion band shown in Figure~\ref{fig:constraint}. We will discuss Fig.~\ref{fig:constraint} 
-in more detail below. If all of the $A'$ produced in the core leave the supernova freely, all 
+in more detail below. If all of the $\Aprime$ produced in the core leave the supernova freely, all 
 values of $\varepsilon$ higher than those given by Eq.~(\ref{eq:bound1}) would be ruled out. 
@@
 negligible amount of energy actually exits the supernova core. For large values or $\varepsilon$, 
-this can occur because of either $A'$ decays or $A'$ scattering. These additional considerations place 
+this can occur because of either $\Aprime$ decays or $\Aprime$ scattering. These additional considerations place 
 an upper limit on the values of $\varepsilon$ for which this constraint applies, 
@@
 The constraint from the streaming limit above provides an upper bound on the allowed coupling 
-from the production on $A'$ bosons. In order to function as an effective cooling channel, the 
+from the production on $\Aprime$ bosons. In order to function as an effective cooling channel, the 
 radiated dark gauge bosons must escape the supernova in sufficient numbers. 
@@
 only kinematically-allowed decay is to electron-positron pairs, correct?). I also rephrased a 
-little bit. Please review this. 
+little bit. Please review this.}
 The dark boson has a typical lifetime of
@@
 \beq
-l = \gamma \tau_{\mathrm{A}'} = \frac{3 E_{A}}{N_{eff} m_A^2 \varepsilon^2},
+\label{eq:decaylength}
+l = \gamma \tau_{\mathrm{A}'} = \frac{3 E_{\mathrm{A}'}}{N_{eff} m_{\mathrm{A}'}^2 \varepsilon^2},
 \eeq
-and so the fraction escaping the supernova before decaying may be estimated as (e.g., \Ref.~\cite{bjorken_etal09})
+and so the fraction escaping the supernova before decaying may be estimated as (e.g., Ref.~\cite{bjorken_etal09})
 \beq
-e^{r_{decay}/l} = e^{r_{decay} N_{eff} m_A^2 \varepsilon^2/(3 E_A)}.
+\label{eq:decayfactor}
+\exp \left( - \frac{r_{\mathrm{decay}}}{l} \right) = 
+\exp \left( - \frac{r_{\mathrm{decay}} m_{\mathrm{A}'}^2 \varepsilon^2}{3 E_{\mathrm{A}'}} \right),
 \eeq
 %
+an approximation which is valid so long as the size of the supernova within which standard model decay 
+products can interact and be thermalized is significantly larger than the region within which $\Aprime$ are produced, 
+an assumption which should be satisfied comfortably. 
 To account for the suppression of gauge boson luminosity due to decays we simply multiply the phase space 
@@
 
-The luminosity in $A'$ will be an increasing function of $\varepsilon$ until decays suppress the gauge boson luminosity, 
+\arz{I have a few questions here. First, what did you choose for the value or $r_{\mathrm{decay}}$? This must 
+be specified.
+
+Second, this treatment is valid under the assumption of relativistic dark photons. However, it is not clear to me that this limit is 
+the appropriate limit. This limit is valid when $m_{\mathrm{A}'} < T = 30 \, \mathrm{MeV}$. However, I think that 
+the decays only become more important than trapping for masses $m_{\mathrm{A}'} \gtrsim 30\, \mathrm{MeV}$. 
+This suggests that we should use the non-relativistic limit here. Do I misunderstand something?}
+
+The luminosity in $\Aprime$ will be an increasing function of $\varepsilon$ until decays suppress the gauge boson luminosity, 
 at which point $L_{\mathrm{A}'}$ becomes a rapidly decreasing function of $\varepsilon$. Therefore, the excluded values of 
 $\varepsilon$ at a given mass will generally have a lower bound set by the calculations of the previous subsection, and an 
-upper bound set by decays.
+upper bound set by decays. An approximate treatment of the upper bound due to decays, as we present here, is 
+sufficient because over almost the entire mass range of interest, larger values of $\varepsilon$ are independently 
+excluded by terrestrial beam dump experiments \cite{bjorken_etal09}. Therefore, it is far more important to 
+derive an accurate estimate of the {\em lower} boundary of the exclusion region (as was done in 
+the previous subsection) than the upper boundary of the exclusion region.
 
@@
 \arz{This section needs some work as it is a bit hard to follow.}
+
 The second effect that produces an upper bound on the excluded region 
@@
 will be emitted from an approximately spherical ``dark photosphere" at the radial position 
-where the $A'$ mean free path becomes larger than the typical size of the supernova core. 
+where the $\Aprime$ mean free path becomes larger than the typical size of the supernova core. 
 In this case the luminosity is given simply by Stefan's law, 
 \beq
-\mathcal{L}_t  = 4\pi r^2 T_A^4 \sigma,
+\mathcal{L}_t  = 4\pi \rdp^2 T_{\mathrm{A}'}^4 \sigma,
 \eeq
-where $r$ is now the radius of the emitting shell and $T_A$ its temperature. 
-We estimate the radius of this dark photosphere as $r=10$ km, 
+where $\rdp$ is now the radius of the emitting shell and $T_{\mathrm{A}'}$ its temperature. 
+We estimate the radius of this dark photosphere as $\rdp=10$ km, 
 because the density of the supernova drops drastically around that point. 
-After taking that value for r, the bound on the luminosity translates into a bound on $ T_A $ 
+\arz{We need a citation for this statement, but I do not know one off of the top of my head.}
+The bound on the luminosity can then be recast as a bound on $T_{\mathrm{A}'}$, 
+%
 \beq
-T_A \le 9.586\rm\ MeV.
+T_{\mathrm{A}'} \lesssim 9.6\rm\ MeV.
 \eeq
-That bound can then be translated into the desired bound on the coupling as a function of mass by assuming that the particles are emitted from an optical depth $ \tau = 2/3 $, and finding the temperature that corresponds to that optical depth.
-This is a somewhat involved calculation.
-First, one needs a model for the density and temperature in the supernova. Following \cite{dent_etal12}, we assume 
+%
+That bound can then be translated into the desired bound on the coupling as a function of mass by adopting a 
+simple model for the supernova atmosphere, assuming that the particles are emitted from the dark photosphere 
+at a point where the optical depth to scattering is $\tau = 2/3 $, and finding the temperature that corresponds 
+to that optical depth.
+
+\arz{In what follow ALL SUBSCRIPTS SHOULD BE MADE CONSISTENT WITH PRD CONVENTIONS. Please 
+make all subscripts in roman type using ``mathrm." Please take $A \rightarrow \Aprime$, and so on.}
+
+This is a somewhat involved calculation. First, one needs a model for 
+the density and temperature in the supernova. Following \cite{turner88}, 
+we assume a simple power-law model for the supernova core, with 
 \bea
-\rho &=& \rho_p \left(\frac{R}{r}\right)^n,\\
-T &=& T_R \left(\frac{\rho(r)}{\rho_R}\right)^{1/3},
+\rho &=& \rho_{\mathrm{p}} \left( \frac{R}{r}\right )^n,\\
+T &=& T_{\mathrm{R}} \left[ \frac{\rho(r)}{\rho_{\mathrm{p}}} \right]^{1/3},
 \eea
-with $  \rho_p  = 3\times10^{14}\ {\rm g/cm}^3, T_R = 30$ MeV, and taking $ n = 5 $. The optical depth is given by 
+with $  \rho_{\mathrm{p}}  = 3\times10^{14}\ {\rm g/cm}^3$, $T_{\mathrm{R}} = 30$~MeV, 
+and $n = 5$. \arz{What is R?}
+The optical depth is given by 
 \beq
-\tau = \int_{r_x}^{\infty} \kappa \rho dr,
+\tau = \int_{r_x}^{\infty}\, \kappa \rho\,  \dd r,
 \eeq
-where $ \kappa$ is the opacity.  To find the opacity, we start from the reduced mean Rosseland opacity 
+where $ \kappa$ is the opacity.  To find the opacity, we start from the reduced mean 
+Rosseland mean opacity 
 \beq
-\frac{1}{\kappa \rho} = \int_{m_x}^{\infty} \frac{15}{4 \pi^4 T^5} \frac{E_A^2 e^{E_A/T} \sqrt{E_A^2 - m_A^2}}{(e^{E_A/T}-1)^2} l_A dE_A,
+\frac{1}{\kappa \rho} = 
+\frac{15}{4 \pi^4 T^5}\, \int_{m_x}^{\infty}\, \frac{E_A^2 e^{E_A/T} \sqrt{E_A^2 - m_A^2}}{(e^{E_A/T}-1)^2}\, l_A\, \dd E_A,
 \eeq
@@
 
-The inverse mean free path can readily be obtained by modifying $ Q_i $, the expression for the energy loss rate, as follows: removing the factor of $ E_A $ and the phase space integral over $ \qa $, and adding a factor of $ e^{E_A/T} $ for detailed balance.
+The inverse mean free path can readily be obtained by modifying $ Q_i $, 
+the expression for the energy loss rate, as follows: removing the factor of $ E_A $ 
+and the phase space integral over $ \qa $, and adding a factor of $ e^{E_A/T} $ for detailed balance. 
+\arz{I'm not sure that I follow this somewhat cavalier statement about detailed balance. Can someone 
+please explain this to me when we meet. In my earlier rounds of thinking about this, I took that factor 
+at face value as given, assuming I'd eventually be able to figure out where it comes from.} 
 This gives the inverse mean free path as a function of mass and coupling. 
-Again the required integration is performed numerically.
+Again, we perform the required integration numerically. \arz{Do you use the same software package here? 
+If so, you must say so.} 
 This then allows the calculation of $ \kappa_x $. 
-The inverse opacities for the $pn$ and $pp$ processes add, giving the total opacity $ \kappa^{-1} = \kappa_{pp}^{-1} + \kappa_{pn}^{-1} $
+\arz{By $\kappa_{\mathrm{x}}$ I suspect that you mean either $\kappa_{\mathrm{pp}}$ or 
+$\kappa_{\mathrm{pn}}$. However you never say this. You should state what you mean clearly and explicitly.  
+In this particular case, it is probably more cumbersome to define $\kappa_{\mathrm{x}}$ than it is worth because you 
+will only use it one time.} 
+The inverse opacities for the $pn$ and $pp$ processes add, 
+giving the total opacity $ \kappa^{-1} = \kappa_{pp}^{-1} + \kappa_{pn}^{-1} $
 
-Having obtained an expression for $ \kappa $, we can now find the optical depth as follows: define a new quantity $ \tau_R = \kappa_R \rho_R R $. We then have 
-\beq \kappa \rho R = \tau_R (\frac{\rho}{\rho_R})^2 (\frac{T_R}{T})^{3/2}  \eeq
-This is combined with the expressions for the density and temperature as a function of r and plugged in to the integral expression for the optical depth to obtain 
-\bea \tau_x &=& \int_{r_x}^{\infty} \tau_R (\frac{R}{r})^{3n/2} \\
- &=& \frac{\tau_r}{\frac{3n}{2}-1} (\frac{T_A}{T_R})^{(9/2-3/n)} \eea
-and the bound on the coupling is finally found by requiring  $ \tau_x(\varepsilon,m_A) \le 2/3 $
+Having obtained an expression for $ \kappa $, we can now find the optical depth as follows. 
+Define a typical optical depth as $\tau_R = \kappa_R \rho_R R $. We then have 
+\beq 
+\kappa \rho R = \tau_R \left( \frac{\rho}{\rho_R} \right)^2 \left( \frac{T_R}{T} \right)^{3/2}.
+\eeq
+%
+This can be combined with the previous expressions for the density and temperature as a function of position 
+and plugged in to the integral expression for the optical depth to obtain 
+\bea 
+\tau_x &=& \int_{r_x}^{\infty}\, \tau_R \left( \frac{R}{r} \right)^{3n/2} \dd r \\
+ &=& \frac{\tau_r}{\frac{3n}{2}-1} \left( \frac{T_A}{T_R} \right)^{(9/2-3/n)}. 
+ \eea
+ The bound on the coupling is obtained by requiring  $ \tau_x(\varepsilon,m_A) \le 2/3 $
+ \arz{Is it possible to include a few further details here?
 
-\subsection{Phase Space Integration}
+ Also, it seems as though you can check the consistency of your assumptions can 
+ be checked within this calculation. For example, you can actually use this calculation 
+ to estimate the radius at which $\tau=2/3$ and see if it is actually close to 
+ $10$~km. Have you done this?
+ }
 
-In every case
-
-Once the integration is complete the calculation of the trapping and streaming limits is a straightforward application of the equations previously derived, and proceeded as outlined above.
-The decay limit is somewhat harder, since $ \varepsilon $ appears on both sides of the equation.
-Again we employed an unsubtle approach to solving the problem: $ \varepsilon $ was set to an arbitrary value where the constraint was satisfied, and then iteratively reduced until the constraint was no longer satisfied.
-This obviously introduces another source of error, but with a sufficiently small interval in $ \varepsilon $ this is negligible.
-The one further slight complication is that at after a certain value of $ M_A $ the decay limit rapidly goes to zero, at which point the procedure was terminated.
+As we stated in the previous subsection, the approximate treatment of the upper limit of the exclusion region 
+is justified by the fact that values of $\varepsilon$ close to the upper limit of the exclusion region are 
+ruled out by independent, terrestrial experiments.
 
@@
 
-Let's put some text here.
+The considerations of the previous section lead to constraints on the 
+viable parameters for dark electromagnetism models of SIDM.
 

### 2017-04-04 draft.tex
Edited the introduction.

@@
 
-A nearly overwhelming preponderance of observational evidence indicates that a form of nonrelativistic, nonbaryonic, 
-dark matter constitutes the vast majority of mass in the Universe and drives the formation of cosmic structure. 
+An overwhelming preponderance of observational evidence indicates that a form of nonrelativistic, nonbaryonic, 
+dark matter constitutes the majority of mass in the Universe and drives the formation of cosmic structure. 
 The pace of the quest to identify the dark matter is accelerating on many fronts. Weakly-interacting massive 
@@
 Dark matter particles that interact with standard model particles only weakly, while interacting among themselves 
-much more strongly have been studied as an alternative to WIMP scenarios in many contexts 
+much more strongly have been studied as an alternative to WIMP scenarios in numerous contexts 
 \cite{carlson_etal92,deLaix_etal95,atrio-barandela_davidson97,spergel_steinhardt00,hogan_dalcanton00,mohapatra_teplitz00,
 dave_etal01,hisano_etal04,hisano_etal05,pospelov_etal08,arkani-hamed_etal08a,lattanzi_silk08,ackerman_etal09,feng_etal09,
-kong_etal15} \arz{Need to add some more recent references here.} 
+kong_etal15} \arz{Cameron: Please review the literature and add some more recent references here. 
+I know that Annika Peter has a few papers and Jonathan Feng probably has some more. 
+Ensuring that you are up to date on these papers is important.} 
 and constraints on self-interacting dark matter (SIDM) models have been explored by many authors \cite{yoshida_etal00,gnedin_ostriker01,miralda-escude02,randall_etal08,kamionkowski_profumo08,zentner09,robertson_zentner09,pieri_etal09,spolyar_etal09,finkbeiner_etal09,
@@
 In this paper, we revisit and update astrophysical constraints on SIDM models from 
-supernova cooling, finding constraints that are considerably less restrictive than in 
-previous work. 
-\arz{Might want to add a comment about SIDM affecting small-scale structure in CDM, the satellites problems and core/cusp problems.}
+supernova cooling.
 
@@
 bosons ($M \lesssim 100$~GeV) can be constrained astrophysically using supernovae, particularly 
-SN1987A. Light gauge bosons will be produced within the hot supernovae core and 
-radiated from the supernova. This non-standard energy loss mechanism can result in an energy loss rate 
-from the supernova core that is inconsistent with observations of SN1987A, analogous to the 
-classic constraint on axions \cite{turner88,raffelt96_book}. This mechanism was already exploited by 
-\cite{dent_etal12} (and \cite{rrapaj_reddy16}, with a slight modification) (\arz{Cameron, add others of which you may be aware.}) 
-to constraint dark electromagnetism models of SIDM in which the self-interaction arises from a Yukawa potential 
-and the vector boson is kinetically mixed with the standard model photon.
+SN1987A. Light gauge bosons will be produced within the hot supernova core, primarily through 
+brehmsstrahlung, and radiated. This non-standard energy loss mechanism can result in an energy loss rate 
+from the supernova core that is inconsistent with observations of neutrinos from SN1987A, 
+analogous to the classic constraint on axions \cite{turner88,raffelt96_book}. 
+This effect has already been exploited by Dent et al. \cite{dent_etal12}, Rrapaj and Reddy \cite{rrapaj_reddy16}, and 
+Hardy and Lasenby \cite{hardy_lasenby17} \arz{Cameron, add others of which you may be aware.}
+to constraint dark electromagnetism models in which the new gauge boson, the so-called dark photon, 
+is kinetically mixed with the standard model photon. The SN1987A constraint places a limit on the mixing parameter.
 
-As we mentioned above, we find SN1987A constraints on dark photon SIDM models that are considerably different 
-from those of \cite{dent_etal12}. If correct, our result has important consequences. 
-The Snowmass white paper by Kaplinghat, Tulin, and Yu \cite{kaplinghat_etal13_whitepaper} nicely 
-summarizes a variety of constraints on dark electromagnetism models of SIDM (many details can be 
-found in the the very informative work of Ref.~\cite{bjorken_etal09}). 
-One point that is clear from Ref.~\cite{kaplinghat_etal13_whitepaper} is that there exists 
-only a narrow range of viable photon mixing parameters that can lead to production of SIDM in the early universe and 
-interesting effects on cosmological structure formation, while simultaneously evading all constraints, 
-including the constraint of Ref.~\cite{dent_etal12}. Our results suggest that the SN1987A constraints from 
-Ref.~\cite{dent_etal12} are too restrictive. The constraints that we quote reveal a region of unrestricted mixing 
-parameters that ranges over two orders of magnitude. Interestingly, the parameter space opened by our updated 
-constraints corresponds to SIDM models that may have a significant impact on cosmological structure formation, 
-particularly the structures of dark matter halos and galaxies.
+We initiated our study because of a number of ambiguities appearing in the previous literature on this subject. 
+In particular, we could not reproduce the constraints of Ref.~\cite{dent_etal12}. During the course of our 
+study, we identified a number of errors in the analysis of Ref.~\cite{dent_etal12}. First, it is straightforward 
+to demonstrate that the kinematical relationships given in Appendix A of Ref.~\cite{dent_etal12} are 
+incorrect. Second, the squared matrix elements given in Eq.~(A3) and Eq.~(C18) of Ref.~\cite{dent_etal12} must 
+be incorrect. We have not been able to identify the errors which led to these incorrect expressions; however, 
+there must have been several oversights in the analysis of Ref.~\cite{dent_etal12}. For example, the squared 
+matrix elements in Eq.~(A3) and Eq.~(C18) do not obey the correct symmetries under interchange of incoming 
+and/or outgoing momenta. Furthermore, Ref.~\cite{dent_etal12} neglects the mass of the gauge boson, which 
+is legitimate in the classic case of the $\sim$meV-mass axion, but not in the present context. Finally, Ref.~\cite{dent_etal12} 
+employed an inconsistent model for the permitted energy loss rate from the supernova interior. Our work amounts 
+primarily to repeating the calculation of Ref.~\cite{dent_etal12} in order to rectify these oversights. Our primary 
+calculation treats nucleon scattering via one-pion exchange (OPE). We have repeated this analysis 
+using and effective field theory for the nucleon interaction and find very similar results so we do not 
+report on those in detail. \arz{I think we may want to add back in the EFT calculation for this paper. 
+That would at least give this paper something a bit unique when compared to the other papers on 
+the subject.}
 
-The discrepancy between our result and that of Ref.~\cite{dent_etal12} arises due to multiple factors. First, it is straightforward to 
-demonstrate that the kinematical relationships in given in Appendix A of Ref.~\cite{dent_etal12} are incorrect. Second, the 
-squared matrix elements given in Eq.~(A3) and Eq.~(C18) of Ref.~\cite{dent_etal12} are incorrect. Our squared matrix elements 
-are considerably more complicated. Multiple errors must have led to the incorrect squared matrix elements in 
-Ref.~\cite{dent_etal12}. At the very least, these errors include simplification using the incorrect kinematics and neglect of the 
-mass of the gauge boson (which, while legitimate for the $\sim$meV-mass axion, is not justified in this context). 
-Discrepancies in addition to those kinematical issues must also be present, 
-the causes of which are not apparent from the exposition, because the squared matrix 
-elements in Eq.~(A3) and Eq.~(C18) of Ref.~\cite{dent_etal12} do not obey the 
-correct symmetries under interchange of the incoming or outgoing baryon momenta. 
-Given these errors, we suggest that our results should supercede these previously-published constraints.
+As we were completing our manuscript, two related papers were published. Rrapaj and Reddy \cite{rrapaj_reddy16} 
+computed bounds on mixing of the dark and standard model photons using a soft radiation approximation (SRA) 
+for dark photon Brehmsstrahlung. This has the distinct advantage of enabling nucleon scattering data to be used 
+directly in the estimation of the Brehmsstrahlung rate, but is only approximate because at large dark photon masses 
+the radiated dark photons carry off considerable momentum and energy. We have been able to reproduce the 
+result of Rrapaj and Reddy \cite{rrapaj_reddy16} and find that the SRA plausibly results in only a factor or 
+$\sim 3$ underestimate of the upper bound on the dark photon mixing parameter at most. Moreover, 
+our OPE results agree well with the SRA calculation of Rrapaj and Reddy \cite{rrapaj_reddy16}. Nonetheless, 
+Ref.~\cite{rrapaj_reddy16} quote results very similar to those of Dent et al. \cite{dent_etal12}. We find, 
+rather remarkably, that the various errors in the analysis of Ref.~\cite{dent_etal12} conspire to yield a constraint that 
+is very similar to the correct answer.
+
+More recently, Hardy and Lasenby \cite{hardy_lasenby17} studied bounds on these same models (and others) 
+including plasma effects. For simplicity, we have not included these plasma effects in our calculations. Hardy 
+and Lasenby base their calculation off of the SRA of Ref.~\cite{rrapaj_reddy16}. Consequently, 
+for dark photon masses $\gtrsim 10$~MeV they find very similar results to Ref.~\cite{rrapaj_reddy16} as well 
+as the constraints we present in this manuscript. For dark photon masses $\lesssim 10$~MeV, Hardy and 
+Lasenby demonstrate that constraints on the dark photon mixing parameter are significantly weaker than 
+one finds when neglecting plasma effects \cite{hardy_lasenby17}.
+
+It is important to delineate correctly the range of the viable parameter space for SIDM models. 
+The parameter space available to dark electromagnetism models of SIDM has been studied extensively 
+not only in the aforementioned papers, but also in the work of Bjorken et al. \cite{bjorken_etal09} and 
+the Snowmass white paper by Kaplinghat, Tulin, and Yu \cite{kaplinghat_etal13_whitepaper}. One 
+point that is clear from previous work is that there is at most only a slim sliver of parameter space that 
+can simultaneously yield the correct relic abundance of SIDM through thermal production, 
+have interesting effects on cosmological structure formation, and 
+evade all constraints including the constraints from SN1987A. 
+In accord with Ref.~\cite{rrapaj_reddy16} and Ref.~\cite{hardy_lasenby17}, we find that 
+the constraints quoted in Ref.~\cite{dent_etal12} are too restrictive, but only by a factor 
+of $\sim 4$ due to a conspiratorial cancellation of errors in Ref.~\cite{dent_etal12}. 
+Hardy and Lasenby go on to demonstrate that these constraints are significantly too 
+restrictive for dark photon masses $\lesssim 10$~MeV due to plasma effects.
 
@@
 Section~\ref{section:computational} and present our primary results in Section~\ref{section:results}. 
+We stress only those points that are key to understanding the relationship between our work 
+and the work of both Dent et al. in Ref.~\cite{dent_etal12} and Rrapaj and Reddy in Ref.~\cite{rrapaj_reddy16}. 
 We summarize our work and draw conclusions in Section~\ref{section:conclusions}.
@@
 
-%----- Computational Details
+%----- Methods
 \section{Methods}
@@
 brehmsstrahlung will increase with $\varepsilon$; however, $\varepsilon$ can become sufficiently large 
-that the radiated gauge bosons do not escape the supernova. This happens if the $\Aprime$ either decay to 
-standard model particles or interact with standard model particles prior to exiting the supernova core. 
+that the radiated gauge bosons do not escape the supernova. This happens if the $\Aprime$ particles 
+either decay to or interact with standard model particles prior to exiting the supernova core. 
 In either case, the energy is not lost and the $\Aprime$ does not provide a cooling channel for the supernova. 
@@
 manner. We estimate $\Aprime$ decay and scattering probabilities, and the upper limits on the $\varepsilon$ 
-constraints in this section as well.
+constraints in this section as well. However, we note that terrestrial experiments generally rule out 
+mixing parameters higher than the upper limits of the SN1987A forbidden region, so a precise estimate 
+of these upper limits is not necessary.
 
+%-- Brehmsstrahlung--	
 \subsection{Brehmsstrahlung of $\Aprime$ Bosons}
@@
 
-\begin{figure}[th]
-	\includegraphics[width=9cm]{endtoend.png}
-	\caption{A comparison of the final result for the excluded region with the result from Ref.~\cite{dent_etal12}.
-The excluded region is clearly significantly less restrictive, and opens up the region of parameter space for $\varepsilon \approx  1e-8-9 $.
-\arz{Cameron, some similar comments as for Figure 1. Can we write numbers as "$10^{-9}$" rather 
-than "1e-09" and so on? Can we make the axis labels and tick mark labels larger?}}
-\label{fig:constraint}
-\end{figure}
-
-\begin{figure}[th]
-\includegraphics[width=9cm]{stages.eps}
-\caption{The changes in the bounds generated as each stage of the calculation departs from Ref.~\cite{dent_etal12}. Interestingly the kinematics have apparently relatively little effect.
-\arz{Cameron, several to-do items for this figure. On the y-axis, the symbol should be "$\varepsilon$" rather than 
-"e". Can we write numbers as "$10^{-9}$" rather than "1e-09" and so on? Can we make the axis labels and 
-tick mark labels larger? Can you make all of the lines thicker? Can you make each of the four lines a distinct color?}
+\begin{figure*}[th]
+\includegraphics[width=14cm]{constraint.pdf}
+\caption{
+Constraints on dark photon models. 
 }
-\end{figure}
+\label{fig:constraints}
+\end{figure*}
 

### 2017-04-04 draft.tex
put in tweaked constraint figure
Finished a round of editing. Will complete the abstract and conclusion after we talk about the paper.

@@
 There are two processes to consider in order to estimate the rate of energy loss via $\Aprime$ brehmsstrahlung. The first is  
-proton-proton (pp) scattering with the bremsstrahlung of the dark photon off the proton; $p+p \rightarrow p+p+A$. The 
-second is proton-neutron (pn) scattering with bremsstrahlung off of either the proton or the charged pion; 
-$p+n \rightarrow p+n+A$. We estimate the rates for these processes using the one-pion exchange (OPE) 
+proton-proton (pp) scattering with the bremsstrahlung of the dark photon off the proton; $p+p \rightarrow p+p+\Aprime$. 
+The second is proton-neutron (pn) scattering with bremsstrahlung off of either the proton or the charged pion; 
+$p+n \rightarrow p+n+\Aprime$. We estimate the rates for these processes using the one-pion exchange (OPE) 
 approximation for nucleon interactions. In the pp case, there are eight tree-level diagrams, 
@@
 
+%-------------- NP Feynman Diagram
+\begin{figure}
+\includegraphics[width=8cm]{npdiagram.pdf}
+\caption{One of the five Feynman diagrams for the np process. This particular diagram shows 
+internal brehmsstrahlung off of the charged pion. The remaining four diagrams are analogous to the 
+pp diagram shown in Fig.~\ref{fig:ppdiagram}. In the case of the np processes, there are only four 
+diagrams for brehmsstrahlung off of the external legs because two of the legs correspond to the 
+uncharged neutron.}
+\label{fig:npdiagram}
+\end{figure}
+
 Evaluating these diagrams is tedious, but very straightforward. The calculation differs 
-from the well-known axion bremsstrahlung calculation, because the mass of the $\Aprime$ boson is not 
-necessarily negligible in the kinematic region of interest for supernova explosions.
-The correct kinematical relations are 
+from the well-known axion bremsstrahlung calculation exploited in a similar context \cite{raffelt96_book}, 
+because the mass of the $\Aprime$ boson is not necessarily negligible in the kinematic 
+region of interest for supernova explosions. The correct kinematical relations are 
 %
@@
 \arz{Cameron, can you double check this? I think there were some errors in the momenta and in the relative 
-signs of the diagrams. I tried to fix them. Please go over this carefully.}
+signs of the diagrams. I tried to fix them. Please go over this VERY carefully.}
+
 The eight diagrams contribute the following eight terms to the pp amplitude, 
@@
 %
-where the dark photon polarization is given by $\epsilon^{\nu}$. The squared amplitude is given by 
-%
-\begin{equation}
-\vert \mathcal{M}_{\mathrm{pp}} \vert^2 = \sum_{s_1,s_2}\, \left\vert \sum_{i=1}^{8}\, M_i \right\vert^2, 
-\end{equation}
-%
-where the first summation is over the incoming proton polarizations. These expressions are identical to those 
+where the dark photon polarization is given by $\epsilon^{\nu}$. These expressions are identical to those 
 given in Ref.~\cite{dent_etal12}; however, they do not simplify significantly if the correct kinematics are used. 
 Unfortunately, with the kinematical relations above, the squared amplitude does not yield a tidy expression 
-for the spin-averaged squared matrix element. Our result 
-contains over 200 terms, so we do not reproduce it here for reasons of convenience. However, we note that 
-our result for $\vert \mathcal{M}_{\mathrm{pp}} \vert^2$ is symmetric under exchange of $k$ and $l$ as required.
+for the spin-averaged squared matrix element. Our result contains over 200 terms, 
+so we do not reproduce it here for reasons of convenience. However, we note that 
+our result for $\vert \mathcal{M}_{\mathrm{pp}} \vert^2$ is symmetric 
+under exchange of $k$ and $l$ as required.
 
-The pn process contain four diagrams analogous to the the diagrams for the pp process (there are only four, of course, 
+The pn process contains four diagrams analogous to the the diagrams for the pp process (only four, of course, 
 because the neutrons cannot radiate the $\Aprime$). The new diagram that is relevant in the pn process is shown in 
@@
 %
-The pn processes likewise yield a squared amplitude, 
+The pn processes likewise yields a squared amplitude, 
 $\vert \mathcal{M}_{\mathrm{pn}} \vert^2$ that is unwieldy, so we do not give the 
-the full expression here.
-
-%-------------- NP Feynman Diagram
-\begin{figure}
-\includegraphics[width=8cm]{npdiagram.pdf}
-\caption{One of the five Feynman diagrams for the np process. This particular diagram shows 
-internal brehmsstrahlung off of the charged pion. The remaining four diagrams are analogous to the 
-pp diagram shown in Fig.~\ref{fig:ppdiagram}. In the case of the np processes, there are only four 
-diagrams for brehmsstrahlung off of the external legs because two of the legs correspond to the 
-uncharged neutron.}
-\label{fig:npdiagram}
-\end{figure}
+the full expression here. We provide mathematica notebooks detailing our 
+computation of the amplitudes with this submission.
 
@@
 
-The first and simplest bound that may be obtained arises from assuming that all $\Aprime$ particles produced in the supernova core 
+The first and simplest bound that may be obtained arises from 
+assuming that all $\Aprime$ particles produced in the supernova core 
 leave the supernova, carrying their energies with them. The constraint can be derived simply by 
@@
 \begin{equation}
-d\Pi = \frac{\dd^3 \vec{q}_{\mathrm{A}'}}{(2\pi)^3 2E_{\mathrm{A}'}}\, \prod_{i=1}^{4}\, \frac{\dd^3 \vec{p}_i}{(2\pi^3) 2E_1}
+d\Pi = \frac{\dd^3 \vec{q}_{\mathrm{A}'}}{(2\pi)^3 2E_{\mathrm{A}'}}\, \prod_{j=1}^{4}\, \frac{\dd^3 \vec{p}_j}{(2\pi^3) 2E_j}
 \end{equation} 
@@
 $f(p)$ are the phase-space densities of the incoming nucleons, and 
-the index $i$ refers to either the pp or pn processes. 
+the index $i$ on $Q_i$ refers to either the pp or pn processes. 
 The nucleons in the core are comfortably non-degenerate and non-relativistic, 
@@
 To obtain the dark gauge boson luminosity from $Q_{\mathrm{pp}}$ and $Q_{\mathrm{pn}}$, 
-we assumed that $\Aprime$ production takes place in a stellar core of radius $\sim 1$~km, so that 
-the total luminosity of $\Aprime$ is 
+we assumed that $\Aprime$ production takes place in a stellar core of radius $\sim 1$~km, 
+so that the total luminosity of $\Aprime$ is 
 %
 \begin{equation}
-L_{\mathrm{A}'} = V (Q_{\mathrm{pp}} + Q_{\mathrm{pn}})
+L_{\mathrm{A}'} = V (Q_{\mathrm{pp}} + Q_{\mathrm{pn}}),
 \end{equation}
 %
-where $V$ is the volume of the sphere. Clearly, $L_{\mathrm{A}'}$ is proportional to $\varepsilon^2$. 
-Writing $L_{\mathrm{A}'} = \varepsilon^2 I_{\mathrm{A}'}(m_{\mathrm{A}'},T)$, as in Ref.~\cite{dent_etal12}, 
-and $L_{\nu}$ as the neutrino luminosity, we can write the constraint as 
+where $V$ is the volume of the sphere, and the luminosity per unit mass within the core is 
+%
+\begin{equation}
+\left( \frac{L_{\mathrm{A'}}}{M} \right) = \frac{Q_{\mathrm{pp}} + Q_{\mathrm{pn}}}{\rho}, 
+\end{equation}
+%
+where $\rho = 3 \times 10^{14}\, \mathrm{g/cm}^3$ is the mass density of the core\footnote{
+We use the symbol $\left( L_{\mathrm{A'}}/M \right)$ for the luminosity per unit mass rather than 
+the more conventional symbol $\epsilon_{\mathrm{A'}}$ in order to avoid confusion with the 
+mixing parameter $\varepsilon$.}. Following previous studies, the energy loss rate into novel 
+particles cannot exceed 
+%
+\begin{equation}
+\left( \frac{L_{\mathrm{max}}}{M} \right) \approx 10^{19} \, \frac{\mathrm{erg}}{\mathrm{g}\, \mathrm{s}}
+\end{equation}
+%
+without significantly reducing the duration of the neutrino burst observed at Earth for SN1987A 
+\cite{raffelt96_book}. Writing $(L_{\mathrm{A'}}/M) = \varepsilon^2 I_{\mathrm{A'}}(m_{\mathrm{A'}},T)$, 
+we delineate the constraint on the dark photon mixing parameter by 
 %
@@
 \label{eq:bound1}
-\varepsilon \lesssim \sqrt{\frac{L_{\nu}}{I_{\mathrm{A}'}(m_{\mathrm{A}'}, T)}}.
+\varepsilon \lesssim \sqrt{\frac{(L_{\mathrm{max}}/M)}{I_{\mathrm{A}'}(m_{\mathrm{A}'}, T)}}.
 \end{equation}
 %
-Following SOMEBODY \arz{We need a citation here.}, we derive a constraint taking 
-$L_{\nu} \approx 10^{53}\, \mathrm{erg/s} \approx 4 \times 10^{37}\, \mathrm{MeV}^2$.
+At this point, we note that Dent et al. in Ref.~\cite{dent_etal12} took a value of 
+$(L_{\mathrm{max}}/M)$ approximately three orders of magnitude larger than 
+this accepted value. Remarkably, this nearly canceled the errors in their evaluation of 
+$Q_{\mathrm{pp}}$ and $Q_{\mathrm{np}}$ so that they quote constraints that are 
+within an order of magnitude of the correct result.
 
@@
 
-The constraint from the streaming limit above provides an upper bound on the allowed coupling 
-from the production on $\Aprime$ bosons. In order to function as an effective cooling channel, the 
-radiated dark gauge bosons must escape the supernova in sufficient numbers. 
-As the coupling increases, so do processes that prevent this escape, 
-and so the excluded region has an upper bound, above which the luminosity again drops below the 
-neutrino luminosity. The first such limit may be found by considering decay of the dark bosons 
-into Standard Model particles. Standard model particles will scatter and thermalize 
-on a timescale much shorter than the timescale for the evolution of the core, so decays 
-contribute nothing to the cooling.
+One upper limit to the excluded values of $\varepsilon$ may be found by considering 
+decay of the dark bosons into Standard Model particles. Standard model particles will 
+scatter and thermalize on a timescale much shorter than the timescale for the evolution 
+of the core, so decays contribute little to the cooling of the stellar core.
 
@@
 little bit. Please review this.}
+
 The dark boson has a typical lifetime of
@@
 \arz{I have a few questions here. First, what did you choose for the value or $r_{\mathrm{decay}}$? This must 
-be specified.
+be specified explicitly in the text. Please do so as soon as possible.
 
@@
 the decays only become more important than trapping for masses $m_{\mathrm{A}'} \gtrsim 30\, \mathrm{MeV}$. 
-This suggests that we should use the non-relativistic limit here. Do I misunderstand something?}
+This suggests that we should use the non-relativistic limit here. Do I misunderstand something? Let us address this 
+as soon as possible. Please let me know what you think.}
 
@@
 \beq
-\mathcal{L}_t  = 4\pi \rdp^2 T_{\mathrm{A}'}^4 \sigma,
+L_{\mathrm{A'}}  = 4\pi \rdp^2 T_{\mathrm{A}'}^4 \sigma,
 \eeq
@@
 \eeq
-where $ \kappa$ is the opacity.  To find the opacity, we start from the reduced mean 
-Rosseland mean opacity 
+where $ \kappa$ is the opacity, which we take to be the Rosseland mean 
+%
 \beq 
-\frac{1}{\kappa \rho} = 
-\frac{15}{4 \pi^4 T^5}\, \int_{m_x}^{\infty}\, \frac{E_A^2 e^{E_A/T} \sqrt{E_A^2 - m_A^2}}{(e^{E_A/T}-1)^2}\, l_A\, \dd E_A,
+\frac{1}{\kappa \rho} = \frac{15}{4 \pi^4 T^5}\, \int_{M_{\mathrm{A'}}}^{\infty}\, 
+\frac{E_{\mathrm{A'}}^2\, e^{E_{\mathrm{A'}}/T} 
+\sqrt{E_{\mathrm{A'}}^2 - m_{\mathrm{A'}}^2}}
+{(e^{E_{\mathrm{A'}}/T}-1)^2}\, l_{\mathrm{A'}}\, \dd E_{\mathrm{A'}},
 \eeq
-where $ l_A $ is the mean free path.
+where $l_{\mathrm{A'}}$ is the mean free path.
 
@@
 If so, you must say so.} 
-This then allows the calculation of $ \kappa_x $. 
-\arz{By $\kappa_{\mathrm{x}}$ I suspect that you mean either $\kappa_{\mathrm{pp}}$ or 
-$\kappa_{\mathrm{pn}}$. However you never say this. You should state what you mean clearly and explicitly.  
-In this particular case, it is probably more cumbersome to define $\kappa_{\mathrm{x}}$ than it is worth because you 
-will only use it one time.} 
+This then allows the calculation of $\kappa_{\mathrm{pp}}$ and $\kappa_{\mathrm{pn}}$, 
+which are the opacities due to inverse brehmsstrahlung for proton-proton and proton-neutron 
+processes respectively. These dominate the opacity of the star to $A'$ propagation. 
 The inverse opacities for the $pn$ and $pp$ processes add, 
@@
 \bea 
-\tau_x &=& \int_{r_x}^{\infty}\, \tau_R \left( \frac{R}{r} \right)^{3n/2} \dd r \\
+\tau &=& \int_{r_x}^{\infty}\, \tau_R \left( \frac{R}{r} \right)^{3n/2} \dd r \\
  &=& \frac{\tau_r}{\frac{3n}{2}-1} \left( \frac{T_A}{T_R} \right)^{(9/2-3/n)}. 
  \eea
- The bound on the coupling is obtained by requiring  $ \tau_x(\varepsilon,m_A) \le 2/3 $
- \arz{Is it possible to include a few further details here?
+ The bound on the coupling is obtained by requiring  $ \tau(\varepsilon,m_A) \le 2/3 $
 
- Also, it seems as though you can check the consistency of your assumptions can 
+ \arz{It seems as though you can check the consistency of your assumptions can 
  be checked within this calculation. For example, you can actually use this calculation 
  to estimate the radius at which $\tau=2/3$ and see if it is actually close to 
- $10$~km. Have you done this?
- }
+ $10$~km. Have you done this?}
 
@@
 \caption{
-Constraints on dark photon models. 
+Constraints on dark photon models. Our primary result is the excluded region 
+in the $varepsilon$-$m_{\mathrm{A'}}$ plane shaded in blue. 
+\arz{Cameron, can you describe clearly each line in this caption. Yellow is 
+too hard to see, so please choose another color for this line.}
 }
-\label{fig:constraints}
+\label{fig:constraint}
 \end{figure*}
@@
 The considerations of the previous section lead to constraints on the 
-viable parameters for dark electromagnetism models of SIDM.
+viable parameters for dark electromagnetism models of SIDM, in particular, 
+on the mixing parameter $\varepsilon$ as a function of the dark photon mass $m_{\mathrm{A'}}$. 
+The excluded region is depicted in Fig.~\ref{fig:constraint} as the shaded blue region. The 
+lower limit of our excluded region lies at a value of $\varepsilon$ about a factor of four 
+larger than that of Dent et al. in Ref.~\cite{dent_etal12} and is in excellent agreement 
+with the result of Rrapaj and Reddy \cite{rrapaj_reddy16} despite the fact that they work 
+with an SRA approximation and we work with a OPE model.
+
+Figure~\ref{fig:constraint} shows several other estimates of the lower bound on 
+$\varepsilon$ in an effort to elucidate possibly confusing points in the existing 
+literature. As we stated earlier, the work of Ref.~\cite{dent_etal12} contained several 
+errors that partially cancelled each other. The black line in Fig.~\ref{fig:constraint} represents 
+our effort to reproduce the result of Ref.~\cite{dent_etal12} using (incorrectly) the equations 
+that they quote in their paper. However, Ref.~\cite{dent_etal12} had significant errors in 
+their calculations of the dark photon luminosity and chose an energy loss rate three orders 
+of magnitude higher than other practitioners. Adopting the Dent et al. \cite{dent_etal12} 
+equations for the dark photon luminosity, but the correct limit on the energy loss rate, 
+results in the red line in Fig.~\ref{fig:constraint}. As Ref.~\cite{dent_etal12}, our primary 
+result uses a OPE model for nucleon interactions, so the entirety of the difference between 
+the red line and the lower bound of our exclusion region stems from an incorrect estimate 
+of the brehmsstrahlung rate in Ref.~\cite{dent_etal12}.
+
+Rrapaj and Reddy \cite{rrapaj_reddy16} estimated $A'$ luminosity 
+using the SRA for nucleon interactions, which enabled them to use 
+nuclear scattering data in the estimation of the brehmsstrahlung rate. 
+This approach overcomes the shortcomings of the OPE approximation, 
+though at high dark photon masses this approximation breaks down. 
+We have repeated the calculation in the SRA as described in 
+Rrapaj and Reddy \cite{rrapaj_reddy16} and our result is 
+shown as the yellow line in Fig.~\ref{fig:constraint}. 
+Our SRA result is in excellent agreement with Ref.~\cite{rrapaj_reddy16}. It is 
+also worth noting that the SRA and OPE approximations yield constraints 
+on $\varepsilon$ that agree quite well with each other. This suggests, of course, 
+that the discrepancy between Ref.~\cite{dent_etal12} and Ref.~\cite{rrapaj_reddy16} 
+stems primarily from errors in Ref.~\cite{dent_etal12} and not to the OPE model 
+of nucleon interactions. In an effort to estimate 
+the possible shortcomings of the SRA approximation, the green line in 
+Fig.~\ref{fig:constraints} shows the lower bound on the excluded region that 
+we drive using the SRA along with OPE expressions for nucleon scattering 
+cross sections. As one can see, the SRA is in good agreement with the full 
+OPE bound. Consequently, we suggest that use of the SRA in this context 
+results in an overestimate of the lower limit on $\varepsilon$ of less than 
+a factor or three.
 
 %--------------------------- CONCLUSIONS
-\section{Discussion and Conclusions}
+\section{Discussion}
 \label{section:conclusions}
 
-	The revised approach produce constraints that are significantly weaker than the previous work, and that largely reproduce constraints already obtained from beam dump experiments.
+We have revisited constraints on SIDM models in which the 
+self-interaction arises from dark electromagnetism. We have 
+constrained the mixing parameter for models in which the dark photon 
+mixes with the standard model photon through a kinetic mixing term.
 
@@
 
+\arz{CBM was supported somehow by AKL.}
 AKL was supported in part by NSF grant PHY-1519175. 
+ARZ was supported in part by the DoE through Grant DE-SC0007914 and by 
+the Pittsburgh Particle physics Astrophysics and Cosmology Center (Pitt PACC) 
+at the University of Pittsburgh.
 

### 2017-04-20 draft.tex
Edits
Should finally be the up to date version

@@
 \newcommand{\arz}[1]{{{\bf{\color{BrickRed}[ARZ: #1]}}}}
+\newcommand{\cbm}[1]{{{\bf{\color{Green}[CBM: #1]}}}}
 
@@
 SN1987A. Light gauge bosons will be produced within the hot supernova core, primarily through 
-brehmsstrahlung, and radiated. This non-standard energy loss mechanism can result in an energy loss rate 
+brehmsstrahlung \cbm{This is probably stupid, but shouldn't it be bremsstrahlung, without the first h?}, and radiated. This non-standard energy loss mechanism can result in an energy loss rate 
 from the supernova core that is inconsistent with observations of neutrinos from SN1987A, 
@@
 using and effective field theory for the nucleon interaction and find very similar results so we do not 
-report on those in detail. \arz{I think we may want to add back in the EFT calculation for this paper. 
-That would at least give this paper something a bit unique when compared to the other papers on 
-the subject.}
+report on those in detail.
 
@@
 computed bounds on mixing of the dark and standard model photons using a soft radiation approximation (SRA) 
-for dark photon Brehmsstrahlung. This has the distinct advantage of enabling nucleon scattering data to be used 
-directly in the estimation of the Brehmsstrahlung rate, but is only approximate because at large dark photon masses 
+for dark photon brehmsstrahlung. This has the distinct advantage of enabling nucleon scattering data to be used 
+directly in the estimation of the brehmsstrahlung rate, but is only approximate because at large dark photon masses 
 the radiated dark photons carry off considerable momentum and energy. We have been able to reproduce the 
@@
 
-\arz{Need to add citations to many of the Feng et al. papers here.}
 We consider constraints on SIDM specifically within the context of dark electromagnetism models. 
@@
 where $p_1$ and $p_2$ are the four-momenta of the incoming nucleons, $p_3$ and $p_4$ are the momenta 
-of the outgoing nucleons, $\qa$ is the $\Aprime$ momentum, $k=p_2 - p_3$, $l=p_2 - p_4$, and $M_{\mathrm{N}}$ 
+of the outgoing nucleons, $\qa$ is the $\Aprime$ momentum, $k=p_2 - p_4$, $l=p_2 - p_3$, and $M_{\mathrm{N}}$ 
 is the nucleon mass. These kinematical relations correct the relations in Ref.~\cite{dent_etal12}.
@@
 signs of the diagrams. I tried to fix them. Please go over this VERY carefully.}
+\cbm{Fixed a couple of subscripts. I think it should be okay now.}
 
@@
 	\bar{u}(p_3) \gamma_5 u(p_2)\  \bar{u}(p_4) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed{\epsilon} u(p_1),\\
-	M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_2}\ 
+	M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_2}\ 
 	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
-	M_4 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_2}\ 
+	M_4 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_2}\ 
 	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
 	M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_3}\
-	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
+	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
 	M_6 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_3}\ 
@@
 	M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_4}\ 
-	\bar{u}(p_4) \gamma_5 u(p_2)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),\\
+	\bar{u}(p_3) \gamma_5 u(p_4)\ \bar{u}(p_2) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),\\
 	M_8 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_4}\ 
@@
 core supernova temperature of $T = 30\, \mathrm{MeV}$, both of which are typical choices and thought to 
-be representative of supernova cores. \arz{Need to put a citation here for the properties of supernova cores. 
-I can probably find something in the literature, but please put something here if you have a citation.}
+be representative of supernova cores. \cite{snova_core} \arz{Need to put a citation here for the properties of supernova cores. 
+I can probably find something in the literature, but please put something here if you have a citation.} \cbm{That okay?}
 
-We performed the phase space integrals using the Monte Carlo routines in the {\tt CUBA} library. 
+We performed the phase space integrals using the Monte Carlo routines in the {\tt CUBA} library. \cite{hahn_suave}
 \arz{There needs to be some reference, citation, or some other information give about this library here.} 
@@
 and the magnitude of $\vec{q}_{\mathrm{A}'}$ using the delta functions.
-\arz{Cameron, can you double check this to be sure that it is correct? I rephrased it a bit, 
-but I found the earlier phrasing to be a bit ambiguous and I can't remember which choice 
-you made.} We used the {\tt suave} method provided within {\tt CUBA}, which combines 
+ We used the {\tt suave} method provided within {\tt CUBA}, which combines 
 importance sampling and adaptive subdivision, as this method provided the best compromise 
@@
 
-\arz{I removed reference to $N_{\rm eff}$ because for us $N_{\rm eff}=1$ (doesn't it? the 
-only kinematically-allowed decay is to electron-positron pairs, correct?). I also rephrased a 
-little bit. Please review this.}
-
 The dark boson has a typical lifetime of
@@
 \label{eq:decaylength}
-l = \gamma \tau_{\mathrm{A}'} = \frac{3 E_{\mathrm{A}'}}{N_{eff} m_{\mathrm{A}'}^2 \varepsilon^2},
+l = \beta \tau_{\mathrm{A}'} = \frac{3 q_{\mathrm{A}'}}{m_{\mathrm{A'}}^2 \varepsilon^2},
 \eeq
@@
 \exp \left( - \frac{r_{\mathrm{decay}}}{l} \right) = 
-\exp \left( - \frac{r_{\mathrm{decay}} m_{\mathrm{A}'}^2 \varepsilon^2}{3 E_{\mathrm{A}'}} \right),
+\exp \left( - \frac{r_{\mathrm{decay}} m_{\mathrm{A'}}^2 \varepsilon^2}{3 q_{\mathrm{A'}}} \right),
 \eeq
 %
-an approximation which is valid so long as the size of the supernova within which standard model decay 
+where $r_\mathrm{decay}$ is chosen to be 10 km, since the density of the supernova drops quickly around that size.
+This approximation should be valid so long as the size of the supernova within which standard model decay
 products can interact and be thermalized is significantly larger than the region within which $\Aprime$ are produced, 
@@
 The constraint Eq.~(\ref{eq:bound1}), therefore, becomes a transcendental equation that must be solved numerically.
-
-\arz{I have a few questions here. First, what did you choose for the value or $r_{\mathrm{decay}}$? This must 
-be specified explicitly in the text. Please do so as soon as possible.
-
-Second, this treatment is valid under the assumption of relativistic dark photons. However, it is not clear to me that this limit is 
-the appropriate limit. This limit is valid when $m_{\mathrm{A}'} < T = 30 \, \mathrm{MeV}$. However, I think that 
-the decays only become more important than trapping for masses $m_{\mathrm{A}'} \gtrsim 30\, \mathrm{MeV}$. 
-This suggests that we should use the non-relativistic limit here. Do I misunderstand something? Let us address this 
-as soon as possible. Please let me know what you think.}
 
@@
 \arz{This section needs some work as it is a bit hard to follow.} 
+\cbm{I think I've spent too long dealing with the calculation to fix this by myself.
+I can tell it's a bit confusing as a whole, but when I focus on any one part it of course all pretty much makes sense
+	to me}
 
@@
 \beq
-L_{\mathrm{A'}}  = 4\pi \rdp^2 T_{\mathrm{A}'}^4 \sigma,
+L_{\mathrm{A'}}  = 4\pi \rdp^2 T_{\mathrm{A'}}^4 \sigma,
 \eeq
-where $\rdp$ is now the radius of the emitting shell and $T_{\mathrm{A}'}$ its temperature. 
+where $\rdp$ is now the radius of the emitting shell and $T_{\mathrm{A'}}$ its temperature. 
 We estimate the radius of this dark photosphere as $\rdp=10$ km, 
-because the density of the supernova drops drastically around that point. 
-\arz{We need a citation for this statement, but I do not know one off of the top of my head.}
+because the density of the supernova drops drastically around that point. \cite{snova_density} 
+\arz{We need a citation for this statement, but I do not know one off of the top of my head.}\cbm{And that?}
 The bound on the luminosity can then be recast as a bound on $T_{\mathrm{A}'}$, 
@@
 \eea
-with $  \rho_{\mathrm{p}}  = 3\times10^{14}\ {\rm g/cm}^3$, $T_{\mathrm{R}} = 30$~MeV, 
-and $n = 5$. \arz{What is R?}
+with $  \rho_{\mathrm{p}}  = 3\times10^{14}\ {\rm g/cm}^3$, $T_{\mathrm{R}} = 30$~MeV, $R = 10$ km,
+and $n = 5$.
 The optical depth is given by 
@@
 The inverse mean free path can readily be obtained by modifying $ Q_i $, 
-the expression for the energy loss rate, as follows: removing the factor of $ E_A $ 
-and the phase space integral over $ \qa $, and adding a factor of $ e^{E_A/T} $ for detailed balance. 
+the expression for the energy loss rate, as follows: removing the factor of $ E_\mathrm{A'} $ 
+and the phase space integral over $ \qa $, and adding a factor of $ e^{E_\mathrm{A'}/T} $ for detailed balance. 
 \arz{I'm not sure that I follow this somewhat cavalier statement about detailed balance. Can someone 
@@
 This gives the inverse mean free path as a function of mass and coupling. 
-Again, we perform the required integration numerically. \arz{Do you use the same software package here? 
-If so, you must say so.} 
+Again, we perform the required integration numerically using the {\tt CUBA }package. 
 This then allows the calculation of $\kappa_{\mathrm{pp}}$ and $\kappa_{\mathrm{pn}}$, 
@@
 The inverse opacities for the $pn$ and $pp$ processes add, 
-giving the total opacity $ \kappa^{-1} = \kappa_{pp}^{-1} + \kappa_{pn}^{-1} $
+giving the total opacity $ \kappa^{-1} = \kappa_{\mathrm{pp}}^{-1} + \kappa_{\mathrm{pn}}^{-1} $
 
 Having obtained an expression for $ \kappa $, we can now find the optical depth as follows. 
-Define a typical optical depth as $\tau_R = \kappa_R \rho_R R $. We then have 
+Define a typical optical depth as $\tau_\mathrm{R} = \kappa_\mathrm{R} \rho_\mathrm{R} R $. We then have 
 \beq 
-\kappa \rho R = \tau_R \left( \frac{\rho}{\rho_R} \right)^2 \left( \frac{T_R}{T} \right)^{3/2}.
+\kappa \rho R = \tau_\mathrm{R} \left( \frac{\rho}{\rho_\mathrm{R}} \right)^2 \left( \frac{T_\mathrm{R}}{T} \right)^{3/2}.
 \eeq
@@
 \bea 
-\tau &=& \int_{r_x}^{\infty}\, \tau_R \left( \frac{R}{r} \right)^{3n/2} \dd r \\
- &=& \frac{\tau_r}{\frac{3n}{2}-1} \left( \frac{T_A}{T_R} \right)^{(9/2-3/n)}. 
+\tau &=& \int_{r_x}^{\infty}\, \tau_\mathrm{R} \left( \frac{R}{r} \right)^{3n/2} \dd r \\
+ &=& \frac{\tau_\mathrm{r}}{\frac{3n}{2}-1} \left( \frac{T_\mathrm{A'}}{T_\mathrm{R}} \right)^{(9/2-3/n)}. 
  \eea
- The bound on the coupling is obtained by requiring  $ \tau(\varepsilon,m_A) \le 2/3 $
+ The bound on the coupling is obtained by requiring  $ \tau(\varepsilon,m_\mathrm{A'}) \le 2/3 $
 
@@
  to estimate the radius at which $\tau=2/3$ and see if it is actually close to 
- $10$~km. Have you done this?}
+ $10$~km. Have you done this?} %On second thought, put that separately%
 
@@
 \begin{figure*}[th]
-\includegraphics[width=14cm]{constraint.pdf}
+\includegraphics[width=14cm]{compiledbounds_edited.pdf}
 \caption{
 Constraints on dark photon models. Our primary result is the excluded region 
-in the $varepsilon$-$m_{\mathrm{A'}}$ plane shaded in blue. 
+in the $\varepsilon$-$m_{\mathrm{A'}}$ plane shaded in blue. 
 \arz{Cameron, can you describe clearly each line in this caption. Yellow is 
-too hard to see, so please choose another color for this line.}
+too hard to see, so please choose another color for this line.} \cbm{Isn't that what this whole section of text does? It seems redundant}
 }
@@
 
+\cbm{Should the dependence on specific temperature chosen - viz. that it's at most a roughly comparable factor - be mentioned here?}
+
 %--------------------------- CONCLUSIONS

### 2017-04-20 draft.tex
Raffelt as supernova property citation?

@@
 core supernova temperature of $T = 30\, \mathrm{MeV}$, both of which are typical choices and thought to 
-be representative of supernova cores. \cite{snova_core} \arz{Need to put a citation here for the properties of supernova cores. 
-I can probably find something in the literature, but please put something here if you have a citation.} \cbm{That okay?}
+be representative of supernova cores. \arz{Need to put a citation here for the properties of supernova cores. 
+I can probably find something in the literature, but please put something here if you have a citation.} \cbm{On second thought, is Raffelt not good enough for both of these?
+That's where everybody started}
 
@@
 We estimate the radius of this dark photosphere as $\rdp=10$ km, 
-because the density of the supernova drops drastically around that point. \cite{snova_density} 
-\arz{We need a citation for this statement, but I do not know one off of the top of my head.}\cbm{And that?}
+because the density of the supernova drops drastically around that point. 
+\arz{We need a citation for this statement, but I do not know one off of the top of my head.}
 The bound on the luminosity can then be recast as a bound on $T_{\mathrm{A}'}$, 

### 2017-04-20 draft.tex
modified some subscripts and fixed typo.

@@
 SN1987A. Light gauge bosons will be produced within the hot supernova core, primarily through 
-brehmsstrahlung \cbm{This is probably stupid, but shouldn't it be bremsstrahlung, without the first h?}, and radiated. This non-standard energy loss mechanism can result in an energy loss rate 
+bremsstrahlung, and radiated. This non-standard energy loss mechanism can result in an energy loss rate 
 from the supernova core that is inconsistent with observations of neutrinos from SN1987A, 
@@
 \bea 
-p_1 \cdot p_2 &=& M_N^2 - \frac{l^2}{2} - \frac{k^2}{2} + p_2 \cdot \qa,\\
-p_1 \cdot p_3 &=& M_N^2 + k \cdot l - \frac{k^2}{2} + p_3 \cdot \qa,\\  
-p_1 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2}{2} + p_4 \cdot \qa, \\
-p_2 \cdot p_3 &=& M_N^2 - \frac{l^2}{2}, \\ 
-p_2 \cdot p_4 &=& M_N^2 - \frac{k^2}{2},\quad \mathrm{and}\\
-p_3 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2 + k^2}{2},
+p_1 \cdot p_2 &=& M_{\mathrm N}^2 - \frac{l^2}{2} - \frac{k^2}{2} + p_2 \cdot \qa,\\
+p_1 \cdot p_3 &=& M_{\mathrm N}^2 + k \cdot l - \frac{k^2}{2} + p_3 \cdot \qa,\\  
+p_1 \cdot p_4 &=& k \cdot l + M_{\mathrm N}^2 - \frac{l^2}{2} + p_4 \cdot \qa, \\
+p_2 \cdot p_3 &=& M_{\mathrm N}^2 - \frac{l^2}{2}, \\ 
+p_2 \cdot p_4 &=& M_{\mathrm N}^2 - \frac{k^2}{2},\quad \mathrm{and}\\
+p_3 \cdot p_4 &=& k \cdot l + M_{\mathrm N}^2 - \frac{l^2 + k^2}{2},
 \eea
@@
 \begin{eqnarray}
-	M_1 &=& \frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_1}\ 
+	M_1 &=& \frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_1}\ 
 	\bar{u}(p_4) \gamma_5 u(p_2)\  \bar{u}(p_3) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed \epsilon  u(p_1), \\
-	M_2 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_1}\  
+	M_2 &=& -\frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_1}\  
 	\bar{u}(p_3) \gamma_5 u(p_2)\  \bar{u}(p_4) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed{\epsilon} u(p_1),\\
-	M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_2}\ 
+	M_3 &=& \frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_2}\ 
 	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
-	M_4 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_2}\ 
+	M_4 &=& -\frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_2}\ 
 	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
-	M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_3}\
+	M_5 &=& \frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_3}\
 	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
-	M_6 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_3}\ 
+	M_6 &=& -\frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_3}\ 
 	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
-	M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_4}\ 
+	M_7 &=& \frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_4}\ 
 	\bar{u}(p_3) \gamma_5 u(p_4)\ \bar{u}(p_2) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),\\
-	M_8 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_4}\ 
+	M_8 &=& -\frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_4}\ 
 	\bar{u}(p_3) \gamma_5 u(p_2)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),
@@
 \beq
-f(p) =  \frac{n_b}{2} \left( \frac{2 \pi}{M_N T} \right)^{3/2} \exp \left(-\frac{p^2}{2 M_N T} \right).
+f(p) =  \frac{n_b}{2} \left( \frac{2 \pi}{M_{\mathrm{N}} T} \right)^{3/2} \exp \left(-\frac{p^2}{2 M_{\mathrm{N}} T} \right).
 \eeq

### 2017-04-26 draft.tex
Mad a bunch of small changes, added a question or two, general clean up.

@@
 \newcommand{\cbm}[1]{{{\bf{\color{Green}[CBM: #1]}}}}
+\newcommand{\akl}[1]{{{\bf{\color{Blue}[AKL: #1]}}}}
 
@@
 incorrect. Second, the squared matrix elements given in Eq.~(A3) and Eq.~(C18) of Ref.~\cite{dent_etal12} must 
-be incorrect. We have not been able to identify the errors which led to these incorrect expressions; however, 
-there must have been several oversights in the analysis of Ref.~\cite{dent_etal12}. For example, the squared 
+be incorrect. 
+%We have not been able to identify the errors which led to these incorrect expressions; however,  there must have been several oversights in the analysis of Ref.~\cite{dent_etal12}. 
+For example, the squared 
 matrix elements in Eq.~(A3) and Eq.~(C18) do not obey the correct symmetries under interchange of incoming 
@@
 calculation treats nucleon scattering via one-pion exchange (OPE). We have repeated this analysis 
-using and effective field theory for the nucleon interaction and find very similar results so we do not 
+using an effective field theory for the nucleon interaction and find very similar results so we do not 
 report on those in detail.
@@
 computed bounds on mixing of the dark and standard model photons using a soft radiation approximation (SRA) 
-for dark photon brehmsstrahlung. This has the distinct advantage of enabling nucleon scattering data to be used 
-directly in the estimation of the brehmsstrahlung rate, but is only approximate because at large dark photon masses 
+for dark photon bremsstrahlung. This has the distinct advantage of enabling nucleon scattering data to be used 
+directly in the estimation of the bremsstrahlung rate, but is only approximate because at large dark photon masses 
 the radiated dark photons carry off considerable momentum and energy. We have been able to reproduce the 
@@
 We consider constraints on SIDM specifically within the context of dark electromagnetism models. 
-Dark electromagnetism models are models in which a hidden, dark, sector contains a broken U(1)$'$ 
+Dark electromagnetism models are models in which a hidden, dark sector contains a broken U(1)$'$ 
 symmetry and the U(1)$'$ gauge boson is kinetically mixed with the standard model photon. For the 
@@
 Dark gauge bosons are produced in astrophysical environments such as supernova 
-cores primarily via brehmsstrahlung off of standard model particles. This brehmsstrahlung 
+cores primarily via bremsstrahlung off of standard model particles. This bremsstrahlung 
 occurs through the $\varepsilon q$ coupling to charged standard model particles, 
-in this  particular case the proton and pion. The rate of brehmsstrahlung 
+in this  particular case the proton and pion. The rate of bremsstrahlung 
 depends upon both $\varepsilon$ and the mass of the $\Aprime$. Consequently, 
@@
 
-We aim to estimate the rate of energy loss from the core of a supernova from $\Aprime$ brehmsstrahlung 
+We aim to estimate the rate of energy loss from the core of a supernova from $\Aprime$ bremsstrahlung 
 during nucleon-nucleon interactions. The calculation is analogous to the well-known estimate of axion 
@@
 negligible. This section describes the calculation of the rate of energy loss from a supernova core 
-from $\Aprime$ brehmsstrahlung.
+from $\Aprime$ bremsstrahlung.
 
-The brehmsstrahlung process is not the only process with which we must be concerned. Clearly, the rate of 
-brehmsstrahlung will increase with $\varepsilon$; however, $\varepsilon$ can become sufficiently large 
+The bremsstrahlung process is not the only process with which we must be concerned. Clearly, the rate of 
+bremsstrahlung will increase with $\varepsilon$; however, $\varepsilon$ can become sufficiently large 
 that the radiated gauge bosons do not escape the supernova. This happens if the $\Aprime$ particles 
@@
 
-%-- Brehmsstrahlung--	
-\subsection{Brehmsstrahlung of $\Aprime$ Bosons}
+%-- bremsstrahlung--	
+\subsection{bremsstrahlung of $\Aprime$ Bosons}
 
-There are two processes to consider in order to estimate the rate of energy loss via $\Aprime$ brehmsstrahlung. The first is  
+There are two processes to consider in order to estimate the rate of energy loss via $\Aprime$ bremsstrahlung. The first is  
 proton-proton (pp) scattering with the bremsstrahlung of the dark photon off the proton; $p+p \rightarrow p+p+\Aprime$. 
@@
 \caption{One of the five Feynman diagrams for the np process. This particular diagram shows 
-internal brehmsstrahlung off of the charged pion. The remaining four diagrams are analogous to the 
+internal bremsstrahlung off of the charged pion. The remaining four diagrams are analogous to the 
 pp diagram shown in Fig.~\ref{fig:ppdiagram}. In the case of the np processes, there are only four 
-diagrams for brehmsstrahlung off of the external legs because two of the legs correspond to the 
+diagrams for bremsstrahlung off of the external legs because two of the legs correspond to the 
 uncharged neutron.}
@@
 
-\arz{Cameron, can you double check this? I think there were some errors in the momenta and in the relative 
-signs of the diagrams. I tried to fix them. Please go over this VERY carefully.}
-\cbm{Fixed a couple of subscripts. I think it should be okay now.}
-
 The eight diagrams contribute the following eight terms to the pp amplitude, 
+\akl{The expressions below have $M_n/m_\pi$, while in Dent it is $(M_n/m_\pi)^2$.  Which is correct?}
 %
@@
 	M_5 &=& \frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_3}\
-	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
+	\bar{u}(p_4) \gamma_5 u(p_2)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_1),\\
 	M_6 &=& -\frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_3}\ 
@@
 	M_7 &=& \frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_4}\ 
-	\bar{u}(p_3) \gamma_5 u(p_4)\ \bar{u}(p_2) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),\\
+	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_2),\\
 	M_8 &=& -\frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_4}\ 
@@
 given in Ref.~\cite{dent_etal12}; however, they do not simplify significantly if the correct kinematics are used. 
-Unfortunately, with the kinematical relations above, the squared amplitude does not yield a tidy expression 
-for the spin-averaged squared matrix element. Our result contains over 200 terms, 
+%Unfortunately, with the kinematical relations above, the squared amplitude does not yield a tidy expression for the spin-averaged squared matrix element. 
+Our result contains over 200 terms, 
 so we do not reproduce it here for reasons of convenience. However, we note that 
@@
 M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{(l-\qa)^2 - m_\pi^2} 
-\bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p_4) \gamma_5 u(p_2) (\qa - 2l)\cdot \varepsilon.
+\bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p_4) \gamma_5 u(p_2) (\qa - 2l)\cdot \epsilon.
 \end{equation}
@@
 \beq
-f(p) =  \frac{n_b}{2} \left( \frac{2 \pi}{M_{\mathrm{N}} T} \right)^{3/2} \exp \left(-\frac{p^2}{2 M_{\mathrm{N}} T} \right).
+f(p) =  \frac{n_{\mathrm{b}}}{2} \left( \frac{2 \pi}{M_{\mathrm{N}} T} \right)^{3/2} \exp \left(-\frac{p^2}{2 M_{\mathrm{N}} T} \right).
 \eeq
@@
 
-We performed the phase space integrals using the Monte Carlo routines in the {\tt CUBA} library. \cite{hahn_suave}
-\arz{There needs to be some reference, citation, or some other information give about this library here.} 
+We performed the phase space integrals using the Monte Carlo routines in the {\tt CUBA} library \cite{Hahn:2004fe}.
 We integrated over the momenta $\vec{p}_1$, $\vec{p}_2$, $\vec{p}_3$, and the direction of the 
@@
 \begin{equation}
-\left( \frac{L_{\mathrm{max}}}{M} \right) \approx 10^{19} \, \frac{\mathrm{erg}}{\mathrm{g}\, \mathrm{s}}
+\left( \frac{L_{\mathrm{max}}}{M} \right) \approx 10^{19} \, \frac{\mathrm{erg}}{\mathrm{g}\cdot \mathrm{s}}
 \end{equation}
@@
 %
-At this point, we note that Dent et al. in Ref.~\cite{dent_etal12} took a value of 
+At this point, we note that in Ref.~\cite{dent_etal12} took a value of 
 $(L_{\mathrm{max}}/M)$ approximately three orders of magnitude larger than 
@@
 scatter and thermalize on a timescale much shorter than the timescale for the evolution 
-of the core, so decays contribute little to the cooling of the stellar core.
+of the core, so decays within the core contribute little to the supernova cooling.
 
@@
 \end{equation}
-where $\alpha$ is the fine structure constant. Therefore, in the relativistic limit, 
+where $\alpha$ is the fine structure constant. Therefore,
 the typical travel distance to decay is given by 
@@
 \label{eq:decaylength}
-l = \beta \tau_{\mathrm{A}'} = \frac{3 q_{\mathrm{A}'}}{m_{\mathrm{A'}}^2 \varepsilon^2},
+l = \beta \tau_{\mathrm{A}'} = \frac{3 q_{\mathrm{A}'}}{\varepsilon^2 \alpha m_{\mathrm{A}'}^2},
 \eeq
@@
 \exp \left( - \frac{r_{\mathrm{decay}}}{l} \right) = 
-\exp \left( - \frac{r_{\mathrm{decay}} m_{\mathrm{A'}}^2 \varepsilon^2}{3 q_{\mathrm{A'}}} \right),
+\exp \left( - \frac{r_{\mathrm{decay}} m_{\mathrm{A'}}^2\alpha \varepsilon^2}{3 q_{\mathrm{A'}}} \right),
 \eeq
@@
 
-\arz{In what follow ALL SUBSCRIPTS SHOULD BE MADE CONSISTENT WITH PRD CONVENTIONS. Please 
-make all subscripts in roman type using ``mathrm." Please take $A \rightarrow \Aprime$, and so on.}
-
 This is a somewhat involved calculation. First, one needs a model for 
@@
 This then allows the calculation of $\kappa_{\mathrm{pp}}$ and $\kappa_{\mathrm{pn}}$, 
-which are the opacities due to inverse brehmsstrahlung for proton-proton and proton-neutron 
+which are the opacities due to inverse bremsstrahlung for proton-proton and proton-neutron 
 processes respectively. These dominate the opacity of the star to $A'$ propagation. 
@@
  $10$~km. Have you done this?} %On second thought, put that separately%
+\akl{Cameron, you did this correct?  Can you describe?}
 
@@
 in the $\varepsilon$-$m_{\mathrm{A'}}$ plane shaded in blue.
-\arz{Cameron, can you describe clearly each line in this caption. Yellow is 
-too hard to see, so please choose another color for this line.} \cbm{Isn't that what this whole section of text does? It seems redundant}
+The red curve is our attempts to reproduce exactly Ref.~\cite{dent_etal12}, while the black curve is Ref.~\cite{dent_etal12} but with the correct luminosity constraint.
+The yellow curve is using the SRA fixing the cross section using nuclear scattering data, while the green curve uses the soft radiation approximation of the OPE result.
+\arz{Yellow is too hard to see, so please choose another color for this line.} 
 }
@@
 the red line and the lower bound of our exclusion region stems from an incorrect estimate 
-of the brehmsstrahlung rate in Ref.~\cite{dent_etal12}.
+of the bremsstrahlung rate in Ref.~\cite{dent_etal12}.
 
@@
 using the SRA for nucleon interactions, which enabled them to use 
-nuclear scattering data in the estimation of the brehmsstrahlung rate. 
+nuclear scattering data in the estimation of the bremsstrahlung rate. 
 This approach overcomes the shortcomings of the OPE approximation, 
@@
 the possible shortcomings of the SRA approximation, the green line in 
-Fig.~\ref{fig:constraints} shows the lower bound on the excluded region that 
+Fig.~\ref{fig:constraint} shows the lower bound on the excluded region that 
 we drive using the SRA along with OPE expressions for nucleon scattering 
@@
 
-\arz{CBM was supported somehow by AKL.}
 AKL was supported in part by NSF grant PHY-1519175. 

### 2017-04-27 draft.tex
fixed coefficient
Made small corrections

@@
 The eight diagrams contribute the following eight terms to the pp amplitude, 
-\akl{The expressions below have $M_n/m_\pi$, while in Dent it is $(M_n/m_\pi)^2$.  Which is correct?}
 %
@@
 \begin{eqnarray}
-	M_1 &=& \frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_1}\ 
+	M_1 &=& \frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_1}\ 
 	\bar{u}(p_4) \gamma_5 u(p_2)\  \bar{u}(p_3) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed \epsilon  u(p_1), \\
-	M_2 &=& -\frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_1}\  
+	M_2 &=& -\frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_1}\  
 	\bar{u}(p_3) \gamma_5 u(p_2)\  \bar{u}(p_4) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed{\epsilon} u(p_1),\\
-	M_3 &=& \frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_2}\ 
+	M_3 &=& \frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_2}\ 
 	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
-	M_4 &=& -\frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_2}\ 
+	M_4 &=& -\frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_2}\ 
 	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
-	M_5 &=& \frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_3}\
+	M_5 &=& \frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_3}\
 	\bar{u}(p_4) \gamma_5 u(p_2)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_1),\\
-	M_6 &=& -\frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_3}\ 
+	M_6 &=& -\frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_3}\ 
 	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
-	M_7 &=& \frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_4}\ 
+	M_7 &=& \frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_4}\ 
 	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_2),\\
-	M_8 &=& -\frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_4}\ 
+	M_8 &=& -\frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_4}\ 
 	\bar{u}(p_3) \gamma_5 u(p_2)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),
@@
 The red curve is our attempts to reproduce exactly Ref.~\cite{dent_etal12}, while the black curve is Ref.~\cite{dent_etal12} but with the correct luminosity constraint.
-The yellow curve is using the SRA fixing the cross section using nuclear scattering data, while the green curve uses the soft radiation approximation of the OPE result.
-\arz{Yellow is too hard to see, so please choose another color for this line.} 
+The purple curve is using the SRA fixing the cross section using nuclear scattering data, while the green curve uses the soft radiation approximation of the OPE result.
 }
@@
 Rrapaj and Reddy \cite{rrapaj_reddy16} and our result is 
-shown as the yellow line in Fig.~\ref{fig:constraint}. 
+shown as the purple line in Fig.~\ref{fig:constraint}. 
 Our SRA result is in excellent agreement with Ref.~\cite{rrapaj_reddy16}. It is 

### 2017-05-03 draft.tex
updated

@@
  \eea
- The bound on the coupling is obtained by requiring  $ \tau(\varepsilon,m_\mathrm{A'}) \le 2/3 $
+ The bound on the coupling is obtained by requiring  $ \tau(\varepsilon,m_\mathrm{A'}) \le 2/3 $.
+Note that strictly speaking we should have determined $ r_{\mathrm{dp}} $ rather than assuming a value.
+To check if our assumption is valid we can go backwards through the calculation and determine the value of $ r_{\mathrm{dp}} $ at which $ \tau = 2/3$.
+Doing so we find that our choice of 10 km is roughly correct.
 

### 2017-05-10 draft.tex

--- 2017-04-27 draft.tex
@@
 I know that Annika Peter has a few papers and Jonathan Feng probably has some more. 
-Ensuring that you are up to date on these papers is important.} 
-and constraints on self-interacting dark matter (SIDM) models have been explored by many authors \cite{yoshida_etal00,gnedin_ostriker01,miralda-escude02,randall_etal08,kamionkowski_profumo08,zentner09,robertson_zentner09,pieri_etal09,spolyar_etal09,finkbeiner_etal09,
-slatyer_etal09,bramante_etal14,albuquerque_etal14,kaplinghat_etal14,chen_etal14,feng_etal16,catena_widmark16}. 
-In this paper, we revisit and update astrophysical constraints on SIDM models from 
-supernova cooling.
+Ensuring that you are up to date on these papers is important.} \arz{As far as I can see, no new 
+references were added here or in any other relevant spots in the paper. Please do a literature search. At the very least, 
+I know of papers by Annika Peter and Jonathan Feng that may be relevant here.}
+and constraints on self-interacting dark matter (SIDM) models have been explored by many authors \cite{yoshida_etal00,gnedin_ostriker01,miralda-escude02,randall_etal08,kamionkowski_profumo08,zentner09,robertson_zentner09,pieri_etal09,spolyar_etal09,finkbeiner_etal09,slatyer_etal09,bramante_etal14,albuquerque_etal14,kaplinghat_etal14,chen_etal14,feng_etal16,catena_widmark16}.
+In this paper, we revisit and update astrophysical constraints on SIDM models from supernova cooling.
 
@@
 incorrect. Second, the squared matrix elements given in Eq.~(A3) and Eq.~(C18) of Ref.~\cite{dent_etal12} must 
-be incorrect. 
-%We have not been able to identify the errors which led to these incorrect expressions; however,  there must have been several oversights in the analysis of Ref.~\cite{dent_etal12}. 
-For example, the squared 
-matrix elements in Eq.~(A3) and Eq.~(C18) do not obey the correct symmetries under interchange of incoming 
+be incorrect. These matrix elements do not obey the correct symmetries under interchange of incoming 
 and/or outgoing momenta. Furthermore, Ref.~\cite{dent_etal12} neglects the mass of the gauge boson, which 
@@
 given in Ref.~\cite{dent_etal12}; however, they do not simplify significantly if the correct kinematics are used. 
-%Unfortunately, with the kinematical relations above, the squared amplitude does not yield a tidy expression for the spin-averaged squared matrix element. 
-Our result contains over 200 terms, 
-so we do not reproduce it here for reasons of convenience. However, we note that 
-our result for $\vert \mathcal{M}_{\mathrm{pp}} \vert^2$ is symmetric 
-under exchange of $k$ and $l$ as required.
+Our result contains over 200 terms, so we do not reproduce it here for reasons of convenience.
+However, we note that our result for $\vert \mathcal{M}_{\mathrm{pp}} \vert^2$ is symmetric under exchange of $k$ and $l$ as required.
 
@@
 core supernova temperature of $T = 30\, \mathrm{MeV}$, both of which are typical choices and thought to 
-be representative of supernova cores. \arz{Need to put a citation here for the properties of supernova cores. 
-I can probably find something in the literature, but please put something here if you have a citation.} \cbm{On second thought, is Raffelt not good enough for both of these?
-That's where everybody started}
+be representative of supernova cores.
 
@@
 %
-At this point, we note that in Ref.~\cite{dent_etal12} took a value of 
+At this point, we note that Dent et al. in Ref.~\cite{dent_etal12} took a value of 
 $(L_{\mathrm{max}}/M)$ approximately three orders of magnitude larger than 
@@
 where $r_\mathrm{decay}$ is chosen to be 10 km, since the density of the supernova drops quickly around that size.
-This approximation should be valid so long as the size of the supernova within which standard model decay
-products can interact and be thermalized is significantly larger than the region within which $\Aprime$ are produced, 
-an assumption which should be satisfied comfortably. 
-To account for the suppression of gauge boson luminosity due to decays we simply multiply the phase space 
-integrand in Eq.~(\ref{eq:rate1}) by the exponential suppression factor, after which the calculation proceeds 
-as in the previous subsection. The limit is derived in the same way, 
-with the additional complication that $I_{\mathrm{A}'}$ is now a function of $\varepsilon $, in addition to $m_{\mathrm{A}'}$ and $T$. 
+This approximation should be valid so long as the size of the supernova within which standard model decay products can interact and be thermalized is significantly larger than the region within which $\Aprime$ are produced, an assumption which should be satisfied comfortably.
+To account for the suppression of gauge boson luminosity due to decays we simply multiply the phase space integrand in Eq.~(\ref{eq:rate1}) by the exponential suppression factor, after which the calculation proceeds as in the previous subsection.
+The limit is derived in the same way, with the additional complication that $I_{\mathrm{A}'}$ is now a function of $\varepsilon $, in addition to $m_{\mathrm{A}'}$ and $T$.
 The constraint Eq.~(\ref{eq:bound1}), therefore, becomes a transcendental equation that must be solved numerically.
@@
 
-\arz{This section needs some work as it is a bit hard to follow.} 
-\cbm{I think I've spent too long dealing with the calculation to fix this by myself.
-I can tell it's a bit confusing as a whole, but when I focus on any one part it of course all pretty much makes sense
-	to me}
-
 The second effect that produces an upper bound on the excluded region 
@@
 We estimate the radius of this dark photosphere as $\rdp=10$ km, 
-because the density of the supernova drops drastically around that point. 
-\arz{We need a citation for this statement, but I do not know one off of the top of my head.}
-The bound on the luminosity can then be recast as a bound on $T_{\mathrm{A}'}$, 
+because the density of the supernova drops drastically around that point. We will 
+confirm shortly that this estimate is consistent within the context of the simple model that we 
+adopt for the interior structure of the supernova atmospherer. The bound on the luminosity can then 
+be recast as a bound on $T_{\mathrm{A}'}$, 
 %
@@
 
-This is a somewhat involved calculation. First, one needs a model for 
-the density and temperature in the supernova. Following \cite{turner88}, 
-we assume a simple power-law model for the supernova core, with 
+This is a somewhat involved calculation.
+First, one needs a model for the density and temperature in the supernova.
+Following the simple, early model of Ref.~\cite{turner88}, we assume a simple power-law model for the supernova core, with
 \bea
@@
 
-The inverse mean free path can readily be obtained by modifying $ Q_i $, 
+The inverse mean free path can be obtained by modifying $ Q_i $, 
 the expression for the energy loss rate, as follows: removing the factor of $ E_\mathrm{A'} $ 
@@
  \eea
- The bound on the coupling is obtained by requiring  $ \tau(\varepsilon,m_\mathrm{A'}) \le 2/3 $
-
- \arz{It seems as though you can check the consistency of your assumptions can 
- be checked within this calculation. For example, you can actually use this calculation 
- to estimate the radius at which $\tau=2/3$ and see if it is actually close to 
- $10$~km. Have you done this?} %On second thought, put that separately%
-\akl{Cameron, you did this correct?  Can you describe?}
+ The bound on the coupling is obtained by requiring  $ \tau(\varepsilon,m_\mathrm{A'}) \le 2/3 $.
+Note that strictly speaking we should have determined $ r_{\mathrm{dp}}$ rather than assuming a value.
+However, it is possible to verify the self-consistency of our assumption using this model for the supernova atmosphere.
+In particular, this model implies that an optical depth of $\tau=2/3$ is reached at a radial position of $ r_{\mathrm{dp}}=XXXX$,  validating the assumption made at the outset.
+\arz{Put in the missing number here.}
 
@@
 The purple curve is using the SRA fixing the cross section using nuclear scattering data, while the green curve uses the soft radiation approximation of the OPE result.
+\arz{The labels in the figure legend appear to be incorrect now.}
 }
@@
 
-\cbm{Should the dependence on specific temperature chosen - viz. that it's at most a roughly comparable factor - be mentioned here?}
-
 %--------------------------- CONCLUSIONS

### 2017-05-10 draft.tex
Wrote a brief conclusion section.

@@
 constrained the mixing parameter for models in which the dark photon 
-mixes with the standard model photon through a kinetic mixing term.
+mixes with the standard model photon through a kinetic mixing term. Our calculation 
+is similar to previous work in Ref.~\cite{dent_etal12} and Ref.~\cite{rrapaj_reddy16} and 
+is aimed at clarifying some confusion in the literature on this subject that may stem 
+from several errors in the calculation of Ref.~\cite{dent_etal12}.
+
+Our constraints are on the mixing parameter are shown in 
+Fig.~\ref{fig:constraint} and agree well with the those presented in 
+Ref.~\cite{rrapaj_reddy16} and, for dark photon masses $m_{\mathrm{A}'} \gtrsim 10$~MeV, 
+Ref.~\cite{hardy_lasenby17}. We argue that the lower bound on the dark photon mixing parameter 
+is only sensitive to the SRA to within a factor of $\sim 3$ or less. A more precise constraint 
+on such models from SN1987A is probably not practicable because the interior temperature 
+of the SN1987A core is somewhat uncertain and this uncertainty alone gives rise to an uncertainty 
+in the excluded region of at least a factor of $\sim 2-3$. Finally, \citet{hardy_lasenby17} consider 
+plasma effects within the supernova. The most important ramification of this work in the context of 
+our paper is that it suggests significantly weaker constraints on $\varepsilon$ in the mass 
+range $m_{\mathrm{A}'} \lesssim 10$~MeV.
 

### 2017-05-14 draft.tex
Wrote conclusion section. Minor edits throughout.

@@
 \newcommand{\apjl}{Astrophys. J. Lett.}
+\newcommand{\apjs}{Astrophys. J. Supp. Ser.}
 \newcommand{\jcap}{J. Cosmol. Astropart. Phys.}
@@
 In particular, this model implies that an optical depth of $\tau=2/3$ is reached at a radial position of $ r_{\mathrm{dp}}=XXXX$,  validating the assumption made at the outset.
-\arz{Put in the missing number here.}
-
-As we stated in the previous subsection, the approximate treatment of the upper limit of the exclusion region 
-is justified by the fact that values of $\varepsilon$ close to the upper limit of the exclusion region are 
-ruled out by independent, terrestrial experiments.
+\arz{Put in the missing number here.} As we stated in the previous subsection, the approximate treatment of the upper limit of the exclusion region is justified by the fact that values of $\varepsilon$ close to the upper limit of the exclusion region are ruled out by independent, terrestrial experiments.
 
@@
 plasma effects within the supernova. The most important ramification of this work in the context of 
-our paper is that it suggests significantly weaker constraints on $\varepsilon$ in the mass 
-range $m_{\mathrm{A}'} \lesssim 10$~MeV.
+our paper is that it demonstrates that constraints on $\varepsilon$ should be significantly weakened 
+relative to our results in the mass range $m_{\mathrm{A}'} \lesssim 10$~MeV.
+
+Finally, we note that the interior temperature and density within the progenitor of SN1987A remain 
+uncertain at least at the level of tens of percent \citep[e.g.][]{perego15,farmer16}. This is well worth 
+noting because the constraints one derives using the techniques in this work or similar techniques 
+are quite sensitive to the properties of the SN1987A core, particularly the core temperature. Though 
+we do not show this result explicitly, we have replicated our calculations for shifts in core temperature 
+of $\pm 5\, \mathrm{MeV}$ and find that the boundaries of the excluded region shift by a factor of $\sim 2-3$ at low 
+mass ($m_{\mathrm{A}'} \lesssim T$ where $T = 30\, \mathrm{MeV}$ in our fiducial calculation, following 
+work or previous authors) and considerably more at high mass. 
+We conclude that the differences among theoretical techniques for 
+computing the excluded region (OPE, EFT, SRA, ...) lead to uncertainties that are of the same order or 
+smaller than the uncertainty in the excluded region induced by our limited knowledge of the 
+properties of the SN1987A progenitor interior. The excluded regions we and other authors delineate 
+should be considered to be uncertain by a factor or $\sim 3$. Refining the theoretical approach to this 
+problem is therefore unwarranted until a breakthrough in our understanding of the interior of the 
+SN1987A progenitor is achieved.
 
@@
 
+We thank Carles Badenes, John Hillier, and Francis Timmes for guidance in understanding 
+the state of knowledge of the SN1987A progenitor. 
 AKL was supported in part by NSF grant PHY-1519175. 

### 2017-05-15 draft.tex
lots of small changes.

@@
 %-- bremsstrahlung--	
-\subsection{bremsstrahlung of $\Aprime$ Bosons}
+\subsection{Bremsstrahlung of $\Aprime$ Bosons}
 
@@
 	M_1 &=& \frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_1}\ 
-	\bar{u}(p_4) \gamma_5 u(p_2)\  \bar{u}(p_3) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed \epsilon  u(p_1), \\
+	\bar{u}(p_4) \gamma_5 u(p_2)\  \bar{u}(p_3) \gamma_5 (\slashed{p}_1 - \qa +M_{\mathrm N})\slashed \epsilon  u(p_1), \\
 	M_2 &=& -\frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_1}\  
-	\bar{u}(p_3) \gamma_5 u(p_2)\  \bar{u}(p_4) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed{\epsilon} u(p_1),\\
+	\bar{u}(p_3) \gamma_5 u(p_2)\  \bar{u}(p_4) \gamma_5 (\slashed{p}_1 - \qa +M_{\mathrm N})\slashed{\epsilon} u(p_1),\\
 	M_3 &=& \frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_2}\ 
-	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
+	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \gamma_5 (\slashed{p}_2 - \qa +M_{\mathrm N})\slashed \epsilon  u(p_2), \\
 	M_4 &=& -\frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_2}\ 
-	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
+	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \gamma_5 (\slashed{p}_2 - \qa +M_{\mathrm N})\slashed \epsilon  u(p_2), \\
 	M_5 &=& \frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_3}\
-	\bar{u}(p_4) \gamma_5 u(p_2)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_1),\\
+	\bar{u}(p_4) \gamma_5 u(p_2)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_{\mathrm N})\gamma_5 u(p_1),\\
 	M_6 &=& -\frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_3}\ 
-	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
+	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_{\mathrm N})\gamma_5 u(p_2),\\
 	M_7 &=& \frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_4}\ 
-	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_2),\\
+	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_{\mathrm N})\gamma_5 u(p_2),\\
 	M_8 &=& -\frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_4}\ 
-	\bar{u}(p_3) \gamma_5 u(p_2)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),
+	\bar{u}(p_3) \gamma_5 u(p_2)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_{\mathrm N})\gamma_5 u(p_1),
 \end{eqnarray}
@@
 given in Ref.~\cite{dent_etal12}; however, they do not simplify significantly if the correct kinematics are used. 
-Our result contains over 200 terms, so we do not reproduce it here for reasons of convenience.
+Our squared matrix element contains over 200 terms, so we do not reproduce it here for reasons of convenience.
 However, we note that our result for $\vert \mathcal{M}_{\mathrm{pp}} \vert^2$ is symmetric under exchange of $k$ and $l$ as required.
 
-The pn process contains four diagrams analogous to the the diagrams for the pp process (only four, of course, 
+The pn process contains four diagrams analogous to the diagrams for the pp process (only four, of course, 
 because the neutrons cannot radiate the $\Aprime$). The new diagram that is relevant in the pn process is shown in 
@@
 this accepted value. Remarkably, this nearly canceled the errors in their evaluation of 
-$Q_{\mathrm{pp}}$ and $Q_{\mathrm{np}}$ so that they quote constraints that are 
+$Q_{\mathrm{pp}}$ and $Q_{\mathrm{pn}}$ so that they quote constraints that are 
 within an order of magnitude of the correct result.
@@
 where $r_\mathrm{decay}$ is chosen to be 10 km, since the density of the supernova drops quickly around that size.
-This approximation should be valid so long as the size of the supernova within which standard model decay products can interact and be thermalized is significantly larger than the region within which $\Aprime$ are produced, an assumption which should be satisfied comfortably.
+This approximation should be valid so long as the size of the supernova within which standard model decay products can interact and be thermalized is significantly larger than the region within which $\Aprime$ are produced, an assumption that should be satisfied comfortably.
 To account for the suppression of gauge boson luminosity due to decays we simply multiply the phase space integrand in Eq.~(\ref{eq:rate1}) by the exponential suppression factor, after which the calculation proceeds as in the previous subsection.
@@
 which are the opacities due to inverse bremsstrahlung for proton-proton and proton-neutron 
-processes respectively. These dominate the opacity of the star to $A'$ propagation. 
-The inverse opacities for the $pn$ and $pp$ processes add, 
+processes respectively. These dominate the opacity of the star to $\mathrm{A'}$ propagation. 
+The inverse opacities for the $\mathrm{pn}$ and $\mathrm{pp}$ processes add, 
 giving the total opacity $ \kappa^{-1} = \kappa_{\mathrm{pp}}^{-1} + \kappa_{\mathrm{pn}}^{-1} $
@@
 
-Rrapaj and Reddy \cite{rrapaj_reddy16} estimated $A'$ luminosity 
+Rrapaj and Reddy \cite{rrapaj_reddy16} estimated $\mathrm{A'}$ luminosity 
 using the SRA for nucleon interactions, which enabled them to use 

### 2017-05-15 draft.tex
a few more fixes.

@@
 \includegraphics[width=8cm]{npdiagram.pdf}
-\caption{One of the five Feynman diagrams for the np process. This particular diagram shows 
+\caption{One of the five Feynman diagrams for the pn process. This particular diagram shows 
 internal bremsstrahlung off of the charged pion. The remaining four diagrams are analogous to the 
-pp diagram shown in Fig.~\ref{fig:ppdiagram}. In the case of the np processes, there are only four 
+pp diagram shown in Fig.~\ref{fig:ppdiagram}. In the case of the pn processes, there are only four 
 diagrams for bremsstrahlung off of the external legs because two of the legs correspond to the 
@@
 \begin{equation}
-M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{(l-\qa)^2 - m_\pi^2} 
+M'_5 = \frac{4 M_{\mathrm N}}{ m_\pi} \frac{f_{pn}^2 e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{(l-\qa)^2 - m_\pi^2} 
 \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p_4) \gamma_5 u(p_2) (\qa - 2l)\cdot \epsilon.

### 2017-05-15 draft.tex
Added references and a few comments.

@@
 references were added here or in any other relevant spots in the paper. Please do a literature search. At the very least, 
-I know of papers by Annika Peter and Jonathan Feng that may be relevant here.}
-and constraints on self-interacting dark matter (SIDM) models have been explored by many authors \cite{yoshida_etal00,gnedin_ostriker01,miralda-escude02,randall_etal08,kamionkowski_profumo08,zentner09,robertson_zentner09,pieri_etal09,spolyar_etal09,finkbeiner_etal09,slatyer_etal09,bramante_etal14,albuquerque_etal14,kaplinghat_etal14,chen_etal14,feng_etal16,catena_widmark16}.
+I know of papers by Annika Peter and Jonathan Feng that may be relevant here.} \akl{I added these: }\cite{Buckley:2009in,Boddy:2014yra,Boddy:2014qxa,Boddy:2016bbu}
+and constraints on self-interacting dark matter (SIDM) models have been explored by many authors \cite{yoshida_etal00,gnedin_ostriker01,miralda-escude02,randall_etal08,kamionkowski_profumo08,zentner09,robertson_zentner09,pieri_etal09,spolyar_etal09,finkbeiner_etal09,slatyer_etal09,bramante_etal14,albuquerque_etal14,kaplinghat_etal14,chen_etal14,feng_etal16,catena_widmark16} \akl{I added these:} \cite{Markevitch:2003at,Zavala:2012us,Rocha:2012jg,Peter:2012jh,Kahlhoefer:2013dca,Elbert:2014bma,Feng:2015hja,DelNobile:2015uua,Feng:2016ijc,Dooley:2016ajo,Kim:2016ujt,Bringmann:2016din}.
 In this paper, we revisit and update astrophysical constraints on SIDM models from supernova cooling.
@@
 to constraint dark electromagnetism models in which the new gauge boson, the so-called dark photon, 
-is kinetically mixed with the standard model photon. The SN1987A constraint places a limit on the mixing parameter.
+is kinetically mixed with the standard model photon. \akl{I added these:} See also \cite{Kazanas:2014mca,Zhang:2014wra,Chang:2016ntp}. The SN1987A constraint places a limit on the mixing parameter.
 
@@
 Fig.~\ref{fig:ppdiagram}. The fifth diagram, shown in Fig.~\ref{fig:npdiagram}, corresponds to 
-emission of the $\Aprime$ from the exchanged, charged pion.
+emission of the $\Aprime$ from the exchanged, charged pion. \akl{Cameron, can you make the $A' \to \mathrm{A'}$ in figures 1 and 2?}
 
@@
 The purple curve is using the SRA fixing the cross section using nuclear scattering data, while the green curve uses the soft radiation approximation of the OPE result.
-\arz{The labels in the figure legend appear to be incorrect now.}
+\arz{The labels in the figure legend appear to be incorrect now.} \akl{In the legend, the red and black lines need to be switched, and the "Full excluded region" needs to be switched with the "SRA using OPE model".}
 }
@@
 are quite sensitive to the properties of the SN1987A core, particularly the core temperature. Though 
-we do not show this result explicitly, we have replicated our calculations for shifts in core temperature 
+we do not show this result explicitly \akl{Seems to me we should...}, we have replicated our calculations for shifts in core temperature 
 of $\pm 5\, \mathrm{MeV}$ and find that the boundaries of the excluded region shift by a factor of $\sim 2-3$ at low 

### 2017-05-15 draft.tex
added/modified few things.

@@
 Fig.~\ref{fig:ppdiagram}. The fifth diagram, shown in Fig.~\ref{fig:npdiagram}, corresponds to 
-emission of the $\Aprime$ from the exchanged, charged pion. \akl{Cameron, can you make the $A' \to \mathrm{A'}$ in figures 1 and 2?}
+emission of the $\Aprime$ from the exchanged, charged pion. \akl{Andrew, can you make the $A' \to \mathrm{A'}$ in figures 1 and 2?}
 
@@
 and the phase space integral over $ \qa $, and adding a factor of $ e^{E_\mathrm{A'}/T} $ for detailed balance.
+This factor comes from turning the $\mathrm{A'}$ from an outgoing to an incoming state in the calculation.
+See, e.g., Eq.~(4.43) in \cite{raffelt96_book}.
 \arz{I'm not sure that I follow this somewhat cavalier statement about detailed balance. Can someone 
 please explain this to me when we meet. In my earlier rounds of thinking about this, I took that factor 
-at face value as given, assuming I'd eventually be able to figure out where it comes from.} 
+at face value as given, assuming I'd eventually be able to figure out where it comes from.} \akl{Is that good enough?}
 This gives the inverse mean free path as a function of mass and coupling. 
@@
 However, it is possible to verify the self-consistency of our assumption using this model for the supernova atmosphere.
-In particular, this model implies that an optical depth of $\tau=2/3$ is reached at a radial position of $ r_{\mathrm{dp}}=XXXX$,  validating the assumption made at the outset.
-\arz{Put in the missing number here.} As we stated in the previous subsection, the approximate treatment of the upper limit of the exclusion region is justified by the fact that values of $\varepsilon$ close to the upper limit of the exclusion region are ruled out by independent, terrestrial experiments.
+In particular, this model implies that an optical depth of $\tau=2/3$ is reached at a radial position of $ r_{\mathrm{dp}}= 11$ km,  validating the assumption made at the outset.
+As we stated in the previous subsection, the approximate treatment of the upper limit of the exclusion region is justified by the fact that values of $\varepsilon$ close to the upper limit of the exclusion region are ruled out by independent, terrestrial experiments.
 
@@
 The purple curve is using the SRA fixing the cross section using nuclear scattering data, while the green curve uses the soft radiation approximation of the OPE result.
-\arz{The labels in the figure legend appear to be incorrect now.} \akl{In the legend, the red and black lines need to be switched, and the "Full excluded region" needs to be switched with the "SRA using OPE model".}
+\arz{The labels in the figure legend appear to be incorrect now.} \akl{In the legend, the red and black lines need to be switched, and the "Full excluded region" needs to be switched with the "SRA using OPE model".
+Also, can you put a cdot or space between erg and s in the vertical label.}
 }

### 2017-05-15 draft.tex
Made changes

@@
 dave_etal01,hisano_etal04,hisano_etal05,pospelov_etal08,arkani-hamed_etal08a,lattanzi_silk08,ackerman_etal09,feng_etal09,
-kong_etal15} \arz{Cameron: Please review the literature and add some more recent references here. 
-I know that Annika Peter has a few papers and Jonathan Feng probably has some more. 
-Ensuring that you are up to date on these papers is important.} \arz{As far as I can see, no new 
-references were added here or in any other relevant spots in the paper. Please do a literature search. At the very least, 
-I know of papers by Annika Peter and Jonathan Feng that may be relevant here.} \akl{I added these: }\cite{Buckley:2009in,Boddy:2014yra,Boddy:2014qxa,Boddy:2016bbu}
-and constraints on self-interacting dark matter (SIDM) models have been explored by many authors \cite{yoshida_etal00,gnedin_ostriker01,miralda-escude02,randall_etal08,kamionkowski_profumo08,zentner09,robertson_zentner09,pieri_etal09,spolyar_etal09,finkbeiner_etal09,slatyer_etal09,bramante_etal14,albuquerque_etal14,kaplinghat_etal14,chen_etal14,feng_etal16,catena_widmark16} \akl{I added these:} \cite{Markevitch:2003at,Zavala:2012us,Rocha:2012jg,Peter:2012jh,Kahlhoefer:2013dca,Elbert:2014bma,Feng:2015hja,DelNobile:2015uua,Feng:2016ijc,Dooley:2016ajo,Kim:2016ujt,Bringmann:2016din}.
+kong_etal15,Buckley:2009in,Boddy:2014yra,Boddy:2014qxa,Boddy:2016bbu}
+and constraints on self-interacting dark matter (SIDM) models have been explored by many authors \cite{yoshida_etal00,gnedin_ostriker01,miralda-escude02,randall_etal08,kamionkowski_profumo08,zentner09,robertson_zentner09,pieri_etal09,spolyar_etal09,finkbeiner_etal09,slatyer_etal09,bramante_etal14,albuquerque_etal14,kaplinghat_etal14,chen_etal14,feng_etal16,catena_widmark16,Markevitch:2003at,Zavala:2012us,Rocha:2012jg,Peter:2012jh,Kahlhoefer:2013dca,Elbert:2014bma,Feng:2015hja,DelNobile:2015uua,Feng:2016ijc,Dooley:2016ajo,Kim:2016ujt,Bringmann:2016din}
 In this paper, we revisit and update astrophysical constraints on SIDM models from supernova cooling.
@@
 This effect has already been exploited by Dent et al. \cite{dent_etal12}, Rrapaj and Reddy \cite{rrapaj_reddy16}, and 
-Hardy and Lasenby \cite{hardy_lasenby17} \arz{Cameron, add others of which you may be aware.}
+Hardy and Lasenby \cite{hardy_lasenby17} 
 to constraint dark electromagnetism models in which the new gauge boson, the so-called dark photon, 
-is kinetically mixed with the standard model photon. \akl{I added these:} See also \cite{Kazanas:2014mca,Zhang:2014wra,Chang:2016ntp}. The SN1987A constraint places a limit on the mixing parameter.
+is kinetically mixed with the standard model photon. See also \cite{Kazanas:2014mca,Zhang:2014wra,Chang:2016ntp}. The SN1987A constraint places a limit on the mixing parameter.
 

### 2017-05-23 draft.tex
small changes
changed color of my comment to red which is more visible
Drafted abstract.

@@
 \newcommand{\cbm}[1]{{{\bf{\color{Green}[CBM: #1]}}}}
-\newcommand{\akl}[1]{{{\bf{\color{Blue}[AKL: #1]}}}}
+\newcommand{\akl}[1]{{{\bf{\color{Red}[AKL: #1]}}}}
 
@@
 \baselineskip 3.0ex
-Abstract?
+
+We revisit SN1987A constraints on light, hidden sector gauge bosons (``dark photon'') that are coupled to the standard model through kinetic mixing with the photon.
+These constraints are realized because excessive bremsstrahlung radiation of the dark photon can lead to rapid cooling of the SN1987A progenitor core, in contradiction to the observed neutrinos from that event.
+The models we consider are of interest as phenomenological models of strongly self-interacting dark matter (SIDM).
+We clarify several possible ambiguities in the literature and identify errors in prior analyses.
+We find constraints on the dark photon mixing parameter that are in rough agreement with the early estimates of Dent et al.
+\cite{dent_etal12}, but only because significant errors in their analyses fortuitously canceled.
+Our constraints are in good agreement with subsequent analyses by Rrapaj \& Reddy \cite{rrapaj_reddy16} and Hardy \& Lasenby \cite{hardy_lasenby17}.
+We estimate the dark photon bremsstrahlung rate using one-pion exchange (OPE), while Rrapaj \& Reddy use a soft radiation approximation (SRA) to exploit measured nuclear scattering cross sections.
+We find that the differences between mixing parameter constraints obtained through the OPE approximation, the SRA approximation, or an effective field theory model of nuclear interactions are roughly a factor of $\sim 2-3$.
+Hardy \& Laseby \cite{hardy_lasenby17} include plasma effects in their calculations finding significantly weaker constraints on dark photon mixing for dark photon masses below $\sim 10\, \mathrm{MeV}$.
+We do not consider plasma effects.
+Lastly, we point out that the properties of the SN1987A progenitor core remain somewhat uncertain and that this uncertainty alone causes uncertainty of at least a factor or $\sim 2-3$ in the excluded values of the dark photon mixing parameter.
+Further refinement of these estimates is unwarranted until either the interior of the SN1987A progenitor is more well understood or additional, large, and heretofore neglected effects, such as the plasma interactions studied by Hardy \& Lasenby \cite{hardy_lasenby17}, are identified.
+
 \end{abstract}
@@
 \maketitle
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Fig.~\ref{fig:ppdiagram}. The fifth diagram, shown in Fig.~\ref{fig:npdiagram}, corresponds to 
-emission of the $\Aprime$ from the exchanged, charged pion. \akl{Andrew, can you make the $A' \to \mathrm{A'}$ in figures 1 and 2?}
+emission of the $\Aprime$ from the exchanged, charged pion.
 
@@
 %-------------- NP Feynman Diagram
-\begin{figure}
+\begin{figure}[b]
 \includegraphics[width=8cm]{npdiagram.pdf}
@@
 \begin{equation}
-\left( \frac{L_{\mathrm{max}}}{M} \right) \approx 10^{19} \, \frac{\mathrm{erg}}{\mathrm{g}\cdot \mathrm{s}}
+\epsilon_{\mathrm{A}'} = \left( \frac{L_{\mathrm{max}}}{M} \right) \approx 10^{19} \, \frac{\mathrm{erg}}{\mathrm{g}\cdot \mathrm{s}}
 \end{equation}
@@
 $(L_{\mathrm{max}}/M)$ approximately three orders of magnitude larger than 
-this accepted value. Remarkably, this nearly canceled the errors in their evaluation of 
-$Q_{\mathrm{pp}}$ and $Q_{\mathrm{pn}}$ so that they quote constraints that are 
+this generally accepted value. Remarkably, this nearly canceled the errors in their evaluation of 
+$Q_{\mathrm{pp}}$ and $Q_{\mathrm{pn}}$, so that they quote constraints that are 
 within an order of magnitude of the correct result.
@@
 and the phase space integral over $ \qa $, and adding a factor of $ e^{E_\mathrm{A'}/T} $ for detailed balance.
-This factor comes from turning the $\mathrm{A'}$ from an outgoing to an incoming state in the calculation.
-See, e.g., Eq.~(4.43) in \cite{raffelt96_book}.
-\arz{I'm not sure that I follow this somewhat cavalier statement about detailed balance. Can someone 
-please explain this to me when we meet. In my earlier rounds of thinking about this, I took that factor 
-at face value as given, assuming I'd eventually be able to figure out where it comes from.} \akl{Is that good enough?}
+This factor comes from turning the $\mathrm{A'}$ from an outgoing to an incoming state in the calculation (e.g., see Eq.~(4.43) in Ref.~\cite{raffelt96_book}).
 This gives the inverse mean free path as a function of mass and coupling. 
@@
 \caption{
-Constraints on dark photon models. Our primary result is the excluded region 
+Constraints on dark photon models.
+The constraint scales according to the assumed, maximal energy loss rate of $\varepsilon_{\mathrm{A}'} = 10^{19}\, \mathrm{erg}\, \mathrm{g}^{-1}\ \mathrm{s}^{-1}$ as shown on the vertical axis label.
+Our primary result is the excluded region
 in the $\varepsilon$-$m_{\mathrm{A'}}$ plane shaded in blue.
-The red curve is our attempts to reproduce exactly Ref.~\cite{dent_etal12}, while the black curve is Ref.~\cite{dent_etal12} but with the correct luminosity constraint.
-The purple curve is using the SRA fixing the cross section using nuclear scattering data, while the green curve uses the soft radiation approximation of the OPE result.
-\arz{The labels in the figure legend appear to be incorrect now.} \akl{In the legend, the red and black lines need to be switched, and the "Full excluded region" needs to be switched with the "SRA using OPE model".
-Also, can you put a cdot or space between erg and s in the vertical label.}
+The red curve is our attempt to reproduce exactly Ref.~\cite{dent_etal12}, while the black curve is Ref.~\cite{dent_etal12} but with the correct luminosity constraint.
+The purple curve was computed by using the SRA and fixing the cross section through a polynomial fit to nuclear scattering data (e.g., see \cite{rrapaj_reddy16}), while the green curve uses the SRA of the OPE result.
+\arz{On the vertical label, you need to switch $\epsilon$ to $\varepsilon$.}
 }
@@
 are quite sensitive to the properties of the SN1987A core, particularly the core temperature. Though 
-we do not show this result explicitly \akl{Seems to me we should...}, we have replicated our calculations for shifts in core temperature 
+we do not show this result explicitly \akl{Seems to me we should...} \arz{Cameron will have to do this if we want to include it.}, 
+we have replicated our calculations for shifts in core temperature 
 of $\pm 5\, \mathrm{MeV}$ and find that the boundaries of the excluded region shift by a factor of $\sim 2-3$ at low 

### 2017-05-24 draft.tex
Took out relevant comments

@@
 The purple curve was computed by using the SRA and fixing the cross section through a polynomial fit to nuclear scattering data (e.g., see \cite{rrapaj_reddy16}), while the green curve uses the SRA of the OPE result.
-\arz{On the vertical label, you need to switch $\epsilon$ to $\varepsilon$.}
 }
@@
 are quite sensitive to the properties of the SN1987A core, particularly the core temperature. Though 
-we do not show this result explicitly \akl{Seems to me we should...} \arz{Cameron will have to do this if we want to include it.}, 
+we do not show this result explicitly \akl{Seems to me we should...} 
 we have replicated our calculations for shifts in core temperature 

### 2017-05-25 draft.tex
small stuff

@@
 We estimate the dark photon bremsstrahlung rate using one-pion exchange (OPE), while Rrapaj \& Reddy use a soft radiation approximation (SRA) to exploit measured nuclear scattering cross sections.
-We find that the differences between mixing parameter constraints obtained through the OPE approximation, the SRA approximation, or an effective field theory model of nuclear interactions are roughly a factor of $\sim 2-3$.
+We find that the differences between mixing parameter constraints obtained through the OPE approximation or the SRA approximation are roughly a factor of $\sim 2-3$.
 Hardy \& Laseby \cite{hardy_lasenby17} include plasma effects in their calculations finding significantly weaker constraints on dark photon mixing for dark photon masses below $\sim 10\, \mathrm{MeV}$.
@@
 %
-where $\rho = 3 \times 10^{14}\, \mathrm{g/cm}^3$ is the mass density of the core\footnote{
-We use the symbol $\left( L_{\mathrm{A'}}/M \right)$ for the luminosity per unit mass rather than 
-the more conventional symbol $\epsilon_{\mathrm{A'}}$ in order to avoid confusion with the 
-mixing parameter $\varepsilon$.}. Following previous studies, the energy loss rate into novel 
+where $\rho = 3 \times 10^{14}\, \mathrm{g/cm}^3$ is the mass density of the core.
+%\footnote{We use the symbol $\left( L_{\mathrm{A'}}/M \right)$ for the luminosity per unit mass rather than the more conventional symbol $\epsilon_{\mathrm{A'}}$ in order to avoid confusion with the mixing parameter $\varepsilon$.}.
+Following previous studies, the energy loss rate into novel 
 particles cannot exceed 
@@
 without significantly reducing the duration of the neutrino burst observed at Earth for SN1987A 
-\cite{raffelt96_book}. Writing $(L_{\mathrm{A'}}/M) = \varepsilon^2 I_{\mathrm{A'}}(m_{\mathrm{A'}},T)$, 
+\cite{raffelt96_book}. Writing $\epsilon_{\mathrm{A}'}  = \varepsilon^2 I_{\mathrm{A'}}(m_{\mathrm{A'}},T)$, 
 we delineate the constraint on the dark photon mixing parameter by 
@@
 \label{eq:bound1}
-\varepsilon \lesssim \sqrt{\frac{(L_{\mathrm{max}}/M)}{I_{\mathrm{A}'}(m_{\mathrm{A}'}, T)}}.
+\varepsilon \lesssim \sqrt{\frac{\epsilon_{\mathrm{A}'} }{I_{\mathrm{A}'}(m_{\mathrm{A}'}, T)}}.
 \end{equation}
@@
 At this point, we note that Dent et al. in Ref.~\cite{dent_etal12} took a value of 
-$(L_{\mathrm{max}}/M)$ approximately three orders of magnitude larger than 
+$\epsilon_{\mathrm{A}'} $ approximately three orders of magnitude larger than 
 this generally accepted value. Remarkably, this nearly canceled the errors in their evaluation of 
@@
 Constraints on dark photon models.
-The constraint scales according to the assumed, maximal energy loss rate of $\varepsilon_{\mathrm{A}'} = 10^{19}\, \mathrm{erg}\, \mathrm{g}^{-1}\ \mathrm{s}^{-1}$ as shown on the vertical axis label.
+The constraint scales according to the assumed, maximal energy loss rate of $\epsilon_{\mathrm{A}'} = 10^{19}\, \mathrm{erg}\, \mathrm{g}^{-1}\ \mathrm{s}^{-1}$ as shown on the vertical axis label.
 Our primary result is the excluded region
@@
 The purple curve was computed by using the SRA and fixing the cross section through a polynomial fit to nuclear scattering data (e.g., see \cite{rrapaj_reddy16}), while the green curve uses the SRA of the OPE result.
+\akl{Please change vertical axis label by $\varepsilon_{\mathrm A'} \to \epsilon_{\mathrm A'}$ and remove parenthesis.
+On horizontal axis, put prime over A, not next to the A.}
 }

### 2017-06-08 draft.tex
removed comment now that figure was fixed.
added comment

@@
 The purple curve was computed by using the SRA and fixing the cross section through a polynomial fit to nuclear scattering data (e.g., see \cite{rrapaj_reddy16}), while the green curve uses the SRA of the OPE result.
-\akl{Please change vertical axis label by $\varepsilon_{\mathrm A'} \to \epsilon_{\mathrm A'}$ and remove parenthesis.
-On horizontal axis, put prime over A, not next to the A.}
 }
@@
 are quite sensitive to the properties of the SN1987A core, particularly the core temperature. Though 
-we do not show this result explicitly \akl{Seems to me we should...} 
+we do not show this result explicitly \akl{Seems to me we should...  Also, change horizontal label $M_{A'} \to M_{\mathrm{A}'}$.} 
 we have replicated our calculations for shifts in core temperature 

### 2017-06-09 draft.tex
Put figure in

@@
 %--------------------------- CONCLUSIONS
+\begin{figure*}[th]
+	\includegraphics[width=14cm]{temp_sensitivity.pdf}
+	\caption{Effect of changing the core temperature on the dark photon constraint.
+	}
+	\label{fig:temperature}
+\end{figure*}
+
 \section{Discussion}
@@
 are quite sensitive to the properties of the SN1987A core, particularly the core temperature. Though 
-we do not show this result explicitly \akl{Seems to me we should...  Also, change horizontal label $M_{A'} \to M_{\mathrm{A}'}$.} 
+we do not show this result explicitly \akl{Seems to me we should.} 
 we have replicated our calculations for shifts in core temperature 

### 2017-06-09 draft.tex
Had a crack at the temperature

@@
 in the $\varepsilon$-$m_{\mathrm{A'}}$ plane shaded in blue.
-The red curve is our attempt to reproduce exactly Ref.~\cite{dent_etal12}, while the black curve is Ref.~\cite{dent_etal12} but with the correct luminosity constraint.
+The black curve is our attempt to reproduce exactly Ref.~\cite{dent_etal12}, while the red curve is Ref.~\cite{dent_etal12} but with the correct luminosity constraint.
 The purple curve was computed by using the SRA and fixing the cross section through a polynomial fit to nuclear scattering data (e.g., see \cite{rrapaj_reddy16}), while the green curve uses the SRA of the OPE result.
@@
 	\includegraphics[width=14cm]{temp_sensitivity.pdf}
-	\caption{Effect of changing the core temperature on the dark photon constraint.
+	\caption{Effect of changing the core temperature on the lower bound of the dark photon constraint.
+The  calculation that produced the blue line of Fig.
+\ref{fig:constraint} was repeated for core temperatures of 25 MeV, 30 MeV, and 35 MeV.
+In this case the energy loss rate was throughout taken to be $\epsilon_{\mathrm{A}'} = 10^{19}\, \mathrm{erg}\, \mathrm{g}^{-1}\ \mathrm{s}^{-1}$
 	}
@@
 of the SN1987A core is somewhat uncertain and this uncertainty alone gives rise to an uncertainty 
-in the excluded region of at least a factor of $\sim 2-3$. Finally, \citet{hardy_lasenby17} consider 
+in the excluded region of at least a factor of $\sim 2$. Finally, \citet{hardy_lasenby17} consider 
 plasma effects within the supernova. The most important ramification of this work in the context of 
@@
 noting because the constraints one derives using the techniques in this work or similar techniques 
-are quite sensitive to the properties of the SN1987A core, particularly the core temperature. Though 
-we do not show this result explicitly \akl{Seems to me we should.} 
-we have replicated our calculations for shifts in core temperature 
-of $\pm 5\, \mathrm{MeV}$ and find that the boundaries of the excluded region shift by a factor of $\sim 2-3$ at low 
+are quite sensitive to the properties of the SN1987A core, particularly the core temperature. %Though 
+%we do not show this result explicitly \akl{Seems to me we should.} 
+As shown in Fig.
+~\ref{fig:temperature}, we have repeated a portion of our calculations after shifting the core temperature by $\pm 5\, \mathrm{MeV}$ and found that the lower boundary of the excluded region shifts by a factor of $\sim 2$ at low
 mass ($m_{\mathrm{A}'} \lesssim T$ where $T = 30\, \mathrm{MeV}$ in our fiducial calculation, following 
-work or previous authors) and considerably more at high mass. 
+work of previous authors) and considerably more at high mass. 
 We conclude that the differences among theoretical techniques for 
-computing the excluded region (OPE, EFT, SRA, ...) lead to uncertainties that are of the same order or 
+computing the excluded region (OPE, SRA, ...) lead to uncertainties that are of the same order or 
 smaller than the uncertainty in the excluded region induced by our limited knowledge of the 
 properties of the SN1987A progenitor interior. The excluded regions we and other authors delineate 
-should be considered to be uncertain by a factor or $\sim 3$. Refining the theoretical approach to this 
+should be considered to be uncertain by a factor of $\sim 3$. Refining the theoretical approach to this 
 problem is therefore unwarranted until a breakthrough in our understanding of the interior of the 

### 2017-06-19 draft.tex
Removed stray EFT reference.

@@
 We do not consider plasma effects.
-Lastly, we point out that the properties of the SN1987A progenitor core remain somewhat uncertain and that this uncertainty alone causes uncertainty of at least a factor or $\sim 2-3$ in the excluded values of the dark photon mixing parameter.
+Lastly, we point out that the properties of the SN1987A progenitor core remain somewhat uncertain and that this uncertainty alone causes uncertainty of at least a factor of $\sim 2-3$ in the excluded values of the dark photon mixing parameter.
 Further refinement of these estimates is unwarranted until either the interior of the SN1987A progenitor is more well understood or additional, large, and heretofore neglected effects, such as the plasma interactions studied by Hardy \& Lasenby \cite{hardy_lasenby17}, are identified.
-
 \end{abstract}
@@
 primarily to repeating the calculation of Ref.~\cite{dent_etal12} in order to rectify these oversights. Our primary 
-calculation treats nucleon scattering via one-pion exchange (OPE). We have repeated this analysis 
-using an effective field theory for the nucleon interaction and find very similar results so we do not 
-report on those in detail.
+calculation treats nucleon scattering via one-pion exchange (OPE).
 
@@
 Finally, we note that the interior temperature and density within the progenitor of SN1987A remain 
-uncertain at least at the level of tens of percent \citep[e.g.][]{perego15,farmer16}. This is well worth 
+uncertain at least at the level of several tens of percent \citep[e.g.][]{perego15,farmer16}. This is well worth 
 noting because the constraints one derives using the techniques in this work or similar techniques 
-are quite sensitive to the properties of the SN1987A core, particularly the core temperature. %Though 
-%we do not show this result explicitly \akl{Seems to me we should.} 
-As shown in Fig.
-~\ref{fig:temperature}, we have repeated a portion of our calculations after shifting the core temperature by $\pm 5\, \mathrm{MeV}$ and found that the lower boundary of the excluded region shifts by a factor of $\sim 2$ at low
+are quite sensitive to the properties of the SN1987A core, particularly the core temperature. 
+As an example of this, we have repeated a portion of our calculations after 
+shifting the core temperature by $\pm 5\, \mathrm{MeV}$. This result is shown in Figure~\ref{fig:temperature}.  
+We find that the lower boundary of the excluded region shifts by a factor of $\sim 2$ at low 
 mass ($m_{\mathrm{A}'} \lesssim T$ where $T = 30\, \mathrm{MeV}$ in our fiducial calculation, following 
-work of previous authors) and considerably more at high mass. 
-We conclude that the differences among theoretical techniques for 
-computing the excluded region (OPE, SRA, ...) lead to uncertainties that are of the same order or 
+work of previous authors) and considerably more at high mass. We conclude that the differences among theoretical 
+techniques for computing the excluded region (OPE, SRA, ...) lead to uncertainties that are of the same order or 
 smaller than the uncertainty in the excluded region induced by our limited knowledge of the 

### 2017-06-20 draft.tex
fixed typos

@@
 
-We revisit SN1987A constraints on light, hidden sector gauge bosons (``dark photon'') that are coupled to the standard model through kinetic mixing with the photon.
+We revisit SN1987A constraints on light, hidden sector gauge bosons (``dark photons'') that are coupled to the standard model through kinetic mixing with the photon.
 These constraints are realized because excessive bremsstrahlung radiation of the dark photon can lead to rapid cooling of the SN1987A progenitor core, in contradiction to the observed neutrinos from that event.
-The models we consider are of interest as phenomenological models of strongly self-interacting dark matter (SIDM).
+The models we consider are of interest as phenomenological models of strongly self-interacting dark matter.
 We clarify several possible ambiguities in the literature and identify errors in prior analyses.
@@
 kong_etal15,Buckley:2009in,Boddy:2014yra,Boddy:2014qxa,Boddy:2016bbu}
-and constraints on self-interacting dark matter (SIDM) models have been explored by many authors \cite{yoshida_etal00,gnedin_ostriker01,miralda-escude02,randall_etal08,kamionkowski_profumo08,zentner09,robertson_zentner09,pieri_etal09,spolyar_etal09,finkbeiner_etal09,slatyer_etal09,bramante_etal14,albuquerque_etal14,kaplinghat_etal14,chen_etal14,feng_etal16,catena_widmark16,Markevitch:2003at,Zavala:2012us,Rocha:2012jg,Peter:2012jh,Kahlhoefer:2013dca,Elbert:2014bma,Feng:2015hja,DelNobile:2015uua,Feng:2016ijc,Dooley:2016ajo,Kim:2016ujt,Bringmann:2016din}
+and constraints on self-interacting dark matter (SIDM) models have been explored by many authors \cite{yoshida_etal00,gnedin_ostriker01,miralda-escude02,randall_etal08,kamionkowski_profumo08,zentner09,robertson_zentner09,pieri_etal09,spolyar_etal09,finkbeiner_etal09,slatyer_etal09,bramante_etal14,albuquerque_etal14,kaplinghat_etal14,chen_etal14,feng_etal16,catena_widmark16,Markevitch:2003at,Zavala:2012us,Rocha:2012jg,Peter:2012jh,Kahlhoefer:2013dca,Elbert:2014bma,Feng:2015hja,DelNobile:2015uua,Feng:2016ijc,Dooley:2016ajo,Kim:2016ujt,Bringmann:2016din}.
 In this paper, we revisit and update astrophysical constraints on SIDM models from supernova cooling.
@@
 the radiated dark photons carry off considerable momentum and energy. We have been able to reproduce the 
-result of Rrapaj and Reddy \cite{rrapaj_reddy16} and find that the SRA plausibly results in only a factor or 
+result of Rrapaj and Reddy \cite{rrapaj_reddy16} and find that the SRA plausibly results in only a factor of 
 $\sim 3$ underestimate of the upper bound on the dark photon mixing parameter at most. Moreover, 
